### 2014-10-13 PAPER_AMMLY.tex
First draft

\documentclass[twoside]{article}
\usepackage{aistats2014}
\usepackage{amsthm,amsmath}
\usepackage{amssymb}
\usepackage[boxed]{algorithm2e}
\usepackage{bm}
\usepackage{bbm}
\usepackage{url}
\usepackage{comment}
\usepackage{url}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{color}
\usepackage{tikz}

% If your paper is accepted, change the options for the package
% aistats2014 as follows:
%
%\usepackage[accepted]{aistats2014}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

\begin{document}

% If your paper is accepted and the title of your paper is very long,
% the style will print as headings an error message. Use the following
% command to supply a shorter title of your paper so that it can be
% used as headings.
%
%\runningtitle{I use this title instead because the last one was very long}

% If your paper is accepted and the number of authors is large, the
% style will print as headings an error message. Use the following
% command to supply a shorter version of the authors names so that
% they can be used as headings (for example, use only the surnames)
%
%\runningauthor{Surname 1, Surname 2, Surname 3, ...., Surname n}

\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]

\def\layersep{2cm}
\def\layersepp{4cm}

\twocolumn[

\aistatstitle{Connecting deep networks with the spin-glass model}

\aistatsauthor{ Anonymous Author 1 \And Anonymous Author 2 \And Anonymous Author 3 }
%\aistatsauthor{
%\And
%Anna Choromanska \\
%\texttt{achoroma@cims.nyu.edu} \\
%\And
%Mikael Henaff\\
%\texttt{mbh305@nyu.edu} \\
%\And
%Michael Mathieu\\
%\texttt{mathieu@cs.nyu.edu}\\
%\And
%Levent Sagun\\
%\texttt{sagun@cims.nyu.edu} \\
%\And
%Yann LeCun\\
%\texttt{yann@cs.nyu.edu} \\
%}

\aistatsaddress{ Unknown Institution 1 \And Unknown Institution 2 \And Unknown Institution 3 } ]
%\aistatsaddress{
%Courant Institute of Mathematical Sciences \\
%New York University\\
%New York, NY 10012 \\
%}]

\begin{abstract}
We explore the approximate equivalence of the highly non-convex loss function of a simple model of the fully-connected feed-forward neural network with the Hamiltonian of the spherical spin glass model under a certain assumptions. Using the results from the random matrix theory, we demonstrate that for large-size near-symmetric networks the lowest critical values above the global minimum of the loss function are located in a well-defined band and furthermore they form a layered structure. We show that the expected number of local minima of the loss function in this band grows exponentially with the size of the network, and at the same time the probability of finding a saddle point in this band diminishes exponentially. We empirically demonstrate that both simulated annealing and SGD converges to the band of the lowest critical values, and furthermore all critical points found there correspond to the same learning quality measured by the test error.
\end{abstract}

\section{Introduction}

\section{Deep network and spin-glass model}

\subsection{Preliminaries}

For the theoretical analysis, we consider a simple model of the fully-connected feed-forward deep network with a single output and rectified linear units. We call the network $\mathcal{N}$. We focus on a binary classification task. Let $X$ be the random input vector of dimensionality $d$. Let $(H-1)$ denote the number of hidden layers in the network and we will refer to the input layer as the $0^{\text{th}}$ layer and to the output layer as the $H^{\text{th}}$ layer. Let $n_i$ denote the number of units in the $i^{\text{th}}$ layer (note that $n_0 = d$ and $n_H = 1$). Let $W_i$ be the matrix of weights between $(i - 1)^{\text{th}}$ and $i^{th}$ layers of the network. Also, let $\sigma$ denotes the activation function that converts a unit's weighted input to its output activation. We consider linear rectifiers thus $\sigma(x) = \max(0,x)$. We can therefore write that for any given random input vector $X$, the network gives the following (random) output $Y$:
\[Y = q\sigma(W_H^{\top}\sigma(W_{H-1}^{\top}\dots\sigma(W_1^{\top}X)))\dots),
\]
where $q = \sqrt{\frac{n_0n_1 + n_1n_2 + ... + n_{H-1}n_H}{n_0n_1...n_H}}$ is simply a normalization factor. The same expression for the output of the network can be re-expressed in the following way:
\begin{equation}
Y = q\sum_{i=1}^{n_0}\sum_{j = 1}^\gamma X_{i,j}A_{i,j}\prod_{k = 1}^{H}w_{i,j}^{(k)},
\label{eq:befrein}
\end{equation}
where the first summation is over the network inputs and the second one is over all paths from a given network input to its output, where $\gamma$ is the total number of such paths (note that $\gamma = n_1n_2\dots n_H$). Furthermore, $w_{i,j}^{(k)}$ is the weight of the $k^{\text{th}}$ segment of path indexed with $(i,j)$ which connects layer $(k-1)^{st}$ with layer $k^{\text{th}}$ of the network. Note that each path corresponds to a certain set of $H$ weights, which we refer to as a \textit{configuration of weights}. Random variable $A_{i,j}$ denotes whether path $(i,j)$ is active ($A_{i,j} = 1$) or not ($A_{i,j} = 0$).  We assume each path is equally likely to be active thus $A_{i,j}$'s will be modelled as Bernoulli random variables with the same probability of success $\rho$.

\begin{definition}
The mass of the network $\Psi$ is the total number of all paths between all network inputs and outputs: $\Psi = \prod_{i=0}^Hn_i$.
\end{definition}

\begin{definition}
The size of the network $\Lambda$ is the total number of network parameters: $\Lambda = \prod_{i=0}^{H-1}n_in_{i+1}$.
\end{definition}

There exists a lower- and upper-bound on the size of the network that depends on the mass of the network as captured in Theorem~\ref{thm:arge}.
\begin{theorem}
The size of the network is bounded as follows
\[\Psi^2\frac{1}{d} \geq \Lambda \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}}.
\]
\label{thm:arge}
\end{theorem}
\begin{proof}
First we will prove the lower-bound. By the inequality between arithmetic and geometric mean the mass and the size of the network are connected as follows
\[\Lambda \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{n_0n_H}} = \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}}
\]
The upper-bound can be shown as follows
\[\Lambda \leq \prod_{i=0}^{H-1}n_in_{i+1} = \frac{\Psi^2}{n_0n_H} = \Psi^2\frac{1}{d}.
\]
\end{proof}

\subsection{Approximation}

Let $\mathcal{W} = \{w_1,w_2,\dots,w_{\Lambda}\}$ be the set of all weights of the network. Furthermore let $\mathcal{A}_{\Lambda}$ denote the set of all $H$-length configuration of weights chosen from $W$. Note that the size of $\mathcal{A}_{\Lambda}$ is $\Lambda^H$. Also let $\mathcal{B}$ be a set such that each element correspond to the single configuration of weights from Equation~\ref{eq:befrein}, thus $\mathcal{B} = \{(w_{1,1}^1,w_{1,1}^2,\dots,w_{1,1}^H),(w_{1,2}^1,w_{1,2}^2,\dots,w_{1,2}^H),\dots,\\(w_{n_0,\gamma}^1,w_{n_0,\gamma}^2,\dots,w_{n_0,\gamma}^H)\}$, where every single weight comes from set $\mathcal{W}$. Note that in general there might exist elements in $\mathcal{A}_{\Lambda}$ that will never appear in $\mathcal{B}$ and also some elements in $\mathcal{A}_{\Lambda}$ may appear in $\mathcal{B}$ multiple times. Thus Equation~\ref{eq:befrein} can be equivalently restated as 
\[Y \!=\! q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\left(\sum_{c=1}^{r_{i_1,i_2,\dots,i_H}}\!\!\!X_{i_1,i_2,\dots,i_H}^{(c)}A_{i_1,i_2,\dots,i_H}^{(c)}\!\!\right)\!\!\prod_{k = 1}^{H}w_{i_k},
\]
where $r_{i_1,i_2,\dots,i_H}$ denotes the number of times configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein}. Note that $r_{i_1,i_2,\dots,i_H} \in \{\mathbb{Z}^{+}\cup{0}\}$ and furthermore $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H} = \Psi$. Assuming the independence of $X$'s and $A's$ we get
\[\mathbb{E}_A[Y] = q\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\left(\sum_{c=1}^{r_{i_1,i_2,\dots,i_H}}X_{i_1,i_2,\dots,i_H}^{(c)}\right)\rho\prod_{k = 1}^{H}w_{i_k}
\]
Let $Y_{\Lambda} = \mathbb{E}_A[Y]$, where in particular $\Lambda$ in this notation refers to the size of set $\mathcal{A}$ (this notation will be helpful later in this section), and define random variables $Z$'s as
\[Z_{i_1,i_2,\dots,i_H=1} = \frac{1}{\sqrt{r_{i_1,i_2,\dots,i_H}}}\sum_{c=1}^{r_{i_1,i_2,\dots,i_H}}X_{i_1,i_2,\dots,i_H}^{(c)}.
\]
For our theoretical analysis we also assume that $X$'s and also $Z$'s are independent and furthermore that $X$'s are identically distributed such that $X_{i_1,i_2,\dots,i_H}^{(c)}\sim\mathcal{N}(0,1)$. Therefore $Z_{i_1,i_2,\dots,i_H}\sim\mathcal{N}(0,1)$. Thus 
\begin{equation}
Y_{\Lambda}= q\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{r_{i_1,i_2,\dots,i_H}}Z_{i_1,i_2,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k}.
\label{eq:befapprox}
\end{equation}
Let instead the number of uniqe weghts in a network be changed from $\Lambda$ to $s$ where $s \leq \Lambda$. Consider another expression
\begin{equation}
\hat{Y}_s = q\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}Z_{i_1,i_2,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
\label{eq:approx}
\end{equation}
which can be thought of as an output of some network $\hat{\mathcal{N}}$ where the weights are still chosen from $\mathcal{A}$ but there are only $s$ unique weights in $\mathcal{A}$ and the remaining $(\Lambda-s)$ weights are repetitions, and furthermore every $H$ - length configuration of weights chosen from $\mathcal{A}$ is equally likely. We will refer to this expression soon. \textcolor{red}{Draw an example}.

\textcolor{red}{We assume that there exists hidden relations between weights that the architecture is not reflecting and that are strictly data-dependent.}Let us now slowly introduce the notion of $(s,\epsilon)$ - realizability. Consider a family of networks $\{\mathcal{N}^{'}\}_s$ which have the same graph of connections as the network $\mathcal{N}$ but different edge weighting such that they only have $s$ unique weights and $s \leq \Lambda$. Also we require that for any two networks where one of them belongs to set $\{\mathcal{N}^{'}\}_{s_1}$ and produces output $Y_{s_1}$ and the other belongs to set $\{\mathcal{N}^{'}\}_{s_2}$ and produces output $Y_{s_2}$ the following holds
\begin{equation}
corr(Y_{s_1},\hat{Y}_{s_1}) \geq corr(Y_{s_2},\hat{Y}_{s_2}),
\label{eq:condition}
\end{equation}
where $corr$ denotes the correlation defined as $corr(A,B) = \frac{\mathbb{E}[(A - \mathbb{E}[A]])(B - \mathbb{E}[B]])}{std(A)std(B)}$, where $std$ is the standard deviation, and $s_1 \leq s_2$. \textcolor{red}{Intuitively condition in Equation~\ref{eq:condition} seems natural to sattisfy as with smaller $s$ more configurations appearing in $\hat{Y}_s$ should also appear in $Y_s$. Draw an example}.

Furthermore, for a given $s \in \{1,2,\dots,\Lambda\}$ let $\epsilon_s$ be defined
\[\epsilon_s = \max_{\mathcal{M} \in \{\mathcal{N}^{'}\}_s}[\min(1-corr(Y_s,Y_{\Lambda}),1-corr(Y_s,\hat{Y}_s))],
\] 
where $Y_s$ is the output of network $\mathcal{M}$ and $\min(1-corr(Y_s,Y_{\Lambda}),1-corr(Y_s,\hat{Y}_s))$ denotes the smallest of two values: $1-corr(Y_s,Y_{\Lambda})$ and $1-corr(Y_s,\hat{Y}_s)$. We will now define the correlation factor and the symmetry factor of a network $\mathcal{N}$. \textcolor{red}{Typically for large networks small $s$ is sufficient to achieve small $\epsilon_s$.}
\begin{definition}
A correlation factor $\kappa$ of a network $\mathcal{N}$ is
\[\kappa = 1 - \min_{i \in \{1,2,\dots,\Lambda\}} \epsilon_i
\]
and a symmetry factor $s$ of a network $\mathcal{N}$ is
\[s = \arg\min_{i \in \{1,2,\dots,\Lambda\}} \epsilon_i.
\]
A network $\mathcal{N}$ with correlation factor $\kappa$ and symmetry factor $s$ will be called $(s,\kappa)$-realizable.
\end{definition}
We will now define the approximation of the output of a network $\mathcal{N}$.
\begin{definition}
$\hat{Y}$ is a $\delta$-approximation of the output $Y_{\Lambda}$ of network $\mathcal{N}$ if
\[corr(\hat{Y},Y_\Lambda) \geq 1-\delta.
\]
\end{definition}
The next theorem captures that $\hat{Y}_s$ from Equation~\ref{eq:approx} is a $(2\kappa^2-1)$ - approximation of $Y_{\Lambda}$.
\begin{theorem}
Let $\mathcal{N}$ be a $(s,\kappa)$-realizable network producing the output given in Equation~\ref{eq:befapprox}, for some $\kappa \in [-1,1]$ and $s \in \{1,2,\dots,\Delta\}$. Then $Y_s$ given in Equation~\ref{eq:approx} is the $2(1-\kappa^2)$ - approximation of the output of the network $\mathcal{N}$.
\end{theorem}
\begin{proof}
From the fact that $\mathcal{N}$ is $(s,\kappa)$-realizable it follows that 
\[corr(Y_s,Y_{\Lambda}) \geq \kappa \:\:\:\text{and}\:\:\:corr(Y_s,\hat{Y}_s) \geq \kappa
\]
Furthermore, by the property of the correlations
\begin{eqnarray*}
corr(Y_{\Lambda},\hat{Y}_s) \!\!\!\!\!&\geq&\!\!\!\!\! corr(Y_{\Lambda},Y_s)corr(Y_{\Lambda},\hat{Y}_s)\\
&-&\!\!\!\!\! \sqrt{(1 \!-\! corr(Y_{\Lambda},Y_s)^2)(1 \!-\! corr(Y_{\Lambda},\hat{Y}_s)^2)}\\
&=&2\kappa^2-1
\end{eqnarray*}
\end{proof}

\textcolor{red}{The property of a symmetry of a network can be thought of as an assumption on the architecture of the network since it imposes the constraint of having many repetitions of the same set of weights in the network evenly distributed in the network graph so that the set of all paths in the network cover all possible configuration of weights evenly. However note that for very large-size networks, the symmetry assumption is easier and more natural to sattisfy leading to smaller values of $\epsilon$. Consider for instance constructing the $\epsilon$-approximation of $Y$ by first dyscretizing the weights of the oryginal network into $b$ bins. The repetitions of weights occur more frequently now without hurting much the network performance. Note also that in particular in case of a very deep and wide architectures, small values of $b$ are sufficient to achieve two goals simultaneously: well-approximate complex functions and guarantee near-symmetry of a network.}

Next we will consider two frequently used loss functions, absolute loss and hinge loss, where we use $\hat{Y}_s$ as an approximator to the ouput $Y_{\Lambda}$ of a network.

\subsection{Loss function as a $H$-spin spherical spin-glass model}

Let $\mathcal{L}^a_{\Lambda,H}(w)$ and $\mathcal{L}^h_{\Lambda,H}(w)$ be the (random) absolute loss and (random) hinge loss defined as
\[\mathcal{L}^a_{\Lambda,H}({\bm w}) = |Y_t - \hat{Y}_s|
\]
and
\[\mathcal{L}^h_{\Lambda,H}({\bm w}) = \max(0,1-Y_t\hat{Y}_s).
\]
where $Y_t$ is a random variable corresponding the true data labeling that takes values $-1$ or $1$. Also note that in case of the hinge loss $\max$ operator can be modelled as Bernoulli random variable, that we will refer to as $M$, with success ($M = 1$) probability $\rho^{'}$. We assume $M$ is independent of $\hat{Y}_s$. Therefore we obtain that
\[\mathcal{L}^a_{N,H}({\bm w}) = \left \{
  \begin{tabular}{c}
  $\!\!\!\!\!\!1 - \hat{Y}_s$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = 1$ \\
  $\!1 + \hat{Y}_s$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -1$ \\
  \end{tabular}
\right.
\]
and
\begin{eqnarray*}
\mathcal{L}^h_{\Lambda,H}({\bm w}) &=& \mathbb{E}_{M,A}[M(1-Y_t\hat{Y}_s)]\\&=& \left \{
  \begin{tabular}{c}
  $\!\!\!\!\!\!\mathbb{E}_{M}[M(1 - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = 1$ \\
  $\!\mathbb{E}_{M}[M(1 + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -1$ \\
  \end{tabular}
\right.
\end{eqnarray*}
Note that both cases can be generalized to the following
\[\mathcal{L}_{\Lambda,H}({\bm w}) = \left \{
  \begin{tabular}{c}
  $\!\!\!\!\!\!\mathbb{E}_{M}[M(1 - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = 1$ \\
  $\!\mathbb{E}_{M}[M(1 + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -1$ \\
  \end{tabular}
\right.,
\]
where in case of absolute loss $\rho^{'} = 1$. Furthermore, since $X$'s are Gaussian random variables, then so are $-X$'s thus we can further generalize that
\begin{eqnarray*}
\mathcal{L}_{\Lambda,H}({\bm w}) \!\!\!\!\!&=&\!\!\!\!\! \mathbb{E}_{M}[M(1 + \hat{Y}_s)]\\
&=& \!\!\!\!\!\rho^{'} + \rho^{'}\hat{Y}_s\\
&=& \!\!\!\!\!\rho^{'} + q\sqrt{\!\frac{\Psi}{\Lambda^H}\!}\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!Z_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}
\end{eqnarray*}
Let $\tilde{w}_i = \sqrt[H]{\rho\rho^{'}}w_i$ for all $i = \{1,2,\dots,k\}$.  Thus
\begin{equation}
\mathcal{L}_{\Lambda,H}({\bm w}) = \rho + q\sqrt{\frac{\Psi}{\Lambda^H}}\sum_{i_1,\dots,i_H=1}^{\Lambda}Z_{i_1,\dots,i_H}\prod_{k = 1}^{H}\tilde{w}_{i_k}.
\label{eq:befloss}
\end{equation}
We furthermore make a benign assumption that the weights sattisfy the spherical condition 
\begin{equation}
\frac{1}{\Lambda}\sum_{i=1}^{\Lambda}\tilde{w}_i^2 = 1
\label{eq:spherical}
\end{equation}
To simplify the notation in Equation~\ref{eq:befloss} we drop the letter accents and simply denote $\hat{w}$ as $w$. We skip constant $\rho$ as it does not matter when minimizing the loss function.
\begin{equation}
\mathcal{L}_{\Lambda,H}({\bm w}) = \frac{1}{\Lambda^{(H-1)/2}}\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!Z_{i_1,i_2,\dots,i_H}w_{i_1}w_{i_2}\dots\!w_{i_H},
\label{eq:spinglass}
\end{equation}
where the last inequality was obtained by substituting $q = \sqrt{\frac{\Lambda}{\Psi}}$. For the analysis $X$'s are assumed to be independent. Equation~\ref{eq:spinglass} is the centered Gaussian process on the sphere $\mathcal{S}_{N} = S^{N-1}(\sqrt{N})$ and is equivalent to the Hamiltonian of the $H$-spin spherical spin-glass model. The spherical constraint is captured in Equation~\ref{eq:spherical}. An asymptotic evaluation of the comlexity of spherical $H$-spin spherical spin-glass models via random matrix theory was studied in the literature~\cite{AAC2010} where a precise description of the energy landscape for the Hamiltonians of these models is provided. In this paper we explore a strong connection of the Hamiltonian of these models, originated from physics, and the strongly non-convex loss functions used in deep learning. We use the results of the theoretical analysis of the complexity of spin-glass models~\cite{AAC2010} to gain an understading of the optimization in deep learning.

\begin{figure*}[htp!]
  \center
\includegraphics[width = 2.5in]{Theta_cp.pdf} 
\includegraphics[width = 2.5in]{Theta_lm_sp.pdf}
\caption{Functions $\Theta_H(u)$ and $\Theta_{k,H}(u)$ for $k = \{0,1,\dots,5\}$. Parameter $H$ was set to $H = 3$. Black line: $u = -E_0(H)$, magenda line: $u = -E_{\infty}(H)$.}
\label{fig:Thetas}
\end{figure*}

\section{Theoretical results}
Our theoretical findings are direct consequence of the theoretical analysis of the complexity of spherical spin-glass models of~\cite{AAC2010}. We will first introduce the notation and definitions. 
\begin{definition}
Let $B \subset \mathbb{R}$ be any Borel set and $k$ be an integer such that $0 \leq k < \Lambda$. A random number of critical values of $\mathcal{L}_{\Lambda,H}({\bm w})$ in the set $\Lambda B = \{\Lambda X:x\in B\}$ with index equal to $k$ is
\[\mathcal{C}_{\Lambda,k}(B) = \!\!\!\!\!\!\!\!\!\!\!\!\!\!\sum_{{\bm w}:\nabla \mathcal{L}_{\Lambda,H}({\bm w}) = 0}\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\mathbbm{1}\{\mathcal{L}_{\Lambda\!,H}({\bm w})\!\in\! \Lambda B\}\mathbbm{1}\{i(\nabla^2\mathcal{L}_{\Lambda\!,H}({\bm w})) \!=\! k\},
\]
and a random total number of critical values of $\mathcal{L}_{\Lambda,H}(w)$ in the set $\Lambda B = \{\Lambda X:x\in B\}$ is
\[\mathcal{C}_{\Lambda}(B) = \sum_{{\bm w}:\nabla \mathcal{L}_{\Lambda,H}({\bm w}) = 0}\!\!\!\!\!\!\!\!\!\!\!\!\!\mathbbm{1}\{\mathcal{L}_{\Lambda,H}({\bm w})\!\in\! \Lambda B\},
\]
where $\nabla$ and $\nabla^2$ denote respectively gradient and Hessian restricted to $\mathcal{S}_{\Lambda}$ and $i(\nabla^2\mathcal{L}_{\Lambda,H}(w))$ is the number of negative eigenvalues of the Hessian $\nabla^2\mathcal{L}_{\Lambda,H}$ at ${\bm w}$ also called index of $\nabla^2\mathcal{L}_{\Lambda,H}$ at ${\bm w}$.
\end{definition}
Later in the paper by critical values of the loss function that have non-divering (fixed) index we mean the ones with index non-diverging with $\Lambda$. We will also call them low-index saddle points.

Let us now introduce the number that we will refer to as $E_{\infty}$ and use later on.
\begin{equation}
E_{\infty} = E_{\infty}(H) = 2\sqrt{\frac{H-1}{H}}.
\label{eq:E_inf}
\end{equation}
We will also define two non-decreasing, continuous functions on $\mathbb{R}$, $\Theta_H$ and $\Theta_{k,H}$ as follows
\[\Theta_H(u) = \left \{
  \begin{tabular}{c}
  $\!\!\!\!\frac{1}{2}\log(H\!-\!1) \!-\! \frac{H-2}{4(H-1)} \!-\! I(u)$ $\:\:\:$if$\:\:$$u \!\leq\! -E_{\infty}$\\
  $\!\!\!\!\!\frac{1}{2}\log(H\!-\!1) \!-\! \frac{H-2}{4(H-1)}$ $\:\:\:\:\:\:$if$\:\:$$-E_{\infty} \!\leq\! u \leq 0$\\
  $\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\frac{1}{2}\log(H-1)$ $\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:$if$\:\:$$0 \!\leq\! u$
  \end{tabular}
\right.,
\]
and for any integer $k \geq 0$:
\[\Theta_{k,H}(u) \!=\! \left \{
  \begin{tabular}{c}
  $\!\!\!\!\!\frac{1}{2}\!\log(\!H\!-\!1\!) \!-\! \frac{H\!-\!2}{4(\!H-1\!)} \!-\! (k\!+\!1)I(u)$ if$\:$$u \!\!\leq\!\! -E_{\infty}$\\
  $\!\!\!\!\frac{1}{2}\log(\!H\!-\!1\!) \!-\! \frac{H\!-\!2}{4(\!H-1\!)}$ $\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:\:$if$\:$$u \!\!\geq\!\! -E_{\infty}$
  \end{tabular}
\right.
\]
where 
\[I(u) = -\frac{u}{E_{\infty}^2}\sqrt{u^2 - E_{\infty}^2} - \log(-u + \sqrt{u^2 - E_{\infty}^2}) + \log E_{\infty}.
\]
Note that the maximal values of $\Theta_H(u)$ and $\Theta_{k,H}(u)$ are respectively $\frac{1}{2}\log(H-1)$ and $\frac{1}{2}\log(H-1) - \frac{H-2}{H}$. Figure~\ref{fig:Thetas} captures exemplary plots of the functions $\Theta_H(u)$ and $\Theta_{k,H}(u)$ for $k = 0$. Also note that the following corollary holds.
\begin{corollary}
For all $k > 0$ and $u < -E_{\infty}$, $\Theta_{k,H}(u) < \Theta_{0,H}(u)$.
\label{cor:Theta}
\end{corollary}
Finally, for any integer $k \geq 0$, let $E_k = E_k(H) > 0 $ be defined as the unique solution to 
\[\Theta_{k,H}(-E_k) = 0.
\]
For any fixed $H \geq 3$, the sequence $\{E_k(H)\}_{k\in\mathbb{\Lambda}}$ is strictly decreasing and converges to $E_{\infty}$ as $k \rightarrow \infty$~\cite{AAC2010}. We will now define the ground state energy.

\begin{figure*}[htp!]
  \center
\includegraphics[width = 2.5in]{Distr_cp.pdf} 
\includegraphics[width = 2.5in]{Distr_lm.pdf}
\caption{Distribution of the mean number of critical points and local minima. Parameters $H$ and $\Lambda$ were set to $H = 3$ and $\Lambda = 1000$. Black line: $u = -E_0(H)$, magenda line: $u = -E_{\infty}(H)$, blue line: $u = 0$.}
\label{fig:Distr_cp_lm}
\end{figure*}

\begin{definition}
The ground state energy is the (normalized) minimum of the loss function $\mathcal{L}_{\Psi,c,H}$
\[G^\Psi = \frac{1}{\Lambda}\inf_{{\bm w}\in \mathcal{S}_{\Psi,c}}\mathcal{L}_{\Psi,c,H}({\bm w}).
\]
\end{definition}
Next we provide theorems (resp. Theorem~\ref{thm:lb},~\ref{thm:ub},~\ref{thm:layer}, ~\ref{thm:lmsp} and~\ref{thm:cp}) which are direct consequences of the theoretical findings in~\cite{AAC2010} (resp. Theorem 2.12, 2.14, 2.15, 2.5 and 2.8)  and the boundeness of $c$ and $H$.  
\begin{theorem}
For every $H \geq 3$
\[\liminf_{\Lambda \rightarrow \infty} G^\Psi \geq -E_0(H),
\]
and for $H \geq 4$
\[\liminf_{\Lambda \rightarrow \infty} G^\Psi = -E_0(H) \:\:\:\text{in probability.}
\]
\label{thm:lb}
\end{theorem}
By Theorem~\ref{thm:lb}, for large-size networks it is improbable to find a critical value below level $-\Lambda E_0(H)$.
\begin{theorem}
For an integer $k \geq 0$ and $\epsilon > 0$,
\[\limsup_{\Lambda \rightarrow \infty} \frac{1}{\Lambda^2}\log(\mathbb{P}(\mathcal{C}_{\Lambda,k}(-E_{\infty}(H) + \epsilon,\infty)>0)) < 0
\]
\label{thm:ub}
\end{theorem}
Theorem~\ref{thm:ub} implies that for large-size networks all critical values of the loss function that are of non-diverging index must lie below the threshold $-\Lambda E_{\infty}(H)$. We will refer to this important threshold as an \textit{energy barrier}. Any critical point that lies above this threshold is a high-index saddle point with overwhelming probablity. Theorem~\ref{thm:lb} and~\ref{thm:ub} both imply that for large-size networks all critical values of the loss function that are of non-diverging index must lie in the band $\left(-\Lambda E_0(H),-\Lambda E_{\infty}(H)\right)$.
\begin{theorem}
For $k \geq 0$ and $\epsilon > 0$,
\[\limsup_{\Lambda \rightarrow \infty} \frac{1}{\Lambda^2}\log(\mathbb{P}(\sum_{i=k}^{\infty}\!\mathcal{C}_{\Lambda,i}(-E_k(H) - \epsilon,\infty) \!>\! 0)) \!<\! 0
\]
\label{thm:layer}
\end{theorem}
Theorem~\ref{thm:layer} implies that for large-size networks finding a critical value with index larger or equal to $k$ (for any fixed integer $k$) below energy level $-\Lambda E_k(H)$ is improbable.

The statements of Theorems~\ref{thm:lb},~\ref{thm:ub} and~\ref{thm:layer} unravel a layered structure for the lowest critical values of the loss function of a large-mass (or large-size) deep network, where with overwhelming probability the critical values above the global minimizer (ground state) of the loss function are local minima exclusively. Above the band ($\left(-\Lambda E_0(H),-\Lambda E_1(H)\right)$) with only local minima, there is another one, ($\left(-\Lambda E_1(H),-\Lambda E_2(H)\right)$), where one can only find local minima (critical points of index $0$) and saddle points of index $1$, and above this band there exists another one, ($\left(-\Lambda E_2(H),-\Lambda E_3(H)\right)$), where one can only find local minima and saddle points of index $1$ and $2$, etc. The above-described layered structure of the lowest critical values of the Hamiltonian of the spherical spin glass model was in-detail described in~\cite{AAC2010}, however with no connection to deep learning that instead we explore.

An interesting implication of Theorems~\ref{thm:lb},~\ref{thm:ub} and~\ref{thm:layer} is that recovering the global minimizer when starting from any (local) minima from one of the energy bands above, e.g. $\left(-\Lambda E_i(H),-\Lambda E_{i+1}(H)\right)$, diverges with $\Psi$ since it is bounded below by $\Lambda (E_0(H) - E_i(H))$.

Next we will show the logarithmic asymptotics of the mean number of critical points (the asymptotics of the mean number of critical points can be found in the Supplementary material).

\begin{figure*}[htp!]
  \center
\includegraphics[width = 2.2in]{Distr_lm_sp_li.pdf} 
\includegraphics[width = 2.2in]{Distr_lm_sp_li_zoomed_left.pdf} 
\includegraphics[width = 2.2in]{Distr_lm_sp_li_zoomed_right.pdf} 
\caption{Distribution of the mean number of local minima and low-index saddle points (oryginal and zoomed). Parameters $H$ and $\Lambda$ were set to $H = 3$ and $\Lambda = 1000$. Black line: $u = -E_0(H)$, magenda line: $u = -E_{\infty}(H)$.}
\label{fig:Distr_lm_sp}
\end{figure*}

\begin{theorem}
For all $H \geq 2$ and $k \geq 0$ fixed
\[\lim_{\Lambda \rightarrow \infty}\frac{1}{\Lambda}\log\mathbb{E}[\mathcal{C}_{\Lambda,k}(u)] = \Theta_{k,H}(u).
\]
\label{thm:lmsp}
\end{theorem}
\begin{theorem}
For all $H \geq 2$
\[\lim_{\Lambda \rightarrow \infty}\frac{1}{\Lambda}\log\mathbb{E}[\mathcal{C}_{\Lambda}(u)] = \Theta_{H}(u).
\]
\label{thm:cp}
\end{theorem}
Figure~\ref{fig:Distr_cp_lm} captures exemplary plots of the distributions of the mean number of critical points and local minima and Figure~\ref{fig:Distr_lm_sp} captures exemplary plots of the distributions of the mean number of local minima and low-index saddle points. Both figures clearly show that the local minima and low-index saddle points are located in the band $\left(-\Lambda E_0(H),-\Lambda E_{\infty}(H)\right)$ whereas high-index saddle points can only be found above the energy barrier $-\Lambda E_{\infty}(H)$. Figure~\ref{fig:Distr_lm_sp} also clearly reveals the layered structure for the lowest critical values of the loss function as predicted by the theory.

Note that from Theorem~\ref{thm:lmsp} and Corollary~\ref{cor:Theta} it follows that the number of critical points in the band $\left(-\Lambda E_0(H),-\Lambda E_{\infty}(H)\right)$ increases exponentially as $\Psi$ grows and that local minima dominate over saddle points and this domination also grows exponentially as $\Psi$ grows. Thus for large-size networks (large $\Psi$) the probability of recovering a saddle point in the band $\left(-\Lambda E_0(H),-\Lambda E_{\infty}(H)\right)$, rather than a local minima, goes to $0$.

\bibliographystyle{apalike}
\bibliography{PAPER_AMMLY}

\newpage

\toptitlebar 
{\Large \bf  \centering{Deep-optimization with large networks\\(Supplementary Material)} \par}
\bottomtitlebar

\section{Approximation of 2-spin Spin Glasses by 1-layer Neural Networks}

The Hamiltonian of a H-spin glass is given by

\begin{equation}
 S_H(w) = \sum_{i_1,...,i_H}^N x_{i_1,...,i_H} w_{i_1} \cdot ... \cdot w_{i_H}
\end{equation}
and the output of a deep linear network with $H$ layers by 
\begin{equation}
 Y_H(w) = \sum_{p = (i_1,...,i_H) \in \mathcal{P}} x_{i_1,...,i_H} w_{i_1} \cdot ... \cdot w_{i_H}
\end{equation}

Here $\mathcal{P}$ denotes the set of all paths from inputs to outputs in the network. Let $\mathcal{U} = \{ w_{i_1} \cdot ... \cdot w_{i_H} : 1 \leq i_1,...,i_H \leq N \} $.
Note that the number of terms in the sum $S_H(w)$ is equal to $|\mathcal{U}| = N^H$ and the number of terms in $Y_H(w)$ is equal to $|\mathcal{P}|$.

\begin{definition}
 Let $P_1(w), P_2(w)$ be random polynomials in $w$, where $w \in \mathbb{R}^N$, and let $m_1,m_2$ be the number of nonzero terms in $P_1,P_2$. Assume that all nonzero terms which appear in $P_1$ also appear in $P_2$. 
 We define a measure of similarity between the polynomials as $\Phi(P_1,P_2) = \frac{m_1}{m_2}$.
\end{definition}

\begin{lemma}
Consider the following network $\mathcal{N}$ whose output is given by $Y(w) = \sum \sigma Wx$, where $\sigma$ is a rectified linear unit non-linearity.
Furthermore assume that $rank(W) = k$.
Then $\Phi(Y(w),S(w))  = \frac{1}{4k}$.
\end{lemma}

\begin{proof}
 Assume for simplicity that $W$ is $n \times n$. Since $W$ has rank $k$, it can be written as $W = UV^T$, where $U$ and $V$ have dimension $n \times k$.
 We can therefore reparameterize the system so that the free parameters consist of the entries of $U$ and $V$, which brings the number of parameters to $2kn$. 
 Assume these are reindexed of the form $\{w_1,w_2,...,w_{2kn} \}$.
 A spin glass model with this set of parameters and $H=2$ will have $(2kn)^2=4k^2n^2$ terms in its sum.
 Let us now count the number of unique terms in the polynomial $Y(w)$ which represents our network. 
 The matrix $W = UV^T$ has $n^2$ entries, each of which is of the form $u^Tv$ for some row $u$ of $U$ and $v$ of $V$. 
 Since $u,v \in \mathbb{R}^k$, each entry is the sum of $k$ terms of the form $w_i w_j$. 
 It follows that each entry in the column vector $Wx$ is the sum of $nk$ terms, and hence the output $y$ is the sum of $n^2k$ terms, all of the form $w_iw_jx_{ij}$.
 We thus have $\Phi(Y(w),S(w)) = \frac{n^2k}{4n^2k^2} = \frac{1}{4k}$.
\end{proof}

  In the above example, we can combine pairs of terms of the form $w_iw_jx_{ij} + w_jw_ix_{ji}$ into $w_iw_j(x_{ij}+x_{ji})$. 
  The sum $(x_{ij}+x_{ji})$ has higher variance than the other input terms, but if this is a benign assumption for subsequent results then the ratio of terms becomes $\frac{1}{2k}$ rather than $\frac{1}{4k}$.

\begin{lemma}
 The class of functions which can be learned by networks of the form $y = v^T \sigma Wx$ and $y = \sum \sigma Wx$ is equivalent. 
\end{lemma}

\begin{proof}
 We can show this by simple change of variables. 
 \begin{align*}
  y &= v^T \sigma(Wx) \\
  &= \sum_i v_i \sigma(\sum_j w_{ij} x_j) \\
  &= \sum_i \sigma(\sum_j v_i w_{ij} x_j) \\
  &= \sum_i \sigma(\sum_j w_{ij}' x_j) \\
  &= \sum_i \sigma(W'x)
 \end{align*}

 where $w_{ij}' = v_i w_{ij}$.
\end{proof}

\begin{theorem}
 Let $Y(w)$ be the output of a one-layer linear network, $S(w)$ be the Hamiltonian of a 2-spin spin glass model, and assume that the weights of $Y$ have rank $k$. 
 Then $\Phi(Y(w),S(w)) = \frac{1}{4k}$.
\end{theorem}

\begin{proof}
 This follows directly from the two above lemmas.
\end{proof}

Below, we provide the asymptotics of the mean number of critical points (Theorem~\ref{thm:cpprecise}) and the mean number of local minima (Theorem~\ref{thm:lmspprecise}), which extend Theorem~\ref{thm:lmsp} and Theorem~\ref{thm:cp}. Those results are the consequences of Theorem 2.17. and Corollary 2.18.~\cite{AAC2010} and the boundeness of $c$ and $H$.
\begin{theorem}
For $H \geq 3$, the following holds as $\Lambda \rightarrow \infty$:
\begin{itemize}
\item For $u < -E_{\infty}$\\
\begin{eqnarray*}
\mathbb{E}[\mathcal{C}_{\Lambda}(u)] \!\!\!&=&\!\!\! \frac{h(v)}{\sqrt{2H\pi}}\frac{\exp(I_1(v) - \frac{v}{2}I_1^{'}(v))}{-\Phi^{'}(v) + I_1^{'}(v)}\Lambda^{-\frac{1}{2}}\\
&\cdot& \exp\left(\Lambda\Theta_H(u)\right)(1 + o(1)),
\end{eqnarray*}
where $v = -u\sqrt{\frac{H}{2(H-1)}}$, $\Phi(v) = -\frac{H-2}{2H}v^2$,\\
$h(v) = \left|\frac{v-\sqrt{2}}{v + \sqrt{2}}\right|^{\frac{1}{4}} + \left|\frac{v+\sqrt{2}}{v - \sqrt{2}}\right|^{\frac{1}{4}}$\\
and $I_1(v) = \int_{\sqrt{2}}^{v}\sqrt{|x^2 - 2|}dx$.
\item For $u = -E_{\infty}$\\
\begin{eqnarray*}
\mathbb{E}[\mathcal{C}_{\Lambda}(u)] = \frac{2A(0)\sqrt{2H}}{3(H-2)}\Lambda^{-\frac{1}{3}}\\
\cdot\exp\left(\Lambda\Theta_H(u)\right)(1 + o(1)),
\end{eqnarray*}
where $A$ is the Airy function of first kind.
\item For $u \in (-E_{\infty},0)$\\
\begin{eqnarray*}
\mathbb{E}[\mathcal{C}_{\Lambda}(u)] = \frac{2\sqrt{2H(E_{\infty}^2-u^2)}}{(2-H)\pi u}\\
\cdot\exp\left(\Lambda \Theta_H(u)\right)(1 + o(1)),
\end{eqnarray*}
\item For $u > 0$\\
\begin{eqnarray*}
\mathbb{E}[\mathcal{C}_{\Lambda}(u)] = \frac{4\sqrt{2}}{\sqrt{\pi(H-2)}}\Lambda^{\frac{1}{2}}\\
\cdot\exp\left(\Lambda\Theta_H(0)\right)(1 + o(1)),
\end{eqnarray*}
\end{itemize}
\label{thm:cpprecise}
\end{theorem}
\begin{theorem}
For $H \geq 3$ and $u < -E_{\infty}$, the following holds as $\Lambda \rightarrow \infty$:
\begin{eqnarray*}
\mathbb{E}[\mathcal{C}_{\Lambda,0}(u)] \!\!\!&=&\!\!\! \frac{h(v)}{\sqrt{2H\pi}}\frac{\exp(I_1(v) - \frac{v}{2}I_1^{'}(v))}{-\Phi^{'}(v) + I_1^{'}(v)}\Lambda^{-\frac{1}{2}}\\
&\cdot& \exp\left(\Lambda\Theta_H(u)\right)(1 + o(1)),
\end{eqnarray*}
where $v$, $\Phi$, $h$ and $I_1$ were defined in Theorem~\ref{thm:cpprecise}.
\label{thm:lmspprecise}
\end{theorem}

\end{document}

### 2014-10-15 PAPER_AMMLY.tex
Intro added

@@
 
-\aistatstitle{Connecting deep networks with the spin-glass model}
+\aistatstitle{Connecting large neural networks with the spin-glass model}
 
@@
 \begin{abstract}
-We explore the approximate equivalence of the highly non-convex loss function of a simple model of the fully-connected feed-forward neural network with the Hamiltonian of the spherical spin glass model under a certain assumptions.
-Using the results from the random matrix theory, we demonstrate that for large-size near-symmetric networks the lowest critical values above the global minimum of the loss function are located in a well-defined band and furthermore they form a layered structure.
-We show that the expected number of local minima of the loss function in this band grows exponentially with the size of the network, and at the same time the probability of finding a saddle point in this band diminishes exponentially.
+We explore the approximate equivalence of the highly non-convex loss function of a simple model of the fully-connected feed-forward neural network and the Hamiltonian of the spherical spin-glass model under certain assumptions.
+Using the results from the random matrix theory, we demonstrate that for large-size networks the lowest critical values of the loss function are located in a well-defined narrow band lower-bounded by the global minimum and furthermore they form a layered structure.
+Moreover, finding them outside the band diminishes exponentially with the size of the network.
 We empirically demonstrate that both simulated annealing and SGD converges to the band of the lowest critical values, and furthermore all critical points found there correspond to the same learning quality measured by the test error.
@@
 
+Neural networks are machine learning models used for learning complex and highly non-linear mathematical functions in the context of regression, classification, pattern recognition, clustering, reinforcement learning etc.
+Modern neural networks historically originate from simple early models such as threshold logic~\cite{mcculloch43a}, Hebbian network~\cite{Hebb:1949} and perceptron~\cite{rosenblatt58a} that were followed by more sophisticated models including Hopfield network~\cite{Hopfield:1988:NNP:65669.104422}, Kohonen network~\cite{Kohonen1982}, and Boltzman machines~\cite{Hinton:1986:LRB:104279.104291} (and many others).
+Despite their modeling power, the interest in learning with early neural network significantly weakened when it was shown that they have several limitations including: i) learning limitations such as the inability of single-layer networks to solve the XOR problem~\cite{minsky69perceptrons}, ii) long training time of large networks and proness to overfitting~\cite{JMLR:v15:srivastava14a}, and iii) getting stuck in poor-quality local optima or saddle points while training~\cite{Larochelle:2009:EST:1577069.1577070}.
+Today many of these limitations can be solved with the development of new efficient training strategies (among them backpropagation algorithm~\cite{Werbos:74} which enables to solve the XOR problem), fast GPU-based implementations significantly reducing the training time, and techniques preventing the overfitting such as dropout (e.g.~\cite{JMLR:v15:srivastava14a}).
+Therefore, after a long period of scepticism, the paradigm of learning with neural networks gained significant attention in recent years resulting in many new architectures, such as convolutional networks~\cite{lecun-gradientbased-learning-applied-1998}, recurrent neural networks~\cite{Graves:2009:NCS:1525650.1525782}, deep feedforward neural networks (e.g.~\cite{DBLP:journals/corr/Schmidhuber14} or wide networks~\cite{Huang14}, which basic difference from their early predecessors lies in a much larger parameter space (throughout the paper we refer to the number of network parameters as network size).
+In effect, the optimization problem arising when training these models is highly non-convex with exponentially many critical points.
+Despite the apparent difficulty of this optimization, modern neural network approaches often beat state-of-the-art results on a plethora of learning tasks (pattern recognition~\cite{journals/nn/CiresanMMS12}, brain image segmentation~\cite{NIPS2012_4741}, human pose estimation~\cite{DBLP:journals/corr/TompsonJLB14}, large-scale visual recognition~\cite{sermanet-iclr-14}, transfer learning~\cite{conf/icml/GoodfellowCB12} and many more) which is highly suggestive of their ability to recover high-quality solution to the optimization problem.
+The fundamental question arises: 'Why?'
+
+The paradigm of optimizing a highly non-convex loss function characteristic of modern neural newtorks remains largely ununderstood with a lot of empirical evidence and almost no theoretical justification (the overview of prior work is done in Section~\ref{sec:PriorWork}).
+That results in often perceiving these models as 'black box' tools and rejecting them in favor of significantly simpler models which training is based on solving convex optimization problem.
+Convex optimization is well-understood and nearly-exactly (or exactly) solvable by many standard optimizers with known theoretical convergence guarantees in this setting (some standard results can be found in~\cite{opac-b1104789, ben-tal_nemirovski:2001}).
+The goal of this paper is to provide insights to the paradigm of large-size neural network optimization.
+We establish the connection between the loss function (we focus on hinge loss and absolute loss) of the fully-connected one-output feed-forward neural network of depth $H$ with the Hamiltonian of the $H$-spin spherical spin-glass model.
+We show that the latter can be thought of us an approximator of the loss function of the network.
+This is done in Section~\ref{sec:NNSG}.
+\textcolor{red}{Through the argument of symmetricity and over-parametrization we argue that the approximation factor is small leading to good-quality approximation.} Through the prism of recent findings in random matrix theory~\cite{AAC2010} in Section~\ref{sec:theory} we prove that for large-size networks the local minima and low-index saddle points of the loss function lie within a narrow band lower-bounded by the global minimum and finding them outside the band diminishes exponentially with the size of the network.
+Furthermore, within the band, the lowest critical points form a very well-defined layered structure that we also describe in the paper.
+Finally, recovering the global minimum of the loss function diminishes with network size.
+In the experimental section (Section~\ref{sec:Experiments}) we empirically verify several hypotheses regarding learning with large-size networks:
+\begin{itemize}
+\item For large-size networks local minima are equivalent and correspond to the same quality solution measured by the test error.
+\item Probability of finding a poor quality local minima is non-zero for small-size networks and it exponentially diminishes with the network size.
+\item Finding the global minimum on the training set is not useful in practice as it often leads to overfitting.
+\item The local minima are mostly flat and are characterised by Hessian with mostly zero eigenvalues. This is an indication that large-size networks can be simplified\cite{}.
+\item The number of positive eigenvalues of the Hessian at local minima is invariant to network size.
+\end{itemize}
+The first three hypotheses can be directly justified by our theoretical findings and the last two are provided as corollaries without proof but with strong empirical evidence.
+
+What is new in this paper?
+To the best of our knowledge, this paper is the first work providing a theoretical description of the optimization paradigm with neural networks in the presence of large number of parameters.
+It is also an attempt to make the modern neural network approach more a provable machine learning method and move it away from the 'black-box' shadow.
+We provide new insights explaining why this approach achieve high practical performance supported by the theoretical analysis and empirical verification.
+
+\section{Prior work}
+\label{sec:PriorWork}
+
 \section{Deep network and spin-glass model}
+\label{sec:NNSG}
 
@@
 \includegraphics[width = 2.5in]{Theta_lm_sp.pdf}
-\caption{Functions $\Theta_H(u)$ and $\Theta_{k,H}(u)$ for $k = \{0,1,\dots,5\}$. Parameter $H$ was set to $H = 3$. Black line: $u = -E_0(H)$, magenda line: $u = -E_{\infty}(H)$.}
+\caption{Functions $\Theta_H(u)$ and $\Theta_{k,H}(u)$ for $k = \{0,1,\dots,5\}$. Parameter $H$ was set to $H = 3$. Black line: $u = -E_0(H)$, red line: $u = -E_{\infty}(H)$.}
 \label{fig:Thetas}
@@
 \section{Theoretical results}
+\label{sec:theory}
 Our theoretical findings are direct consequence of the theoretical analysis of the complexity of spherical spin-glass models of~\cite{AAC2010}. We will first introduce the notation and definitions. 
@@
   \center
-\includegraphics[width = 2.5in]{Distr_cp.pdf} 
-\includegraphics[width = 2.5in]{Distr_lm.pdf}
+\includegraphics[width = 3in]{Distr_cp.pdf} 
+\includegraphics[width = 3in]{Distr_lm.pdf}
 \caption{Distribution of the mean number of critical points and local minima.
 Parameters $H$ and $\Lambda$ were set to $H = 3$ and $\Lambda = 1000$.
-Black line: $u = -E_0(H)$, magenda line: $u = -E_{\infty}(H)$, blue line: $u = 0$.}
+Black line: $u = -E_0(H)$, red line: $u = -E_{\infty}(H)$, blue line: $u = 0$.}
 \label{fig:Distr_cp_lm}
@@
 Parameters $H$ and $\Lambda$ were set to $H = 3$ and $\Lambda = 1000$.
-Black line: $u = -E_0(H)$, magenda line: $u = -E_{\infty}(H)$.}
+Black line: $u = -E_0(H)$, red line: $u = -E_{\infty}(H)$.}
 \label{fig:Distr_lm_sp}
@@
 Thus for large-size networks (large $\Psi$) the probability of recovering a saddle point in the band $\left(-\Lambda E_0(H),-\Lambda E_{\infty}(H)\right)$, rather than a local minima, goes to $0$.
+
+\section{Experiments}
+\label{sec:Experiments}
 

### 2014-10-17 PAPER_AMMLY.tex
Introand theory done

@@
 Today many of these limitations can be solved with the development of new efficient training strategies (among them backpropagation algorithm~\cite{Werbos:74} which enables to solve the XOR problem), fast GPU-based implementations significantly reducing the training time, and techniques preventing the overfitting such as dropout (e.g.~\cite{JMLR:v15:srivastava14a}).
-Therefore, after a long period of scepticism, the paradigm of learning with neural networks gained significant attention in recent years resulting in many new architectures, such as convolutional networks~\cite{lecun-gradientbased-learning-applied-1998}, recurrent neural networks~\cite{Graves:2009:NCS:1525650.1525782}, deep feedforward neural networks (e.g.~\cite{DBLP:journals/corr/Schmidhuber14} or wide networks~\cite{Huang14}, which basic difference from their early predecessors lies in a much larger parameter space (throughout the paper we refer to the number of network parameters as network size).
+Therefore, after a long period of scepticism, the paradigm of learning with neural networks gained significant attention in recent years resulting in many new architectures, such as convolutional networks~\cite{lecun-gradientbased-learning-applied-1998}, recurrent neural networks~\cite{Graves:2009:NCS:1525650.1525782}, deep feedforward neural networks (e.g.~\cite{DBLP:journals/corr/Schmidhuber14} or wide networks~\cite{Huang14}, where the most fundamental difference between them and their early predecessors lies in a much larger parameter space (throughout the paper we refer to the number of network parameters as network size).
 In effect, the optimization problem arising when training these models is highly non-convex with exponentially many critical points.
@@
 We establish the connection between the loss function (we focus on hinge loss and absolute loss) of the fully-connected one-output feed-forward neural network of depth $H$ with the Hamiltonian of the $H$-spin spherical spin-glass model.
-We show that the latter can be thought of us an approximator of the loss function of the network.
-This is done in Section~\ref{sec:NNSG}.
-\textcolor{red}{Through the argument of symmetricity and over-parametrization we argue that the approximation factor is small leading to good-quality approximation.} Through the prism of recent findings in random matrix theory~\cite{AAC2010} in Section~\ref{sec:theory} we prove that for large-size networks the local minima and low-index saddle points of the loss function lie within a narrow band lower-bounded by the global minimum and finding them outside the band diminishes exponentially with the size of the network.
+We show that the latter can be thought of us an approximator of the loss function of the network under certain assumptions which we also discuss, and furthermore we provide the theoretical guarantee of the quality of this approximation.
+Through the prism of recent findings in random matrix theory~\cite{AAC2010} in Section~\ref{sec:theory} we prove that for large-size networks the local minima and low-index saddle points of the loss function lie within a narrow band lower-bounded by the global minimum and finding them outside the band diminishes exponentially with the size of the network.
 Furthermore, within the band, the lowest critical points form a very well-defined layered structure that we also describe in the paper.
@@
 In the experimental section (Section~\ref{sec:Experiments}) we empirically verify several hypotheses regarding learning with large-size networks:
+\vspace{-0.05in}
 \begin{itemize}
 \item For large-size networks local minima are equivalent and correspond to the same quality solution measured by the test error.
+\vspace{-0.05in}
 \item Probability of finding a poor quality local minima is non-zero for small-size networks and it exponentially diminishes with the network size.
+\vspace{-0.05in}
 \item Finding the global minimum on the training set is not useful in practice as it often leads to overfitting.
-\item The local minima are mostly flat and are characterised by Hessian with mostly zero eigenvalues. This is an indication that large-size networks can be simplified\cite{}.
+\vspace{-0.05in}
+\item The local minima are mostly flat and are characterised by Hessian with mostly zero eigenvalues. This is an indication that large-size networks can be simplified.
+\vspace{-0.05in}
 \item The number of positive eigenvalues of the Hessian at local minima is invariant to network size.
 \end{itemize}
+\vspace{-0.05in}
 The first three hypotheses can be directly justified by our theoretical findings and the last two are provided as corollaries without proof but with strong empirical evidence.
@@
 Furthermore, $w_{i,j}^{(k)}$ is the weight of the $k^{\text{th}}$ segment of path indexed with $(i,j)$ which connects layer $(k-1)^{st}$ with layer $k^{\text{th}}$ of the network.
-Note that each path corresponds to a certain set of $H$ weights, which we refer to as a \textit{configuration of weights}.
+Note that each path corresponds to a certain set of $H$ weights, which we refer to as a \textit{configuration of weights}, which are multiplied by each other.
 Random variable $A_{i,j}$ denotes whether path $(i,j)$ is active ($A_{i,j} = 1$) or not ($A_{i,j} = 0$).
@@
 
-There exists a lower- and upper-bound on the size of the network that depends on the mass of the network as captured in Theorem~\ref{thm:arge}.
+There mass and the size of the network depend on each other as captured in Theorem~\ref{thm:arge}.
 \begin{theorem}
-The size of the network is bounded as follows
+Let $\Psi$ be the mass of the network, $d$ be the number of network inputs and $H$ be the depth of the network. The size of the network is bounded as
 \[\Psi^2\frac{1}{d} \geq \Lambda \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}}.
@@
 \end{theorem}
-\begin{proof}
-First we will prove the lower-bound. By the inequality between arithmetic and geometric mean the mass and the size of the network are connected as follows
-\[\Lambda \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{n_0n_H}} = \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}}
-\]
-The upper-bound can be shown as follows
-\[\Lambda \leq \prod_{i=0}^{H-1}n_in_{i+1} = \frac{\Psi^2}{n_0n_H} = \Psi^2\frac{1}{d}.
-\]
-\end{proof}
+
+In the rest of this section we will be establishing a connection between the loss function of the neural network and the Hamiltonian of the spin-glass model.
+Under certain assumptions, that will be introduced and discussed, spin-glass model can be though of as a network approximator.
+We will also provide the measure of quality of this approximation.
+All proofs are deferred to the Supplementary material.
 
@@
 Let $\mathcal{W} = \{w_1,w_2,\dots,w_{\Lambda}\}$ be the set of all weights of the network.
-Furthermore let $\mathcal{A}_{\Lambda}$ denote the set of all $H$-length configuration of weights chosen from $W$.
-Note that the size of $\mathcal{A}_{\Lambda}$ is $\Lambda^H$.
+Furthermore let $\mathcal{A}_{\Lambda}$ denote the set of all $H$-length configuration of weights chosen from $\mathcal{W}$ (order of weights in a configuration does matter).
+Note that the size of $\mathcal{A}_{\Lambda}$ is therefore $\Lambda^H$.
 Also let $\mathcal{B}$ be a set such that each element correspond to the single configuration of weights from Equation~\ref{eq:befrein}, thus $\mathcal{B} = \{(w_{1,1}^1,w_{1,1}^2,\dots,w_{1,1}^H),(w_{1,2}^1,w_{1,2}^2,\dots,w_{1,2}^H),\dots,\\(w_{n_0,\gamma}^1,w_{n_0,\gamma}^2,\dots,w_{n_0,\gamma}^H)\}$, where every single weight comes from set $\mathcal{W}$.
 Note that in general there might exist elements in $\mathcal{A}_{\Lambda}$ that will never appear in $\mathcal{B}$ and also some elements in $\mathcal{A}_{\Lambda}$ may appear in $\mathcal{B}$ multiple times.
-Thus Equation~\ref{eq:befrein} can be equivalently restated as
+Thus Equation~\ref{eq:befrein} can be equivalently written as
 \[Y \!=\!
@@
 \]
-For our theoretical analysis we also assume that $X$'s and also $Z$'s are independent and furthermore that $X$'s are identically distributed such that $X_{i_1,i_2,\dots,i_H}^{(c)}\sim\mathcal{N}(0,1)$.
+For our theoretical analysis we assume that $X$'s are independent from each other and so are $Z$'s.
+This assumption is simplistic, yet pervasively used in machine learning theory (plethora of decoupling strategies are discussed in~\cite{opac-b1095246}).
+Let $X$'s be identically distributed such that $X_{i_1,i_2,\dots,i_H}^{(c)}\sim\mathcal{N}(0,1)$.
 Therefore $Z_{i_1,i_2,\dots,i_H}\sim\mathcal{N}(0,1)$.
@@
 \end{equation}
-Let instead the number of uniqe weghts in a network be changed from $\Lambda$ to $s$ where $s \leq \Lambda$. Consider another expression
+Consider a family of networks which have the same graph of connections as network $\mathcal{N}$ but different edge weighting such that they only have $s$ unique weights and $s \leq \Lambda$.
+It was recently shown~\cite{NIPS2013_5025,DBLP:journals/corr/DentonZBLF14} that for large-size networks large number of network parameters (according to~\cite{NIPS2013_5025} even up to $95\%$) are reduntant and can either be learned from a very small set of unique parameters or even not learned at all with almost no loss in prediction accuracy.
+In our experimental section we also demonstrate the empirical evidence of the overparametrization of neural networks.
+It is therefore well-justified to \textit{assume redunancy in network parametrization} where $s$ is the number of unique (non-redundant) parameters.
+
+\begin{definition}
+A network $\mathcal{M}$ which has the same graph of connections as $\mathcal{N}$ and the number of unique weights $s$ satisfying $s \leq \Lambda$ is called a $(s,\epsilon)$-\textit{reduction image} of $\mathcal{N}$ for some $\epsilon \in [0,1]$ if the prediction accuracy of $\mathcal{N}$ and $\mathcal{M}$ differ by no more than $\epsilon$ (thus they classify at most $\epsilon$ fraction of data points differently).
+\end{definition}
+
+\begin{theorem}
+Let $\mathcal{N}$, whose output is $Y_{\Lambda}$, be the neural network predicting $1$ with probability $p$ and $-1$ otherwise.
+Let $\mathcal{M}$ be its $(s,\epsilon)$-reduction image for some $s \leq \Lambda$ and $\epsilon \in [0,1]$.
+Then
+\[corr(sign(Y_s),sign(Y_{\Lambda})) \geq \frac{2p(1 \!-\! p \!+\! \epsilon) \!-\! \epsilon}{2\sqrt{(p \!+\! \epsilon)(1 \!-\! p \!+\! \epsilon)p(1 \!-\! p)}},
+\]
+where $corr$ denotes the correlation defined as $corr(A,B) = \frac{\mathbb{E}[(A - \mathbb{E}[A]])(B - \mathbb{E}[B]])}{std(A)std(B)}$, $std$ is the standard deviation and $sign(\cdot)$ denotes the sign of prediction ($sign(Y_s)$ and $sign(Y_{\Lambda})$ are both random).
+\label{thm:redun}
+\end{theorem}
+
+The assumption of the redundancy of parameters implies that one can preserve $\epsilon$ to be close to $0$ even with $s << \Lambda$.
+
+Finally we assume that unique weights are close to being evenly distributed on the graph of connections of network $\mathcal{M}$.
+We call this assumption a \textit{uniformity assumption} (note it is analogous to the maximum entropy assumption).
+This assumption is in general consistent with the approach in~\cite{NIPS2013_5025}.
+To be more specific, this assumption implies that there exists some bounded non-negative constant $C$ such that for all $(i_1,i_2,\dots,i_H):i_1,i_2,\dots,i_H \in \{1,2,\dots,H\}$ and some $\delta \in [0,1]$ the following holds
+\begin{equation}
+(1-\delta)C\frac{\Psi}{\Lambda^H} \leq r_{i_1,i_2,\dots,i_H} \leq (1+\delta)C\frac{\Psi}{\Lambda^H},
+\label{eq:uniform}
+\end{equation}
+where the factor $\frac{\Psi}{\Lambda^H}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus every node has equal probability of being adjacent to an edge with any of the unique weights) it holds that $r_{i_1,i_2,\dots,i_H} = \frac{\Psi}{\Lambda^H}$.
+Note that this condition can be sattified with small $\delta$ (close to $0$) if $s$ is sufficiently small.
+
+Consider therefore an expression as follows
 \begin{equation}
@@
 \end{equation}
-which can be thought of as an output of some network $\hat{\mathcal{N}}$ where the weights are still chosen from $\mathcal{A}$ but there are only $s$ unique weights in $\mathcal{A}$ and the remaining $(\Lambda-s)$ weights are repetitions, and furthermore every $H$ - length configuration of weights chosen from $\mathcal{A}$ is equally likely.
-We will refer to this expression soon.
-\textcolor{red}{Draw an example}.
+which can be thought of as an output of some network $\mathcal{M}$ where the weights are still chosen from $\mathcal{A}$ but there are only $s$ unique weights in $\mathcal{A}$ among the total of $\Lambda$ weights, and furthermore every $H$ - length configuration of weights chosen from $\mathcal{A}$ is equally likely.
+Then the following theorem (Theorem~\ref{thm:unif}) captures the connection between $\hat{Y}_s$ and $Y_{\Lambda}$.
 
-\textcolor{red}{We assume that there exists hidden relations between weights that the architecture is not reflecting and that are strictly data-dependent.}Let us now slowly introduce the notion of $(s,\epsilon)$ - realizability.
-Consider a family of networks $\{\mathcal{N}^{'}\}_s$ which have the same graph of connections as the network $\mathcal{N}$ but different edge weighting such that they only have $s$ unique weights and $s \leq \Lambda$.
-Also we require that for any two networks where one of them belongs to set $\{\mathcal{N}^{'}\}_{s_1}$ and produces output $Y_{s_1}$ and the other belongs to set $\{\mathcal{N}^{'}\}_{s_2}$ and produces output $Y_{s_2}$ the following holds
-\begin{equation}
-corr(Y_{s_1},\hat{Y}_{s_1}) \geq corr(Y_{s_2},\hat{Y}_{s_2}),
-\label{eq:condition}
-\end{equation}
-where $corr$ denotes the correlation defined as $corr(A,B) = \frac{\mathbb{E}[(A - \mathbb{E}[A]])(B - \mathbb{E}[B]])}{std(A)std(B)}$, where $std$ is the standard deviation, and $s_1 \leq s_2$.
-\textcolor{red}{Intuitively condition in Equation~\ref{eq:condition} seems natural to sattisfy as with smaller $s$ more configurations appearing in $\hat{Y}_s$ should also appear in $Y_s$.
-Draw an example}.
+\begin{theorem}
+Under the uniformity assumption of Equation~\ref{eq:uniform}, random variable $\hat{Y}_s$ in Equation~\ref{eq:approx} and random variable $Y_{\Lambda}$ in Equation~\ref{eq:befapprox} sattisy the following
+\[corr(\hat{Y}_s,Y_{\Lambda}) \geq \sqrt{\frac{1-\delta}{1+\delta}}.
+\]
+\label{thm:unif}
+\end{theorem}
 
-Furthermore, for a given $s \in \{1,2,\dots,\Lambda\}$ let $\epsilon_s$ be defined
-\[\epsilon_s = \max_{\mathcal{M} \in \{\mathcal{N}^{'}\}_s}[\min(1-corr(Y_s,Y_{\Lambda}),1-corr(Y_s,\hat{Y}_s))],
-\] 
-where $Y_s$ is the output of network $\mathcal{M}$ and $\min(1-corr(Y_s,Y_{\Lambda}),1-corr(Y_s,\hat{Y}_s))$ denotes the smallest of two values: $1-corr(Y_s,Y_{\Lambda})$ and $1-corr(Y_s,\hat{Y}_s)$.
-We will now define the correlation factor and the symmetry factor of a network $\mathcal{N}$.
-\textcolor{red}{Typically for large networks small $s$ is sufficient to achieve small $\epsilon_s$.}
-\begin{definition}
-A correlation factor $\kappa$ of a network $\mathcal{N}$ is
-\[\kappa = 1 - \min_{i \in \{1,2,\dots,\Lambda\}} \epsilon_i
-\]
-and a symmetry factor $s$ of a network $\mathcal{N}$ is
-\[s = \arg\min_{i \in \{1,2,\dots,\Lambda\}} \epsilon_i.
-\]
-A network $\mathcal{N}$ with correlation factor $\kappa$ and symmetry factor $s$ will be called $(s,\kappa)$-realizable.
-\end{definition}
-We will now define the approximation of the output of a network $\mathcal{N}$.
-\begin{definition}
-$\hat{Y}$ is a $\delta$-approximation of the output $Y_{\Lambda}$ of network $\mathcal{N}$ if
-\[corr(\hat{Y},Y_\Lambda) \geq 1-\delta.
-\]
-\end{definition}
-The next theorem captures that $\hat{Y}_s$ from Equation~\ref{eq:approx} is a $(2\kappa^2-1)$ - approximation of $Y_{\Lambda}$.
-\begin{theorem}
-Let $\mathcal{N}$ be a $(s,\kappa)$-realizable network producing the output given in Equation~\ref{eq:befapprox}, for some $\kappa \in [-1,1]$ and $s \in \{1,2,\dots,\Delta\}$.
-Then $Y_s$ given in Equation~\ref{eq:approx} is the $2(1-\kappa^2)$ - approximation of the output of the network $\mathcal{N}$.
-\end{theorem}
-\begin{proof}
-From the fact that $\mathcal{N}$ is $(s,\kappa)$-realizable it follows that 
-\[corr(Y_s,Y_{\Lambda}) \geq \kappa \:\:\:\text{and}\:\:\:corr(Y_s,\hat{Y}_s) \geq \kappa
-\]
-Furthermore, by the property of the correlations
-\begin{eqnarray*}
-corr(Y_{\Lambda},\hat{Y}_s) \!\!\!\!\!&\geq&\!\!\!\!\! corr(Y_{\Lambda},Y_s)corr(Y_{\Lambda},\hat{Y}_s)\\
-&-&\!\!\!\!\! \sqrt{(1 \!-\! corr(Y_{\Lambda},Y_s)^2)(1 \!-\! corr(Y_{\Lambda},\hat{Y}_s)^2)}\\
-&=&2\kappa^2-1
-\end{eqnarray*}
-\end{proof}
-
-\textcolor{red}{The property of a symmetry of a network can be thought of as an assumption on the architecture of the network since it imposes the constraint of having many repetitions of the same set of weights in the network evenly distributed in the network graph so that the set of all paths in the network cover all possible configuration of weights evenly.
-However note that for very large-size networks, the symmetry assumption is easier and more natural to sattisfy leading to smaller values of $\epsilon$.
-Consider for instance constructing the $\epsilon$-approximation of $Y$ by first dyscretizing the weights of the oryginal network into $b$ bins.
-The repetitions of weights occur more frequently now without hurting much the network performance.
-Note also that in particular in case of a very deep and wide architectures, small values of $b$ are sufficient to achieve two goals simultaneously: well-approximate complex functions and guarantee near-symmetry of a network.}
-
-Next we will consider two frequently used loss functions, absolute loss and hinge loss, where we use $\hat{Y}_s$ as an approximator to the ouput $Y_{\Lambda}$ of a network.
+We will refer to $\hat{Y}_s$ as an $(s,\epsilon,\delta)$-\textit{approximator} of $Y_{\Lambda}$, where the quality of this approximation is captured in Theorems~\ref{thm:redun} and~\ref{thm:unif}.
+Intuitively, for large-size networks (our analysis in Section~\ref{sec:theory} considers $\Lambda \rightarrow \infty$) one would expect $s$ to be small enough to simultaneously guarantee sufficiently small (close to $0$) $\delta$ and preserve good accuracy (small $\epsilon$).
+\textcolor{red}{That is because large networks have significantly more modelling power thus small $s$ is a natural form of controlling the overfitting.
+Besides then the data is mapped to a higher dimensional space.} Next we will consider two frequently used loss functions, absolute loss and hinge loss, where we approximate $Y_{\Lambda}$ with $\hat{Y}_s$.
 
@@
   \center
-\includegraphics[width = 3in]{Distr_cp.pdf} 
-\includegraphics[width = 3in]{Distr_lm.pdf}
+\includegraphics[width = 2.5in]{Distr_cp.pdf} 
+\includegraphics[width = 2.5in]{Distr_lm.pdf}
 \caption{Distribution of the mean number of critical points and local minima.
@@
 
+\section{Proof of Theorem~\ref{thm:arge}}
+\begin{proof}
+First we will prove the lower-bound. By the inequality between arithmetic and geometric mean the mass and the size of the network are connected as follows
+\[\Lambda \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{n_0n_H}} = \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}}
+\]
+The upper-bound can be shown as follows
+\[\Lambda \leq \prod_{i=0}^{H-1}n_in_{i+1} = \frac{\Psi^2}{n_0n_H} = \Psi^2\frac{1}{d}.
+\]
+\end{proof}
+
+\section{Proof of Theorem~\ref{thm:redun}}
+\begin{proof}
+Consider two random variables $Z_s = sign(Y_s)$ and $Z_{\Lambda} = sign(Y_{\Lambda})$, where the first one considers the sign of prediction of network $\mathcal{N}$ and the latter considers the sign of prediction of network $\mathcal{M}$.
+Let $\mathcal{X}^{+}$ denote the set of data points for which $\mathcal{N}$ predicts $+1$ and let $\mathcal{X}^{-}$ denote the set of data points for which $\mathcal{N}$ predicts $-1$ ($\mathcal{X}^{+} \cup \mathcal{X}^{-} = \mathcal{X}$, where $\mathcal{X}$ is the entire dataset).
+Also let $p = \frac{|\mathcal{X}^{+}|}{|\mathcal{X}|}$.
+Furthermore, let $\mathcal{X}_{\epsilon}^{-}$ denote the dataset for which $Z_{\Lambda} = +1$ and $Z_s = -1$ and $\mathcal{X}_{\epsilon}^{+}$ denote the dataset for which $Z_{\Lambda} = -1$ and $Z_s = +1$, where $\frac{|\mathcal{X}_{\epsilon}^{+}| + |\mathcal{X}_{\epsilon}^{-}|}{\mathcal{X}} = \epsilon$.
+Also let $\epsilon^{+} = \frac{|\mathcal{X}_{\epsilon}^{+}|}{\mathcal{X}}$ and $\epsilon^{-} = \frac{|\mathcal{X}_{\epsilon}^{-}|}{\mathcal{X}}$.
+Therefore
+\[Z_{\Lambda} \!=\! \left \{
+  \begin{tabular}{c}
+  $1$ \:\:if $x \in \mathcal{X}^{+}$\\
+  \!\!\!\!$-1$ \:\:if $x \in \mathcal{X}^{-}$
+  \end{tabular}
+\right.
+\]
+and
+\[Z_s \!=\! \left \{
+  \begin{tabular}{c}
+  $1$ \:\:if $x \in \mathcal{X}^{+} \cup \mathcal{X}_{\epsilon}^{+}  \setminus \mathcal{X}_{\epsilon}^{-}$\\
+  \!\!\!$-1$ \:\:if $x \in \mathcal{X}^{-} \cup \mathcal{X}_{\epsilon}^{-} \setminus \mathcal{X}_{\epsilon}^{+}$.
+  \end{tabular}
+\right.
+\]
+One can compute that $\mathbb{E}[Z_{\Lambda}] = 2p-1$, $\mathbb{E}[Z_s] = 2(p + \epsilon^{+} - \epsilon^{-}) - 1$, $\mathbb{E}[Z_sZ_{\Lambda}] = 1$, $std(Z_s) = 2\sqrt{p(p-1)}$, and finally $std(Z_\Lambda) = 2\sqrt{(p + \epsilon^{+} - \epsilon^{-})(p + \epsilon^{+} - \epsilon^{-} - 1)}$.
+Thus we obtain
+\begin{eqnarray*}
+&&corr(sign(Y_s),sign(Y_{\Lambda})) = corr(Z_s,Z_{\Lambda})\\
+&=& \frac{\mathbb{E}[Z_sZ_{\Lambda}] - \mathbb{E}[Z_s]\mathbb{E}[Z_{\Lambda}]}{std(Z_s)std(Z_{\Lambda})}\\
+&=& \frac{1 - (2(p + \epsilon^{+} - \epsilon^{-}) - 1)(2p-1)}{4\sqrt{(p + \epsilon^{+} - \epsilon^{-})(p + \epsilon^{+} - \epsilon^{-} - 1)p(p-1)}}\\
+&=& \frac{2p + 2(1-2p)(p + \epsilon^{+} - \epsilon^{-})}{4\sqrt{(p + \epsilon^{+} - \epsilon^{-})(1 - p - \epsilon^{+} + \epsilon^{-})p(1 - p)}}\\
+&\geq& \frac{p + (1-2p)(p - \epsilon)}{2\sqrt{(p + \epsilon)(1 - p + \epsilon)p(1 - p)}}\\
+&=& \frac{2p(1 - p + \epsilon) - \epsilon}{2\sqrt{(p + \epsilon)(1 - p + \epsilon)p(1 - p)}}\\
+\end{eqnarray*}
+\end{proof}
+
+\section{Proof of Theorem~\ref{thm:redun}}
+\begin{proof}
+Note that $\mathbb{E}[\hat{Y}_s] = 0$ and $\mathbb{E}[Y_{\Lambda}] = 0$. Furthermore
+\[\mathbb{E}[\hat{Y}_sY_{\Lambda}] = q^2\rho^2\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}r_{i_1,i_2,\dots,i_H}}\prod_{k = 1}^{H}w_{i_k}^2
+\]
+and
+\[std(\hat{Y}_s) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2}
+\]
+\[std(Y_{\Lambda}) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2}.
+\]
+Therefore
+\begin{eqnarray*}
+&&\!\!\!\!\!\!\!\!\!corr(\hat{Y}_s,Y_{\Lambda})\\ 
+&\!\!\!\!\!\!\!\!\!=&\!\!\!\!\!\!\!
+\frac{\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}r_{i_1,\dots,i_H}}\prod_{k = 1}^{H}w_{i_k}^2}{\sqrt{\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2\right)\!\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!r_{i_1,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2\right)}}\\
+&\!\!\!\!\!\!\!\!\geq& \sqrt{\frac{1-\delta}{1+\delta}}, 
+\end{eqnarray*}
+where the last inequality is the direct consequence of the uniformity assumption of Equation~\ref{eq:uniform}.
+\end{proof}
+
+\begin{comment}
 \section{Approximation of 2-spin Spin Glasses by 1-layer Neural Networks}
@@
 \end{proof}
+\end{comment}
 

### 2014-10-19 PAPER_AMMLY.tex
Prior Work added

@@
 
-\aistatstitle{Connecting large neural networks with the spin-glass model}
+\aistatstitle{Complexity of large neural networks}
 
@@
 We explore the approximate equivalence of the highly non-convex loss function of a simple model of the fully-connected feed-forward neural network and the Hamiltonian of the spherical spin-glass model under certain assumptions.
-Using the results from the random matrix theory, we demonstrate that for large-size networks the lowest critical values of the loss function are located in a well-defined narrow band lower-bounded by the global minimum and furthermore they form a layered structure.
+Using the results from the random matrix theory, we study the complexity of neural networks and prove that for large-size networks the lowest critical values of the loss function are located in a well-defined narrow band lower-bounded by the global minimum and furthermore they form a layered structure.
 Moreover, finding them outside the band diminishes exponentially with the size of the network.
-We empirically demonstrate that both simulated annealing and SGD converges to the band of the lowest critical values, and furthermore all critical points found there correspond to the same learning quality measured by the test error.
+We empirically demonstrate that both simulated annealing and SGD converges to the band of the lowest critical values, and furthermore all critical points found there are local minima and correspond to the same high learning quality measured by the test error.
+This emphasizes a major difference between large- and small-size networks where for the latter poor quality local minima have non-zero probability of being recovered.
+Simultaneously we prove that recovering the global minimum diminishes with the network size and that it is in practice irrelevant as global minimum often leads to data overfitting.
 \end{abstract}
@@
 That results in often perceiving these models as 'black box' tools and rejecting them in favor of significantly simpler models which training is based on solving convex optimization problem.
-Convex optimization is well-understood and nearly-exactly (or exactly) solvable by many standard optimizers with known theoretical convergence guarantees in this setting (some standard results can be found in~\cite{opac-b1104789, ben-tal_nemirovski:2001}).
-The goal of this paper is to provide insights to the paradigm of large-size neural network optimization.
+Convex optimization problems due to having no local optima are well-understood and nearly-exactly (or exactly) solvable by many standard efficient optimizers with known theoretical convergence guarantees in this setting (some standard results can be found in~\cite{opac-b1104789, ben-tal_nemirovski:2001}).
+The goal of this paper is to provide insights to the paradigm of large-size neural network optimization where the problem is highly non-convex.
 We establish the connection between the loss function (we focus on hinge loss and absolute loss) of the fully-connected one-output feed-forward neural network of depth $H$ with the Hamiltonian of the $H$-spin spherical spin-glass model.
 We show that the latter can be thought of us an approximator of the loss function of the network under certain assumptions which we also discuss, and furthermore we provide the theoretical guarantee of the quality of this approximation.
-Through the prism of recent findings in random matrix theory~\cite{AAC2010} in Section~\ref{sec:theory} we prove that for large-size networks the local minima and low-index saddle points of the loss function lie within a narrow band lower-bounded by the global minimum and finding them outside the band diminishes exponentially with the size of the network.
+Through the prism of recent findings in random matrix theory~\cite{AAC2010}, in Section~\ref{sec:theory} we study the complexity, i.e.
+the exponential behavior of the mean number of critical points (in total and of given index), of neural networks.
+We prove that for large-size networks the local minima and low-index saddle points of the loss function lie within a narrow band lower-bounded by the global minimum and finding them outside the band diminishes exponentially with the size of the network.
 Furthermore, within the band, the lowest critical points form a very well-defined layered structure that we also describe in the paper.
@@
 The first three hypotheses can be directly justified by our theoretical findings and the last two are provided as corollaries without proof but with strong empirical evidence.
+We finally conclude the paper with brief discussion of our results and future research directions in Section~\ref{sec:ConandFutWork}.
 
@@
 \label{sec:PriorWork}
+
+Machine learning problems are most often formulated as optimization problems, majority of which are convex.
+It is often the case however that introducing non-convextiy into the model results in better practical performance~\cite{Do:2012:RBM:2503308.2503355, Bengio+chapter2007}.
+A typical examples of models giving rise to non-convex problems are neural networks, mixture models, models exploring products of parameters or those with complex non-linearities imposed on parameters.
+Better expressiveness of those models come with a price: the landscape of their objective functions is not-well understood as it contains several local optima.
+Thus those models typically are provided with no theoretical description.
+
+To the best of our knowledge the recent work of~\cite{DBLP:journals/corr/DauphinPGCGB14} is the first one to explore the statistical properties of neural network error surfaces through the prism of statistical physics and random matrix theory.
+In particular these theoretical works~\cite{Bray2007,Fyodorov2007,Baldi:1989:NNP:70359.70362,wigner_semicircle} suggest the existence of a certain structure of critical points of random Gaussian error functions on high dimensional continuous spaces.
+They imply that critical points which error is much higher than the global minimum are exponentially likely to be saddle points with many negative and approximate plateau directions whereas all local minima are likely to have an error very close to that of the global minimum (these results are conveniently reviewed in~\cite{DBLP:journals/corr/DauphinPGCGB14}).
+The work of~\cite{DBLP:journals/corr/DauphinPGCGB14} establishes a strong connection between neural networks and the theory of random Gaussian fields through an empirical evaluation by providing an experimental evidence that the cost function of neural networks exhibits the same properties as the Gaussian error functions on high dimensional continuous spaces.
+Nevertheless they provide no theortical justification for the existence of this connection which instead we provide in this paper.
+
+This work is inspired by the recent advances in random matrix theory and the work of~\cite{AAC2010} and~\cite{AAC2013}.
+The authors of these works provided an asymptotic evaluation of the complexity of the spherical spin-glass model (the spin-glass model originates from the condensed matter physics where it is used to represent a magnet with irregularily aligned spins).
+They discovered and mathematically proved the existence of a layered structure of the low critical values for the model's Hamiltonian which in fact is a Gaussian process.
+Their results are not discussed in details here as it will be done in Section~\ref{sec:theory} in the context of neural networks.
+We build the bridge between their findings and neural networks and show that the objective function used by neural network is analogous to the Hamiltonian of the spin-glass model and thus their landscapes share the same properties.
+We emphasize that the connection between spin-glass models and neural networks was already explored back in the past (a summary can be found in~\cite{Dotsenko1995}).
+In example in~\cite{PhysRevA.32.1007} the authors showed that the long-term behavior of certain neural network models are governed by the statistical mechanism of infinite-range Ising spin-glass Hamiltonians.
+Another work~\cite{0305-4470-30-23-009} examined the nature of the spin-glass transition in the Hopfield neural network model.
+None of these works however make the attempt to explain the paradigm of optimizing the highly non-convex neural network objective function through the prism of spin-glass theory and thus in this respect our approach is very novel.
 
@@
 
+section{Conclusion and Future Work}
+\label{sec:ConandFutWork}
+
 \bibliographystyle{apalike}

### 2014-10-19 PAPER_AMMLY.tex
Making space for Experiments

@@
 Nevertheless they provide no theortical justification for the existence of this connection which instead we provide in this paper.
+\textcolor{red}{We should comment why saddle-point problem in not a problem for us.}
 
@@
 
-\begin{figure*}[htp!]
-  \center
-\includegraphics[width = 2.5in]{Theta_cp.pdf} 
-\includegraphics[width = 2.5in]{Theta_lm_sp.pdf}
-\caption{Functions $\Theta_H(u)$ and $\Theta_{k,H}(u)$ for $k = \{0,1,\dots,5\}$. Parameter $H$ was set to $H = 3$. Black line: $u = -E_0(H)$, red line: $u = -E_{\infty}(H)$.}
-\label{fig:Thetas}
-\end{figure*}
-
 \section{Theoretical results}
@@
 Also note that the following corollary holds.
+
+\begin{figure}[h]
+  \center
+\includegraphics[width = 1.6in]{Theta_cp.pdf}
+\includegraphics[width = 1.6in]{Theta_lm_sp.pdf}
+\vspace{-0.3in}
+\caption{Functions $\Theta_H(u)$ and $\Theta_{k,H}(u)$ for $k = \{0,1,\dots,5\}$.
+Parameter $H$ was set to $H = 3$.
+Black line: $u = -E_0(H)$, red line: $u = -E_{\infty}(H)$.
+Figure must be read in color.}
+\label{fig:Thetas}
+%\vspace{-0.05in}
+\end{figure}
+
 \begin{corollary}
@@
 
-\begin{figure*}[htp!]
-  \center
-\includegraphics[width = 2.5in]{Distr_cp.pdf} 
-\includegraphics[width = 2.5in]{Distr_lm.pdf}
-\caption{Distribution of the mean number of critical points and local minima.
-Parameters $H$ and $\Lambda$ were set to $H = 3$ and $\Lambda = 1000$.
-Black line: $u = -E_0(H)$, red line: $u = -E_{\infty}(H)$, blue line: $u = 0$.}
-\label{fig:Distr_cp_lm}
-\end{figure*}
-
 \begin{definition}
@@
 Theorem 2.12, 2.14, 2.15, 2.5 and 2.8)  and the boundeness of $c$ and $H$.
+
+\begin{figure*}[htp!]
+  \center
+\includegraphics[width = 1.65in]{Distr_cp.pdf}
+\includegraphics[width = 1.65in]{Distr_lm_sp_li.pdf} 
+\includegraphics[width = 1.65in]{Distr_lm_sp_li_zoomed_left.pdf} 
+\includegraphics[width = 1.65in]{Distr_lm_sp_li_zoomed_right.pdf} 
+\vspace{-0.3in}
+\caption{Distribution of the mean number of critical points, local minima and low-index saddle points (oryginal and zoomed).
+Parameters $H$ and $\Lambda$ were set to $H = 3$ and $\Lambda = 1000$.
+Black line: $u = -E_0(H)$, red line: $u = -E_{\infty}(H)$.
+Figure must be read in color.}
+\label{fig:Distr_cp_lm_sp}
+\vspace{-0.1in}
+\end{figure*}
+
 \begin{theorem}
@@
 An interesting implication of Theorems~\ref{thm:lb},~\ref{thm:ub} and~\ref{thm:layer} is that recovering the global minimizer when starting from any (local) minima from one of the energy bands above, e.g.
-$\left(-\Lambda E_i(H),-\Lambda E_{i+1}(H)\right)$, diverges with $\Psi$ since it is bounded below by $\Lambda (E_0(H) - E_i(H))$.
+$\left(-\Lambda E_i(H),-\Lambda E_{i+1}(H)\right)$, diverges with $\Lambda$ since it is bounded below by $\Lambda (E_0(H) - E_i(H))$.
 
 Next we will show the logarithmic asymptotics of the mean number of critical points (the asymptotics of the mean number of critical points can be found in the Supplementary material).
-
-\begin{figure*}[htp!]
-  \center
-\includegraphics[width = 2.2in]{Distr_lm_sp_li.pdf} 
-\includegraphics[width = 2.2in]{Distr_lm_sp_li_zoomed_left.pdf} 
-\includegraphics[width = 2.2in]{Distr_lm_sp_li_zoomed_right.pdf} 
-\caption{Distribution of the mean number of local minima and low-index saddle points (oryginal and zoomed).
-Parameters $H$ and $\Lambda$ were set to $H = 3$ and $\Lambda = 1000$.
-Black line: $u = -E_0(H)$, red line: $u = -E_{\infty}(H)$.}
-\label{fig:Distr_lm_sp}
-\end{figure*}
-
 \begin{theorem}
@@
 \end{theorem}
-Figure~\ref{fig:Distr_cp_lm} captures exemplary plots of the distributions of the mean number of critical points and local minima and Figure~\ref{fig:Distr_lm_sp} captures exemplary plots of the distributions of the mean number of local minima and low-index saddle points.
-Both figures clearly show that the local minima and low-index saddle points are located in the band $\left(-\Lambda E_0(H),-\Lambda E_{\infty}(H)\right)$ whereas high-index saddle points can only be found above the energy barrier $-\Lambda E_{\infty}(H)$.
-Figure~\ref{fig:Distr_lm_sp} also clearly reveals the layered structure for the lowest critical values of the loss function as predicted by the theory.
-
 Note that from Theorem~\ref{thm:lmsp} and Corollary~\ref{cor:Theta} it follows that the number of critical points in the band $\left(-\Lambda E_0(H),-\Lambda E_{\infty}(H)\right)$ increases exponentially as $\Psi$ grows and that local minima dominate over saddle points and this domination also grows exponentially as $\Psi$ grows.
 Thus for large-size networks (large $\Psi$) the probability of recovering a saddle point in the band $\left(-\Lambda E_0(H),-\Lambda E_{\infty}(H)\right)$, rather than a local minima, goes to $0$.
+
+Figure~\ref{fig:Distr_cp_lm_sp} captures exemplary plots of the distributions of the mean number of critical points, local minima and low-index saddle points.
+Clearly local minima and low-index saddle points are located in the band $\left(-\Lambda E_0(H),-\Lambda E_{\infty}(H)\right)$ whereas high-index saddle points can only be found above the energy barrier $-\Lambda E_{\infty}(H)$.
+Figure~\ref{fig:Distr_cp_lm_sp} also reveals the layered structure for the lowest critical values of the loss function.
 
@@
 
-section{Conclusion and Future Work}
+\section{Conclusion and Future Work}
 \label{sec:ConandFutWork}
@@
 
-\newpage
+\clearpage
 
@@
 
+\section{Asymptotics of the mean number of critical points and local minima}
+
 Below, we provide the asymptotics of the mean number of critical points (Theorem~\ref{thm:cpprecise}) and the mean number of local minima (Theorem~\ref{thm:lmspprecise}), which extend Theorem~\ref{thm:lmsp} and Theorem~\ref{thm:cp}.

### 2014-10-19 PAPER_AMMLY.tex
Change after Levent's feedback

@@
 \begin{definition}
-The size of the network $\Lambda$ is the total number of network parameters: $\Lambda = \prod_{i=0}^{H-1}n_in_{i+1}$.
+The size of the network $\Lambda$ is the total number of network parameters: $\Lambda = \sum_{i=0}^{H-1}n_in_{i+1}$.
 \end{definition}
@@
 Also let $\mathcal{B}$ be a set such that each element correspond to the single configuration of weights from Equation~\ref{eq:befrein}, thus $\mathcal{B} = \{(w_{1,1}^1,w_{1,1}^2,\dots,w_{1,1}^H),(w_{1,2}^1,w_{1,2}^2,\dots,w_{1,2}^H),\dots,\\(w_{n_0,\gamma}^1,w_{n_0,\gamma}^2,\dots,w_{n_0,\gamma}^H)\}$, where every single weight comes from set $\mathcal{W}$.
-Note that in general there might exist elements in $\mathcal{A}_{\Lambda}$ that will never appear in $\mathcal{B}$ and also some elements in $\mathcal{A}_{\Lambda}$ may appear in $\mathcal{B}$ multiple times.
+Note that in general there exist elements in $\mathcal{A}_{\Lambda}$ that will never appear in $\mathcal{B}$ (unless we allow repetition of weights in $\mathcal{W}$).
 Thus Equation~\ref{eq:befrein} can be equivalently written as
-\[Y \!=\!
-q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\left(\sum_{c=1}^{r_{i_1,i_2,\dots,i_H}}\!\!\!X_{i_1,i_2,\dots,i_H}^{(c)}A_{i_1,i_2,\dots,i_H}^{(c)}\!\!\right)\!\!\prod_{k = 1}^{H}w_{i_k},
+\[Y \!=\! q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\left(r_{i_1,i_2,\dots,i_H}X_{i_1,i_2,\dots,i_H}A_{i_1,i_2,\dots,i_H}\right)\prod_{k = 1}^{H}w_{i_k},
 \]
-where $r_{i_1,i_2,\dots,i_H}$ denotes the number of times configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein}.
-Note that $r_{i_1,i_2,\dots,i_H} \in \{\mathbb{Z}^{+}\cup{0}\}$ and furthermore $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H} = \Psi$.
+where $r_{i_1,i_2,\dots,i_H}$ denotes whether the configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein} or not thus $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$ and furthermore $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H} = \Psi$.
 Assuming the independence of $X$'s and $A's$ we get
-\[\mathbb{E}_A[Y] = q\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\left(\sum_{c=1}^{r_{i_1,i_2,\dots,i_H}}X_{i_1,i_2,\dots,i_H}^{(c)}\right)\rho\prod_{k = 1}^{H}w_{i_k}
-\]
-Let $Y_{\Lambda} = \mathbb{E}_A[Y]$, where in particular $\Lambda$ in this notation refers to the size of set $\mathcal{A}$ (this notation will be helpful later in this section), and define random variables $Z$'s as
-\[Z_{i_1,i_2,\dots,i_H=1} = \frac{1}{\sqrt{r_{i_1,i_2,\dots,i_H}}}\sum_{c=1}^{r_{i_1,i_2,\dots,i_H}}X_{i_1,i_2,\dots,i_H}^{(c)}.
-\]
-For our theoretical analysis we assume that $X$'s are independent from each other and so are $Z$'s.
-This assumption is simplistic, yet pervasively used in machine learning theory (plethora of decoupling strategies are discussed in~\cite{opac-b1095246}).
-Let $X$'s be identically distributed such that $X_{i_1,i_2,\dots,i_H}^{(c)}\sim\mathcal{N}(0,1)$.
-Therefore $Z_{i_1,i_2,\dots,i_H}\sim\mathcal{N}(0,1)$.
-Thus
 \begin{equation}
-Y_{\Lambda}= q\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{r_{i_1,i_2,\dots,i_H}}Z_{i_1,i_2,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k}.
+Y_{\Lambda} := \mathbb{E}_A[Y] = q\!\!\!\!\!\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!\left(r_{i_1,\dots,i_H}X_{i_1,\dots,i_H}\right)\rho\prod_{k = 1}^{H}\!\!w_{i_k}.
 \label{eq:befapprox}
 \end{equation}
+For our theoretical analysis we also assume that $X$'s are independent identically distributed such that $X_{i_1,i_2,\dots,i_H}^{(c)}\sim\mathcal{N}(0,1)$.
+This assumption is simplistic, yet pervasively used in machine learning theory (plethora of decoupling strategies are discussed in~\cite{opac-b1095246}).
+Finally, let $Y_{\Lambda} = \mathbb{E}_A[Y]$, where in particular $\Lambda$ in this notation refers to the size of set $\mathcal{A}$ (this notation will be helpful later in this section).
+
 Consider a family of networks which have the same graph of connections as network $\mathcal{N}$ but different edge weighting such that they only have $s$ unique weights and $s \leq \Lambda$.
@@
 \begin{equation}
-(1-\delta)C\frac{\Psi}{\Lambda^H} \leq r_{i_1,i_2,\dots,i_H} \leq (1+\delta)C\frac{\Psi}{\Lambda^H},
+(1-\delta)C\sqrt{\frac{\Psi}{\Lambda^H}} \leq r_{i_1,i_2,\dots,i_H} \leq (1+\delta)C\sqrt{\frac{\Psi}{\Lambda^H}},
 \label{eq:uniform}
 \end{equation}
-where the factor $\frac{\Psi}{\Lambda^H}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus every node has equal probability of being adjacent to an edge with any of the unique weights) it holds that $r_{i_1,i_2,\dots,i_H} = \frac{\Psi}{\Lambda^H}$.
+where the factor $\sqrt{\frac{\Psi}{\Lambda^H}}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus every node has equal probability of being adjacent to an edge with any of the unique weights) it holds that $r_{i_1,i_2,\dots,i_H} = C\sqrt{\frac{\Psi}{\Lambda^H}}$.
 Note that this condition can be sattified with small $\delta$ (close to $0$) if $s$ is sufficiently small.
@@
 \begin{equation}
-\hat{Y}_s = q\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}Z_{i_1,i_2,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
+\hat{Y}_s = Cq\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}X_{i_1,i_2,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
 \label{eq:approx}
@@
 &=& \!\!\!\!\!\rho^{'} + \rho^{'}\hat{Y}_s\\
-&=& \!\!\!\!\!\rho^{'} + q\sqrt{\!\frac{\Psi}{\Lambda^H}\!}\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!Z_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}
+&=& \!\!\!\!\!\rho^{'} + Cq\sqrt{\!\frac{\Psi}{\Lambda^H}\!}\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!Z_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}
 \end{eqnarray*}
@@
 \begin{equation}
-\mathcal{L}_{\Lambda,H}({\bm w}) = \rho + q\sqrt{\frac{\Psi}{\Lambda^H}}\sum_{i_1,\dots,i_H=1}^{\Lambda}Z_{i_1,\dots,i_H}\prod_{k = 1}^{H}\tilde{w}_{i_k}.
+\mathcal{L}_{\Lambda,H}({\bm w}) = \rho + Cq\sqrt{\frac{\Psi}{\Lambda^H}}\!\!\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!Z_{i_1,\dots,i_H}\prod_{k = 1}^{H}\tilde{w}_{i_k}.
 \label{eq:befloss}
@@
 \end{equation}
-where the last inequality was obtained by substituting $q = \sqrt{\frac{\Lambda}{\Psi}}$.
+where the last inequality was obtained by substituting $q = \sqrt{\frac{\Lambda}{\Psi}}$ ans assuming, without loss of generality, that $C = 1$.
 For the analysis $X$'s are assumed to be independent.
@@
 Note that $\mathbb{E}[\hat{Y}_s] = 0$ and $\mathbb{E}[Y_{\Lambda}] = 0$. Furthermore
-\[\mathbb{E}[\hat{Y}_sY_{\Lambda}] = q^2\rho^2\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}r_{i_1,i_2,\dots,i_H}}\prod_{k = 1}^{H}w_{i_k}^2
+\[\mathbb{E}[\hat{Y}_sY_{\Lambda}] = C^2q^2\rho^2\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}r_{i_1,i_2,\dots,i_H}^2}\prod_{k = 1}^{H}w_{i_k}^2
 \]
 and
-\[std(\hat{Y}_s) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2}
+\[std(\hat{Y}_s) = Cq\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2}
 \]
-\[std(Y_{\Lambda}) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2}.
+\[std(Y_{\Lambda}) = Cq\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2}.
 \]
@@
 &\!\!\!\!\!\!\!\!\!=&\!\!\!\!\!\!\!
-\frac{\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}r_{i_1,\dots,i_H}}\prod_{k = 1}^{H}w_{i_k}^2}{\sqrt{\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2\right)\!\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!r_{i_1,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2\right)}}\\
+\frac{\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}r_{i_1,\dots,i_H}^2}\prod_{k = 1}^{H}w_{i_k}^2}{\sqrt{\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2\right)\!\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!r_{i_1,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2\right)}}\\
 &\!\!\!\!\!\!\!\!\geq& \sqrt{\frac{1-\delta}{1+\delta}}, 

### 2014-10-19 PAPER_AMMLY.tex
Change

@@
 Let $\Psi$ be the mass of the network, $d$ be the number of network inputs and $H$ be the depth of the network. The size of the network is bounded as
-\[\Psi^2\frac{1}{d} \geq \Lambda \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}}.
+\[\Psi^2\frac{1}{d} \geq \Lambda \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}} \geq \sqrt[H]{\Psi}.
 \]
@@
 Thus Equation~\ref{eq:befrein} can be equivalently written as
-\[Y \!=\! q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\left(r_{i_1,i_2,\dots,i_H}X_{i_1,i_2,\dots,i_H}A_{i_1,i_2,\dots,i_H}\right)\prod_{k = 1}^{H}w_{i_k},
+\[Y = q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!r_{i_1,i_2,\dots,i_H}X_{i_1,i_2,\dots,i_H}A_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k},
 \]
-where $r_{i_1,i_2,\dots,i_H}$ denotes whether the configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein} or not thus $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$ and furthermore $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H} = \Psi$.
+where $r_{i_1,i_2,\dots,i_H}$ denotes whether the configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein} or not thus $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$ and furthermore $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H}^2 = \Psi$.
 Assuming the independence of $X$'s and $A's$ we get
 \begin{equation}
-Y_{\Lambda} := \mathbb{E}_A[Y] = q\!\!\!\!\!\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!\left(r_{i_1,\dots,i_H}X_{i_1,\dots,i_H}\right)\rho\prod_{k = 1}^{H}\!\!w_{i_k}.
+Y_{\Lambda} := \mathbb{E}_A[Y] = q\!\!\!\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!r_{i_1,\dots,i_H}X_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}\!\!w_{i_k}.
 \label{eq:befapprox}
 \end{equation}
-For our theoretical analysis we also assume that $X$'s are independent identically distributed such that $X_{i_1,i_2,\dots,i_H}^{(c)}\sim\mathcal{N}(0,1)$.
+In the notation $Y_{\Lambda}$, index $\Lambda$ refers to the size of set $\mathcal{A}$ (this notation will be helpful later in this section).
+For our theoretical analysis we assume that $X$'s are independent identically distributed such that $X_{i_1,i_2,\dots,i_H}\sim\mathcal{N}(0,1)$.
 This assumption is simplistic, yet pervasively used in machine learning theory (plethora of decoupling strategies are discussed in~\cite{opac-b1095246}).
-Finally, let $Y_{\Lambda} = \mathbb{E}_A[Y]$, where in particular $\Lambda$ in this notation refers to the size of set $\mathcal{A}$ (this notation will be helpful later in this section).
 
@@
 We call this assumption a \textit{uniformity assumption} (note it is analogous to the maximum entropy assumption).
-This assumption is in general consistent with the approach in~\cite{NIPS2013_5025}.
-To be more specific, this assumption implies that there exists some bounded non-negative constant $C$ such that for all $(i_1,i_2,\dots,i_H):i_1,i_2,\dots,i_H \in \{1,2,\dots,H\}$ and some $\delta \in [0,1]$ the following holds
+This assumption is in general consistent with the approach in~\cite{NIPS2013_5025} and allows us to treat $r$'s as probabilities rather than binary values.
+To be more specific, this assumption implies that for all $(i_1,i_2,\dots,i_H):i_1,i_2,\dots,i_H \in \{1,2,\dots,H\}$ there exists $\delta \in [0,1]$ such that the following holds
 \begin{equation}
-(1-\delta)C\sqrt{\frac{\Psi}{\Lambda^H}} \leq r_{i_1,i_2,\dots,i_H} \leq (1+\delta)C\sqrt{\frac{\Psi}{\Lambda^H}},
+(1-\delta)\sqrt{\frac{\Psi}{\Lambda^H}} \leq r_{i_1,i_2,\dots,i_H} \leq (1+\delta)\sqrt{\frac{\Psi}{\Lambda^H}},
 \label{eq:uniform}
 \end{equation}
-where the factor $\sqrt{\frac{\Psi}{\Lambda^H}}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus every node has equal probability of being adjacent to an edge with any of the unique weights) it holds that $r_{i_1,i_2,\dots,i_H} = C\sqrt{\frac{\Psi}{\Lambda^H}}$.
+where the factor $\sqrt{\frac{\Psi}{\Lambda^H}}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus every node has equal probability of being adjacent to an edge with any of the unique weights) it holds that $r_{i_1,i_2,\dots,i_H} = \sqrt{\frac{\Psi}{\Lambda^H}}$.
 Note that this condition can be sattified with small $\delta$ (close to $0$) if $s$ is sufficiently small.
@@
 \begin{equation}
-\hat{Y}_s = Cq\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}X_{i_1,i_2,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
+\hat{Y}_s = q\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}X_{i_1,i_2,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
 \label{eq:approx}
@@
 &=& \!\!\!\!\!\rho^{'} + \rho^{'}\hat{Y}_s\\
-&=& \!\!\!\!\!\rho^{'} + Cq\sqrt{\!\frac{\Psi}{\Lambda^H}\!}\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!Z_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}
+&=& \!\!\!\!\!\rho^{'} + q\sqrt{\!\!\frac{\Psi}{\Lambda^H}\!\!}\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!Z_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}
 \end{eqnarray*}
@@
 \begin{equation}
-\mathcal{L}_{\Lambda,H}({\bm w}) = \rho + Cq\sqrt{\frac{\Psi}{\Lambda^H}}\!\!\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!Z_{i_1,\dots,i_H}\prod_{k = 1}^{H}\tilde{w}_{i_k}.
+\mathcal{L}_{\Lambda,H}({\bm w}) = \rho + q\sqrt{\!\!\frac{\Psi}{\Lambda^H}\!\!}\sum_{i_1,\dots,i_H=1}^{\Lambda}Z_{i_1,\dots,i_H}\prod_{k = 1}^{H}\tilde{w}_{i_k}.
 \label{eq:befloss}
@@
 \end{equation}
-where the last inequality was obtained by substituting $q = \sqrt{\frac{\Lambda}{\Psi}}$ ans assuming, without loss of generality, that $C = 1$.
+where the last inequality was obtained by substituting $q = \sqrt{\frac{\Lambda}{\Psi}}$.
 For the analysis $X$'s are assumed to be independent.
@@
 First we will prove the lower-bound. By the inequality between arithmetic and geometric mean the mass and the size of the network are connected as follows
-\[\Lambda \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{n_0n_H}} = \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}}
+\[\Lambda \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{n_0n_H}} = \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}},
+\]
+and since $\sqrt[H]{\Psi}\frac{H}{\sqrt[H]{d}} = \sqrt[H]{\prod_{i = 1}^{H}n_i}H \geq 1$ then 
+\[\Lambda \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}} \geq \sqrt[H]{\Psi}.
 \]
@@
 Note that $\mathbb{E}[\hat{Y}_s] = 0$ and $\mathbb{E}[Y_{\Lambda}] = 0$. Furthermore
-\[\mathbb{E}[\hat{Y}_sY_{\Lambda}] = C^2q^2\rho^2\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}r_{i_1,i_2,\dots,i_H}^2}\prod_{k = 1}^{H}w_{i_k}^2
+\[\mathbb{E}[\hat{Y}_sY_{\Lambda}] = q^2\rho^2\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}r_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2
 \]
 and
-\[std(\hat{Y}_s) = Cq\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2}
+\[std(\hat{Y}_s) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2}
 \]
-\[std(Y_{\Lambda}) = Cq\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2}.
+\[std(Y_{\Lambda}) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2}.
 \]
@@
 &\!\!\!\!\!\!\!\!\!=&\!\!\!\!\!\!\!
-\frac{\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}r_{i_1,\dots,i_H}^2}\prod_{k = 1}^{H}w_{i_k}^2}{\sqrt{\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2\right)\!\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!r_{i_1,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2\right)}}\\
+\frac{\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}r_{i_1,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2}{\sqrt{\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2\right)\!\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!r_{i_1,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2\right)}}\\
 &\!\!\!\!\!\!\!\!\geq& \sqrt{\frac{1-\delta}{1+\delta}}, 

### 2014-10-20 PAPER_AMMLY.tex
Some more tuning

@@
 Let $\mathcal{N}$, whose output is $Y_{\Lambda}$, be the neural network predicting $1$ with probability $p$ and $-1$ otherwise.
-Let $\mathcal{M}$ be its $(s,\epsilon)$-reduction image for some $s \leq \Lambda$ and $\epsilon \in [0,1]$.
+Let $\mathcal{M}$ be its $(s,\epsilon)$-reduction image for some $s \leq \Lambda$ and $\epsilon \in [0,p]$.
 Then
@@
 Under the uniformity assumption of Equation~\ref{eq:uniform}, random variable $\hat{Y}_s$ in Equation~\ref{eq:approx} and random variable $Y_{\Lambda}$ in Equation~\ref{eq:befapprox} sattisy the following
-\[corr(\hat{Y}_s,Y_{\Lambda}) \geq \sqrt{\frac{1-\delta}{1+\delta}}.
+\[corr(\hat{Y}_s,Y_{\Lambda}) \geq \frac{1-\delta}{1+\delta}.
 \]
@@
 Let $\mathcal{X}^{+}$ denote the set of data points for which $\mathcal{N}$ predicts $+1$ and let $\mathcal{X}^{-}$ denote the set of data points for which $\mathcal{N}$ predicts $-1$ ($\mathcal{X}^{+} \cup \mathcal{X}^{-} = \mathcal{X}$, where $\mathcal{X}$ is the entire dataset).
-Also let $p = \frac{|\mathcal{X}^{+}|}{|\mathcal{X}|}$.
+Also let $p = \frac{|\mathcal{X}^{+}|}{|\mathcal{X}|}$ and without loss of generality assume $p \leq 0.5$.
 Furthermore, let $\mathcal{X}_{\epsilon}^{-}$ denote the dataset for which $Z_{\Lambda} = +1$ and $Z_s = -1$ and $\mathcal{X}_{\epsilon}^{+}$ denote the dataset for which $Z_{\Lambda} = -1$ and $Z_s = +1$, where $\frac{|\mathcal{X}_{\epsilon}^{+}| + |\mathcal{X}_{\epsilon}^{-}|}{\mathcal{X}} = \epsilon$.
@@
 \frac{\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}r_{i_1,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2}{\sqrt{\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2\right)\!\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!r_{i_1,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2\right)}}\\
-&\!\!\!\!\!\!\!\!\geq& \sqrt{\frac{1-\delta}{1+\delta}}, 
+&\!\!\!\!\!\!\!\!\geq& \frac{1-\delta}{1+\delta}, 
 \end{eqnarray*}

### 2014-10-20 PAPER_AMMLY.tex
Theory fixed

@@
 Let $\mathcal{W} = \{w_1,w_2,\dots,w_{\Lambda}\}$ be the set of all weights of the network.
-Furthermore let $\mathcal{A}_{\Lambda}$ denote the set of all $H$-length configuration of weights chosen from $\mathcal{W}$ (order of weights in a configuration does matter).
-Note that the size of $\mathcal{A}_{\Lambda}$ is therefore $\Lambda^H$.
+Furthermore let $\mathcal{A}$ denote the set of all $H$-length configuration of weights chosen from $\mathcal{W}$ (order of weights in a configuration does matter).
+Note that the size of $\mathcal{A}$ is therefore $\Lambda^H$.
 Also let $\mathcal{B}$ be a set such that each element correspond to the single configuration of weights from Equation~\ref{eq:befrein}, thus $\mathcal{B} = \{(w_{1,1}^1,w_{1,1}^2,\dots,w_{1,1}^H),(w_{1,2}^1,w_{1,2}^2,\dots,w_{1,2}^H),\dots,\\(w_{n_0,\gamma}^1,w_{n_0,\gamma}^2,\dots,w_{n_0,\gamma}^H)\}$, where every single weight comes from set $\mathcal{W}$.
-Note that in general there exist elements in $\mathcal{A}_{\Lambda}$ that will never appear in $\mathcal{B}$ (unless we allow repetition of weights in $\mathcal{W}$).
+Note that in general there exist elements in $\mathcal{A}$ that will never appear in $\mathcal{B}$ (unless we allow repetition of weights in $\mathcal{W}$).
 Thus Equation~\ref{eq:befrein} can be equivalently written as
@@
 \]
-where $r_{i_1,i_2,\dots,i_H}$ denotes whether the configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein} or not thus $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$ and furthermore $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H}^2 = \Psi$.
+where $r_{i_1,i_2,\dots,i_H}$ denotes whether the configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein} or not thus $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$ and furthermore $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H} = \Psi$.
 Assuming the independence of $X$'s and $A's$ we get
@@
 In the notation $Y_{\Lambda}$, index $\Lambda$ refers to the size of set $\mathcal{A}$ (this notation will be helpful later in this section).
-For our theoretical analysis we assume that $X$'s are independent identically distributed such that $X_{i_1,i_2,\dots,i_H}\sim\mathcal{N}(0,1)$.
-This assumption is simplistic, yet pervasively used in machine learning theory (plethora of decoupling strategies are discussed in~\cite{opac-b1095246}).
+For our theoretical analysis we assume that $X$'s are identically distributed such that $X_{i_1,i_2,\dots,i_H}\sim\mathcal{N}(0,1)$.
 
@@
 
+Consider $(s,\epsilon)$-reduction image of $\mathcal{N}$ for some $s \leq \Lambda$ and $\epsilon \in [0,1]$. The output $Y_s$ of the image network can in general be expressed as
+\[Y_s = q\!\!\!\sum_{i_1,\dots,i_H=1}^{s}\!\!\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}X_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}\!\!w_{i_k},
+\]
+where $r_{i_1,\dots,i_H}^{'} \in \{\mathbb{Z}^{+}\cup{0}\}$ is the number of times each configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ repeats in Equation~\ref{eq:befapprox} and $\sum_{i_1,\dots,i_H=1}^{s}r_{i_1,\dots,i_H}^{'} = \Psi$.
+We can further rewrite $Y_s$ as follows
+\[Y_s = q\!\!\!\sum_{i_1,\dots,i_H=1}^{s}\!\!\underbrace{\left(\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}\!\!\!X_{i_1,\dots,i_H} + 0 + \dots + 0\right)}_{r_{i_1,\dots,i_H}^{''} \text{summands}}\!\!\rho\prod_{k = 1}^{H}\!\!w_{i_k},
+\]
+where $r_{i_1,\dots,i_H}^{''} \in \{\mathbb{Z}^{+}\cup{0}\}$ is the number of times each configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ would repeat in Equation~\ref{eq:befapprox} if all $r_{i_1,\dots,i_H}$ would be equal to $1$ and $\mathcal{W}$ would have $s$ unique weights and the remaining $(\Lambda - s)$ weights were repetitions\footnote{Note that each $r_{i_1,\dots,i_H}^{''}$ is not uniquely defined here as one could consider many different ways of constructing $\mathcal{W}$ by repeating the same weights different times.}.
+We therefore require that $r_{i_1,\dots,i_H}^{''} \in \{\mathbb{Z}^{+}\cup{0}\}$, $r_{i_1,\dots,i_H}^{''} \geq r_{i_1,\dots,i_H}^{'}$ and $\sum_{i_1,\dots,i_H=1}^{s}r_{i_1,\dots,i_H}^{''} = \Lambda^H$.
+We furthermore define $Z$'s to be independend standard normal random variables satisfying the following (plethora of similar decoupling strategies are discussed in~\cite{opac-b1095246})
+\[\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}X_{i_1,\dots,i_H} = \sum_{j=1}^{r_{i_1,\dots,i_H}^{''}} \sqrt{\frac{r_{i_1,\dots,i_H}^{'}}{r_{i_1,\dots,i_H}^{''}}}Z_{i_1,\dots,i_H}^{(j)}. 
+\]
+Let $\hat{r}_{i_1,\dots,i_H}^{(j)} = \sqrt{\frac{r_{i_1,\dots,i_H}^{'}}{r_{i_1,\dots,i_H}^{''}}}$. Therefore
+\begin{eqnarray*}
+Y_s &=& q\sum_{i_1,\dots,i_H=1}^{s}\sum_{j=1}^{r_{i_1,\dots,i_H}^{''}}\hat{r}_{i_1,\dots,i_H}^{(j)}Z_{i_1,\dots,i_H}^{(j)}\rho\prod_{k = 1}^{H}w_{i_k}\\
+&=& \sum_{i_1,\dots,i_H=1}^{\Lambda}\hat{r}_{i_1,\dots,i_H}Z_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
+\end{eqnarray*}
+where the last step comes from re-indexing terms.
+
 Finally we assume that unique weights are close to being evenly distributed on the graph of connections of network $\mathcal{M}$.
 We call this assumption a \textit{uniformity assumption} (note it is analogous to the maximum entropy assumption).
-This assumption is in general consistent with the approach in~\cite{NIPS2013_5025} and allows us to treat $r$'s as probabilities rather than binary values.
-To be more specific, this assumption implies that for all $(i_1,i_2,\dots,i_H):i_1,i_2,\dots,i_H \in \{1,2,\dots,H\}$ there exists $\delta \in [0,1]$ such that the following holds
+This assumption is in general consistent with the approach in~\cite{NIPS2013_5025}.
+To be more specific, this assumption implies that for all $(i_1,i_2,\dots,i_H):i_1,i_2,\dots,i_H \in \{1,2,\dots,H\}$ there exists non-negative constant $c$ and $\delta \in [0,1]$ such that the following holds
 \begin{equation}
-(1-\delta)\sqrt{\frac{\Psi}{\Lambda^H}} \leq r_{i_1,i_2,\dots,i_H} \leq (1+\delta)\sqrt{\frac{\Psi}{\Lambda^H}},
+c\delta\sqrt{\frac{\Psi}{\Lambda^H}} \leq \hat{r}_{i_1,i_2,\dots,i_H} \leq c\sqrt{\frac{\Psi}{\Lambda^H}},
 \label{eq:uniform}
 \end{equation}
-where the factor $\sqrt{\frac{\Psi}{\Lambda^H}}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus every node has equal probability of being adjacent to an edge with any of the unique weights) it holds that $r_{i_1,i_2,\dots,i_H} = \sqrt{\frac{\Psi}{\Lambda^H}}$.
-Note that this condition can be sattified with small $\delta$ (close to $0$) if $s$ is sufficiently small.
+where the factor $\sqrt{\frac{\Psi}{\Lambda^H}}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus every node has equal probability of being adjacent to an edge with any of the unique weights) it holds that $\hat{r}_{i_1,i_2,\dots,i_H} = \sqrt{\frac{\Psi}{\Lambda^H}}$.
+Note that this condition can be sattified with large $\delta$ (close to $0$) if $s$ is sufficiently small.
 
@@
 \begin{equation}
-\hat{Y}_s = q\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}X_{i_1,i_2,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
+\hat{Y}_s = q\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}Z_{i_1,i_2,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
 \label{eq:approx}
@@
 Under the uniformity assumption of Equation~\ref{eq:uniform}, random variable $\hat{Y}_s$ in Equation~\ref{eq:approx} and random variable $Y_{\Lambda}$ in Equation~\ref{eq:befapprox} sattisy the following
-\[corr(\hat{Y}_s,Y_{\Lambda}) \geq \frac{1-\delta}{1+\delta}.
+\[corr(\hat{Y}_s,Y_{\Lambda}) \geq \delta
 \]
@@
 We will refer to $\hat{Y}_s$ as an $(s,\epsilon,\delta)$-\textit{approximator} of $Y_{\Lambda}$, where the quality of this approximation is captured in Theorems~\ref{thm:redun} and~\ref{thm:unif}.
-Intuitively, for large-size networks (our analysis in Section~\ref{sec:theory} considers $\Lambda \rightarrow \infty$) one would expect $s$ to be small enough to simultaneously guarantee sufficiently small (close to $0$) $\delta$ and preserve good accuracy (small $\epsilon$).
+Intuitively, for large-size networks (our analysis in Section~\ref{sec:theory} considers $\Lambda \rightarrow \infty$) one would expect $s$ to be small enough to simultaneously guarantee sufficiently large (close to $1$) $\delta$ and preserve good accuracy (small $\epsilon$).
 \textcolor{red}{That is because large networks have significantly more modelling power thus small $s$ is a natural form of controlling the overfitting.
@@
 
-\begin{definition}
-The ground state energy is the (normalized) minimum of the loss function $\mathcal{L}_{\Psi,c,H}$
-\[G^\Psi = \frac{1}{\Lambda}\inf_{{\bm w}\in \mathcal{S}_{\Psi,c}}\mathcal{L}_{\Psi,c,H}({\bm w}).
-\]
-\end{definition}
-Next we provide theorems (resp.
-Theorem~\ref{thm:lb},~\ref{thm:ub},~\ref{thm:layer}, ~\ref{thm:lmsp} and~\ref{thm:cp}) which are direct consequences of the theoretical findings in~\cite{AAC2010} (resp.
-Theorem 2.12, 2.14, 2.15, 2.5 and 2.8)  and the boundeness of $c$ and $H$.
-
 \begin{figure*}[htp!]
@@
 \end{figure*}
+
+\begin{definition}
+The ground state energy is the (normalized) minimum of the loss function $\mathcal{L}_{\Psi,c,H}$
+\[G^\Psi = \frac{1}{\Lambda}\inf_{{\bm w}\in \mathcal{S}_{\Psi,c}}\mathcal{L}_{\Psi,c,H}({\bm w}).
+\]
+\end{definition}
+Next we provide theorems (resp.
+Theorem~\ref{thm:lb},~\ref{thm:ub},~\ref{thm:layer}, ~\ref{thm:lmsp} and~\ref{thm:cp}) which are direct consequences of the theoretical findings in~\cite{AAC2010} (resp.
+Theorem 2.12, 2.14, 2.15, 2.5 and 2.8)  and the boundeness of $c$ and $H$.
 
@@
 Note that $\mathbb{E}[\hat{Y}_s] = 0$ and $\mathbb{E}[Y_{\Lambda}] = 0$. Furthermore
-\[\mathbb{E}[\hat{Y}_sY_{\Lambda}] = q^2\rho^2\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}r_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2
+\[\mathbb{E}[\hat{Y}_sY_{\Lambda}] = q^2\rho^2\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}\hat{r}_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2
 \]
@@
 \]
-\[std(Y_{\Lambda}) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2}.
+\[std(Y_{\Lambda}) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\hat{r}_{i_1,i_2,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2}.
 \]
@@
 &\!\!\!\!\!\!\!\!\!=&\!\!\!\!\!\!\!
-\frac{\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}r_{i_1,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2}{\sqrt{\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2\right)\!\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!r_{i_1,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2\right)}}\\
-&\!\!\!\!\!\!\!\!\geq& \frac{1-\delta}{1+\delta}, 
+\frac{\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}\hat{r}_{i_1,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2}{\sqrt{\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2\right)\!\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\hat{r}_{i_1,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2\right)}}\\
+&\!\!\!\!\!\!\!\!\geq& \delta, 
 \end{eqnarray*}

### 2014-10-20 PAPER_AMMLY.tex
more

@@
 Let $W_i$ be the matrix of weights between $(i - 1)^{\text{th}}$ and $i^{th}$ layers of the network.
+We assume weights are bounded.
 Also, let $\sigma$ denotes the activation function that converts a unit's weighted input to its output activation.
@@
 and
-\[\mathcal{L}^h_{\Lambda,H}({\bm w}) = \max(0,1-Y_t\hat{Y}_s).
+\[\mathcal{L}^h_{\Lambda,H}({\bm w}) = \max(0,S-Y_t\hat{Y}_s).
 \]
-where $Y_t$ is a random variable corresponding the true data labeling that takes values $-1$ or $1$.
+where $Y_t$ is a random variable corresponding the true data labeling that takes values $-S$ or $S$, where $S = \sup_{\bf{w}}{\hat{Y}_s}$.
 Also note that in case of the hinge loss $\max$ operator can be modelled as Bernoulli random variable, that we will refer to as $M$, with success ($M = 1$) probability $\rho^{'}$.
@@
 Therefore we obtain that
-\[\mathcal{L}^a_{N,H}({\bm w}) = \left \{
+\[\mathcal{L}^a_{\Lambda,H}({\bm w}) = \left \{
   \begin{tabular}{c}
-  $\!\!\!\!\!\!1 - \hat{Y}_s$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = 1$ \\
-  $\!1 + \hat{Y}_s$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -1$ \\
+  $\!\!\!\!\!\!S - \hat{Y}_s$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = S$ \\
+  $\!S + \hat{Y}_s$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -S$ \\
   \end{tabular}
@@
 \begin{eqnarray*}
-\mathcal{L}^h_{\Lambda,H}({\bm w}) &=& \mathbb{E}_{M,A}[M(1-Y_t\hat{Y}_s)]\\&=& \left \{
+\mathcal{L}^h_{\Lambda,H}({\bm w}) &=& \mathbb{E}_{M,A}[M(
+S-Y_t\hat{Y}_s)]\\&=& \left \{
   \begin{tabular}{c}
-  $\!\!\!\!\!\!\mathbb{E}_{M}[M(1 - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = 1$ \\
-  $\!\mathbb{E}_{M}[M(1 + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -1$ \\
+  $\!\!\!\!\!\!\mathbb{E}_{M}[M(S - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = S$ \\
+  $\!\mathbb{E}_{M}[M(S + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -S$ \\
   \end{tabular}
@@
   \begin{tabular}{c}
-  $\!\!\!\!\!\!\mathbb{E}_{M}[M(1 - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = 1$ \\
-  $\!\mathbb{E}_{M}[M(1 + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -1$ \\
+  $\!\!\!\!\!\!\mathbb{E}_{M}[M(S - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = S$ \\
+  $\!\mathbb{E}_{M}[M(S + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -S$ \\
   \end{tabular}
@@
 \begin{eqnarray*}
-\mathcal{L}_{\Lambda,H}({\bm w}) \!\!\!\!\!&=&\!\!\!\!\! \mathbb{E}_{M}[M(1 + \hat{Y}_s)]\\
-&=& \!\!\!\!\!\rho^{'} + \rho^{'}\hat{Y}_s\\
-&=& \!\!\!\!\!\rho^{'} + q\sqrt{\!\!\frac{\Psi}{\Lambda^H}\!\!}\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!Z_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}
+\mathcal{L}_{\Lambda,H}({\bm w}) \!\!\!\!\!&=&\!\!\!\!\! \mathbb{E}_{M}[M(S + \hat{Y}_s)]\\
+&=& \!\!\!\!\!\rho^{'}S + \rho^{'}\hat{Y}_s\\
+&=& \!\!\!\!\!\rho^{'}S + q\sqrt{\!\!\frac{\Psi}{\Lambda^H}\!\!}\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!Z_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}
 \end{eqnarray*}
@@
 \begin{equation}
-\mathcal{L}_{\Lambda,H}({\bm w}) = \rho + q\sqrt{\!\!\frac{\Psi}{\Lambda^H}\!\!}\sum_{i_1,\dots,i_H=1}^{\Lambda}Z_{i_1,\dots,i_H}\prod_{k = 1}^{H}\tilde{w}_{i_k}.
+\mathcal{L}_{\Lambda,H}({\bm w}) = \rho^{'}S + q\sqrt{\!\!\frac{\Psi}{\Lambda^H}\!\!}\sum_{i_1,\dots,i_H=1}^{\Lambda}Z_{i_1,\dots,i_H}\prod_{k = 1}^{H}\tilde{w}_{i_k}.
 \label{eq:befloss}
@@
 \end{equation}
-To simplify the notation in Equation~\ref{eq:befloss} we drop the letter accents and simply denote $\hat{w}$ as $w$. We skip constant $\rho$ as it does not matter when minimizing the loss function.
+To simplify the notation in Equation~\ref{eq:befloss} we drop the letter accents and simply denote $\hat{w}$ as $w$.
+We skip constant $\rho^{'}S$ as it does not matter when minimizing the loss function.
 \begin{equation}
@@
 For the analysis $X$'s are assumed to be independent.
-Equation~\ref{eq:spinglass} is the centered Gaussian process on the sphere $\mathcal{S}_{N} = S^{N-1}(\sqrt{N})$ and is equivalent to the Hamiltonian of the $H$-spin spherical spin-glass model.
+Equation~\ref{eq:spinglass} is the centered Gaussian process on the sphere $\mathcal{S} = S^{\Lambda-1}(\sqrt{\Lambda})$ and is equivalent to the Hamiltonian of the $H$-spin spherical spin-glass model.
 The spherical constraint is captured in Equation~\ref{eq:spherical}.
@@
 \label{sec:theory}
-Our theoretical findings are direct consequence of the theoretical analysis of the complexity of spherical spin-glass models of~\cite{AAC2010}. We will first introduce the notation and definitions. 
+The theoretical findings of this section are direct consequence of the theoretical analysis of the complexity of spherical spin-glass models of~\cite{AAC2010}.
+We will first introduce the notation and definitions.
 \begin{definition}
@@
 The ground state energy is the (normalized) minimum of the loss function $\mathcal{L}_{\Psi,c,H}$
-\[G^\Psi = \frac{1}{\Lambda}\inf_{{\bm w}\in \mathcal{S}_{\Psi,c}}\mathcal{L}_{\Psi,c,H}({\bm w}).
+\[G^\Psi = \frac{1}{\Lambda}\inf_{{\bm w}\in \mathcal{S}}\mathcal{L}_{\Lambda,H}({\bm w}).
 \]
@@
 Theorem~\ref{thm:lb},~\ref{thm:ub},~\ref{thm:layer}, ~\ref{thm:lmsp} and~\ref{thm:cp}) which are direct consequences of the theoretical findings in~\cite{AAC2010} (resp.
-Theorem 2.12, 2.14, 2.15, 2.5 and 2.8)  and the boundeness of $c$ and $H$.
+Theorem 2.12, 2.14, 2.15, 2.5 and 2.8).
 
@@
 We will refer to this important threshold as an \textit{energy barrier}.
-Any critical point that lies above this threshold is a high-index saddle point with overwhelming probablity.
+Any critical point that lies above the energy barrier is a high-index saddle point with overwhelming probablity.
 Theorem~\ref{thm:lb} and~\ref{thm:ub} both imply that for large-size networks all critical values of the loss function that are of non-diverging index must lie in the band $\left(-\Lambda E_0(H),-\Lambda E_{\infty}(H)\right)$.
@@
 
-The statements of Theorems~\ref{thm:lb},~\ref{thm:ub} and~\ref{thm:layer} unravel a layered structure for the lowest critical values of the loss function of a large-mass (or large-size) deep network, where with overwhelming probability the critical values above the global minimizer (ground state) of the loss function are local minima exclusively.
-Above the band ($\left(-\Lambda E_0(H),-\Lambda E_1(H)\right)$) with only local minima, there is another one, ($\left(-\Lambda E_1(H),-\Lambda E_2(H)\right)$), where one can only find local minima (critical points of index $0$) and saddle points of index $1$, and above this band there exists another one, ($\left(-\Lambda E_2(H),-\Lambda E_3(H)\right)$), where one can only find local minima and saddle points of index $1$ and $2$, etc.
-The above-described layered structure of the lowest critical values of the Hamiltonian of the spherical spin glass model was in-detail described in~\cite{AAC2010}, however with no connection to deep learning that instead we explore.
+The statements of Theorems~\ref{thm:lb},~\ref{thm:ub} and~\ref{thm:layer} unravel a layered structure for the lowest critical values of the loss function of a large-size network, where with overwhelming probability the critical values above the global minimizer (ground state) of the loss function are local minima exclusively.
+Above the band ($\left(-\Lambda E_0(H),-\Lambda E_1(H)\right)$) containing only local minima (critical points of index $0$), there is another one, ($\left(-\Lambda E_1(H),-\Lambda E_2(H)\right)$), where one can only find local minima and saddle points of index $1$, and above this band there exists another one, ($\left(-\Lambda E_2(H),-\Lambda E_3(H)\right)$), where one can only find local minima and saddle points of index $1$ and $2$, etc.
+The above-described layered structure of the lowest critical values of the Hamiltonian of the spherical spin glass model was in-detail described in~\cite{AAC2010}, however with no connection to neural networks which is what we explore.
 
@@
 \end{theorem}
-Note that from Theorem~\ref{thm:lmsp} and Corollary~\ref{cor:Theta} it follows that the number of critical points in the band $\left(-\Lambda E_0(H),-\Lambda E_{\infty}(H)\right)$ increases exponentially as $\Psi$ grows and that local minima dominate over saddle points and this domination also grows exponentially as $\Psi$ grows.
-Thus for large-size networks (large $\Psi$) the probability of recovering a saddle point in the band $\left(-\Lambda E_0(H),-\Lambda E_{\infty}(H)\right)$, rather than a local minima, goes to $0$.
+Note that from Theorem~\ref{thm:lmsp} and Corollary~\ref{cor:Theta} it follows that the number of critical points in the band $\left(-\Lambda E_0(H),-\Lambda E_{\infty}(H)\right)$ increases exponentially as $\Lambda$ grows and that local minima dominate over saddle points and this domination also grows exponentially as $\Lambda$ grows.
+Thus for large-size networks (large $\Lambda$) the probability of recovering a saddle point in the band $\left(-\Lambda E_0(H),-\Lambda E_{\infty}(H)\right)$, rather than a local minima, goes to $0$.
 
@@
 \label{sec:Experiments}
+
+\textcolor{red}{We need to prove that we get ot local minima not flat saddle points from Bengio paper.}
 

### 2014-10-20 PAPER_AMMLY.tex
more

@@
 \begin{abstract}
-We explore the approximate equivalence of the highly non-convex loss function of a simple model of the fully-connected feed-forward neural network and the Hamiltonian of the spherical spin-glass model under certain assumptions.
+We explore the approximate relation between the highly non-convex loss function of a simple model of the fully-connected feed-forward neural network and the Hamiltonian of the spherical spin-glass model under certain assumptions.
 Using the results from the random matrix theory, we study the complexity of neural networks and prove that for large-size networks the lowest critical values of the loss function are located in a well-defined narrow band lower-bounded by the global minimum and furthermore they form a layered structure.
@@
 \begin{equation}
-Y = q\sum_{i=1}^{n_0}\sum_{j = 1}^\gamma X_{i,j}A_{i,j}\prod_{k = 1}^{H}w_{i,j}^{(k)},
+Y = q\sum_{i=1}^{n_0}\sum_{j = 1}^\gamma X_{i}A_{i,j}\prod_{k = 1}^{H}w_{i,j}^{(k)},
 \label{eq:befrein}
@@
 We therefore require that $r_{i_1,\dots,i_H}^{''} \in \{\mathbb{Z}^{+}\cup{0}\}$, $r_{i_1,\dots,i_H}^{''} \geq r_{i_1,\dots,i_H}^{'}$ and $\sum_{i_1,\dots,i_H=1}^{s}r_{i_1,\dots,i_H}^{''} = \Lambda^H$.
-We furthermore define $Z$'s to be independend standard normal random variables satisfying the following (plethora of similar decoupling strategies are discussed in~\cite{opac-b1095246})
+We furthermore define $Z$'s to be independend standard normal random variables satisfying the following equation (plethora of similar decoupling strategies are discussed in~\cite{opac-b1095246})
 \[\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}X_{i_1,\dots,i_H} = \sum_{j=1}^{r_{i_1,\dots,i_H}^{''}} \sqrt{\frac{r_{i_1,\dots,i_H}^{'}}{r_{i_1,\dots,i_H}^{''}}}Z_{i_1,\dots,i_H}^{(j)}. 
@@
 Black line: $u = -E_0(H)$, red line: $u = -E_{\infty}(H)$.
+Notice how narrow band $(-E_0(H),-E_{\infty})$ is.
 Figure must be read in color.}
@@
 \]
-For any fixed $H \geq 3$, the sequence $\{E_k(H)\}_{k\in\mathbb{\Lambda}}$ is strictly decreasing and converges to $E_{\infty}$ as $k \rightarrow \infty$~\cite{AAC2010}.
-We will now define the ground state energy.
 
@@
 \end{figure*}
+
+For any fixed $H \geq 3$, the sequence $\{E_k(H)\}_{k\in\mathbb{\Lambda}}$ is strictly decreasing and converges to $E_{\infty}$ as $k \rightarrow \infty$~\cite{AAC2010}.
+Another important fact is that the band $(-E_0(H),-E_{\infty})$ is very narrow, i.e.
+it is order of magnitudes narrower than band $(-E_{\infty},0)$.
+We will now define the ground state energy.
 

### 2014-10-20 PAPER_AMMLY.tex
Approximation section corrected

@@
 Let $W_i$ be the matrix of weights between $(i - 1)^{\text{th}}$ and $i^{th}$ layers of the network.
-We assume weights are bounded.
 Also, let $\sigma$ denotes the activation function that converts a unit's weighted input to its output activation.
@@
 Random variable $A_{i,j}$ denotes whether path $(i,j)$ is active ($A_{i,j} = 1$) or not ($A_{i,j} = 0$).
-We assume each path is equally likely to be active thus $A_{i,j}$'s will be modelled as Bernoulli random variables with the same probability of success $\rho$.
+For our theoretical analysis we assume that $X$'s are identically distributed such that $X_{i_1,i_2,\dots,i_H}\sim\mathcal{N}(0,1)$.
 
@@
 In the rest of this section we will be establishing a connection between the loss function of the neural network and the Hamiltonian of the spin-glass model.
-Under certain assumptions, that will be introduced and discussed, spin-glass model can be though of as a network approximator.
+Under certain assumptions, that will be introduced and discussed, spin-glass model can be though of as an approximator of a network output.
 We will also provide the measure of quality of this approximation.
@@
 
-Let $\mathcal{W} = \{w_1,w_2,\dots,w_{\Lambda}\}$ be the set of all weights of the network.
-Furthermore let $\mathcal{A}$ denote the set of all $H$-length configuration of weights chosen from $\mathcal{W}$ (order of weights in a configuration does matter).
+In this section we introduce certain assumptions regarding the neural network model.
+These assumptions consider random variables $X$s and $A$s (their distributions and mutual dependencies) as well as they introduce spherical constraint on the model weights.
+We also introduce two other assumptions regarding redundancy of network parameters and their uniformity (details in the text below), both of them are justified by empirical evidence in the literature.
+The aim of this section is to obtain an approximator to the expectation $\mathbb{E}_A[Y]$ which, as will be seen in Section~\ref{subsec:LFSG}, is used in the definition of the loss function of neural network.
+Theorems~\ref{thm:redun} and~\ref{thm:unif} provide some guarantees regarding the quality of this approximation.
+
+\paragraph{Equally likely paths}
+We assume each path in Equation~\ref{eq:befrein} is equally likely to be active thus $A_{i,j}$'s will be modelled as Bernoulli random variables with the same probability of success $\rho$.
+By assuming the independence of $X$'s and $A's$ we get the following
+\begin{equation}
+\mathbb{E}_A[Y] = q\sum_{i=1}^{n_0}\sum_{j = 1}^\gamma X_{i}\rho\prod_{k = 1}^{H}w_{i,j}^{(k)}.
+\label{eq:befrein2}
+\end{equation}
+
+\paragraph{Spherical constraint}
+Let $\mathcal{W} = \{w_1,w_2,\dots,w_{\Lambda}\}$ be the set of all weights of the network. We make a benign assumption that the weights sattisfy the spherical condition 
+\begin{equation}
+\frac{1}{\Lambda}\sum_{i=1}^{\Lambda}w_i^2 = \mathcal{C},
+\label{eq:spherical}
+\end{equation}
+where $\mathcal{C}$ is some positive constant.
+
+\paragraph{Redundancy in network parametrization}
+Let $\mathcal{A}$ denote the set of all $H$-length configuration of weights chosen from $\mathcal{W}$ (order of weights in a configuration does matter).
 Note that the size of $\mathcal{A}$ is therefore $\Lambda^H$.
-Also let $\mathcal{B}$ be a set such that each element correspond to the single configuration of weights from Equation~\ref{eq:befrein}, thus $\mathcal{B} = \{(w_{1,1}^1,w_{1,1}^2,\dots,w_{1,1}^H),(w_{1,2}^1,w_{1,2}^2,\dots,w_{1,2}^H),\dots,\\(w_{n_0,\gamma}^1,w_{n_0,\gamma}^2,\dots,w_{n_0,\gamma}^H)\}$, where every single weight comes from set $\mathcal{W}$.
+Also let $\mathcal{B}$ be a set such that each element correspond to the single configuration of weights from Equation~\ref{eq:befrein2}, thus $\mathcal{B} = \{(w_{1,1}^1,w_{1,1}^2,\dots,w_{1,1}^H),(w_{1,2}^1,w_{1,2}^2,\dots,w_{1,2}^H),\dots,\\(w_{n_0,\gamma}^1,w_{n_0,\gamma}^2,\dots,w_{n_0,\gamma}^H)\}$, where every single weight comes from set $\mathcal{W}$.
 Note that in general there exist elements in $\mathcal{A}$ that will never appear in $\mathcal{B}$ (unless we allow repetition of weights in $\mathcal{W}$).
-Thus Equation~\ref{eq:befrein} can be equivalently written as
-\[Y = q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!r_{i_1,i_2,\dots,i_H}X_{i_1,i_2,\dots,i_H}A_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k},
-\]
-where $r_{i_1,i_2,\dots,i_H}$ denotes whether the configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein} or not thus $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$ and furthermore $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H} = \Psi$.
-Assuming the independence of $X$'s and $A's$ we get
+Thus Equation~\ref{eq:befrein2} can be equivalently written as
 \begin{equation}
-Y_{\Lambda} := \mathbb{E}_A[Y] = q\!\!\!\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!r_{i_1,\dots,i_H}X_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}\!\!w_{i_k}.
+Y_{\Lambda} \!:=\! \mathbb{E}_A[Y] \!=\! q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!\!\!\!\!r_{i_1\!,i_2,\dots,i_H}\!X_{i_1,i_2,\dots,i_H}\rho\!\prod_{k = 1}^{H}\!\!w_{i_k},
 \label{eq:befapprox}
 \end{equation}
+where $r_{i_1,i_2,\dots,i_H}$ denotes whether the configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein2} or not thus $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$ and furthermore $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H} = \Psi$.
 In the notation $Y_{\Lambda}$, index $\Lambda$ refers to the size of set $\mathcal{A}$ (this notation will be helpful later in this section).
-For our theoretical analysis we assume that $X$'s are identically distributed such that $X_{i_1,i_2,\dots,i_H}\sim\mathcal{N}(0,1)$.
 
@@
 
+\paragraph{Uniformity}
 Consider $(s,\epsilon)$-reduction image of $\mathcal{N}$ for some $s \leq \Lambda$ and $\epsilon \in [0,1]$. The output $Y_s$ of the image network can in general be expressed as
@@
 \textcolor{red}{That is because large networks have significantly more modelling power thus small $s$ is a natural form of controlling the overfitting.
-Besides then the data is mapped to a higher dimensional space.} Next we will consider two frequently used loss functions, absolute loss and hinge loss, where we approximate $Y_{\Lambda}$ with $\hat{Y}_s$.
+Besides then the data is mapped to a higher dimensional space.} In the next we will consider two frequently used loss functions, absolute loss and hinge loss, where we approximate $Y_{\Lambda}$ with $\hat{Y}_s$.
 
 \subsection{Loss function as a $H$-spin spherical spin-glass model}
+\label{subsec:LFSG}
 
@@
 where $Y_t$ is a random variable corresponding the true data labeling that takes values $-S$ or $S$, where $S = \sup_{\bf{w}}{\hat{Y}_s}$.
-Also note that in case of the hinge loss $\max$ operator can be modelled as Bernoulli random variable, that we will refer to as $M$, with success ($M = 1$) probability $\rho^{'}$.
+Also note that in case of the hinge loss $\max$ operator can be modelled as Bernoulli random variable, that we will refer to as $M$, with success ($M = 1$) probability $\rho^{'} = \frac{1}{\rho\sqrt{\mathcal{C}^H}}$.
 We assume $M$ is independent of $\hat{Y}_s$.
@@
 \end{eqnarray*}
-Let $\tilde{w}_i = \sqrt[H]{\rho\rho^{'}}w_i$ for all $i = \{1,2,\dots,k\}$.  Thus
+Let $\tilde{w}_i = \sqrt[H]{\rho\rho^{'}}w_i$ for all $i = \{1,2,\dots,k\}$. Note that $\tilde{w}_i = \frac{1}{\sqrt{C}}$. Thus
 \begin{equation}
@@
 \end{equation}
-We furthermore make a benign assumption that the weights sattisfy the spherical condition 
+Note that the spherical assumption in Equation~\ref{eq:spherical} directly implies that
 \begin{equation}
@@
 where the last inequality was obtained by substituting $q = \sqrt{\frac{\Lambda}{\Psi}}$.
-For the analysis $X$'s are assumed to be independent.
 Equation~\ref{eq:spinglass} is the centered Gaussian process on the sphere $\mathcal{S} = S^{\Lambda-1}(\sqrt{\Lambda})$ and is equivalent to the Hamiltonian of the $H$-spin spherical spin-glass model.

### 2014-10-20 PAPER_AMMLY.tex
Approximation section corrected

@@
 We also introduce two other assumptions regarding redundancy of network parameters and their uniformity (details in the text below), both of them are justified by empirical evidence in the literature.
-The aim of this section is to obtain an approximator to the expectation $\mathbb{E}_A[Y]$ which, as will be seen in Section~\ref{subsec:LFSG}, is used in the definition of the loss function of neural network.
+The aim of this section is to obtain an approximator to the expectation $\mathbb{E}_A[Y]$ (note it is still a random variable) which, as will be seen in Section~\ref{subsec:LFSG}, is used in the definition of the loss function of neural network.
 Theorems~\ref{thm:redun} and~\ref{thm:unif} provide some guarantees regarding the quality of this approximation.
@@
 We therefore require that $r_{i_1,\dots,i_H}^{''} \in \{\mathbb{Z}^{+}\cup{0}\}$, $r_{i_1,\dots,i_H}^{''} \geq r_{i_1,\dots,i_H}^{'}$ and $\sum_{i_1,\dots,i_H=1}^{s}r_{i_1,\dots,i_H}^{''} = \Lambda^H$.
-We furthermore define $Z$'s to be independend standard normal random variables satisfying the following equation (plethora of similar decoupling strategies are discussed in~\cite{opac-b1095246})
+\textcolor{red}{We should provide the decoupling inequality as exact equality does not hold!} We furthermore define $Z$'s to be independend standard normal random variables satisfying the following equation (plethora of similar decoupling strategies are discussed in~\cite{opac-b1095246})
 \[\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}X_{i_1,\dots,i_H} = \sum_{j=1}^{r_{i_1,\dots,i_H}^{''}} \sqrt{\frac{r_{i_1,\dots,i_H}^{'}}{r_{i_1,\dots,i_H}^{''}}}Z_{i_1,\dots,i_H}^{(j)}. 

### 2014-10-20 PAPER_AMMLY.tex
Approximation section corrected again

@@
 \frac{1}{\Lambda}\sum_{i=1}^{\Lambda}w_i^2 = \mathcal{C},
-\label{eq:spherical}
+\label{eq:befspherical}
 \end{equation}
@@
 \begin{theorem}
-Let $\mathcal{N}$, whose output is $Y_{\Lambda}$, be the neural network predicting $1$ with probability $p$ and $-1$ otherwise.
-Let $\mathcal{M}$ be its $(s,\epsilon)$-reduction image for some $s \leq \Lambda$ and $\epsilon \in [0,p]$.
+Let $\mathcal{N}$, whose output is $Y_{\Lambda}$, be the neural network predicting $1$ with probability $p$ (without loss of generality assume $p \leq 0.5$) and $-1$ otherwise.
+Let $\mathcal{M}$ be its $(s,\epsilon)$-reduction image for some $s \leq \Lambda$ and $\epsilon \in [0,p)$.
 Then
@@
 and
-\[\mathcal{L}^h_{\Lambda,H}({\bm w}) = \max(0,S-Y_t\hat{Y}_s).
+\[\mathcal{L}^h_{\Lambda,H}({\bm w}) = \max(0,1-Y_t\hat{Y}_s).
 \]
-where $Y_t$ is a random variable corresponding the true data labeling that takes values $-S$ or $S$, where $S = \sup_{\bf{w}}{\hat{Y}_s}$.
+where $Y_t$ is a random variable corresponding the true data labeling that takes values $-S$ or $S$ in case of the absolute loss and $-\frac{1}{S}$ or $\frac{1}{S}$ in case of the hinge loss, where $S = \sup_{\bf{w}}{\hat{Y}_s}$.
 Also note that in case of the hinge loss $\max$ operator can be modelled as Bernoulli random variable, that we will refer to as $M$, with success ($M = 1$) probability $\rho^{'} = \frac{1}{\rho\sqrt{\mathcal{C}^H}}$.
@@
 \mathcal{L}^h_{\Lambda,H}({\bm w}) &=& \mathbb{E}_{M,A}[M(
-S-Y_t\hat{Y}_s)]\\&=& \left \{
+1-Y_t\hat{Y}_s)]\\&=& \left \{
   \begin{tabular}{c}
-  $\!\!\!\!\!\!\mathbb{E}_{M}[M(S - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = S$ \\
-  $\!\mathbb{E}_{M}[M(S + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -S$ \\
+  $\!\!\!\!\!\!\mathbb{E}_{M}[M(1 - \frac{1}{S}\hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = \frac{1}{S}$ \\
+  $\!\mathbb{E}_{M}[M(1 + \frac{1}{S}\hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -\frac{1}{S}$ \\
   \end{tabular}
@@
   \begin{tabular}{c}
-  $\!\!\!\!\!\!\mathbb{E}_{M}[M(S - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = S$ \\
-  $\!\mathbb{E}_{M}[M(S + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -S$ \\
+  $\!\mathbb{E}_{M}[M(s_1 - s_2\hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t  > 0$ \\
+  $\!\mathbb{E}_{M}[M(s_1 + s_2\hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t < 0$ \\
   \end{tabular}
@@
 \]
-where in case of absolute loss $\rho^{'} = 1$. Furthermore, since $X$'s are Gaussian random variables, then so are $-X$'s thus we can further generalize that
+where in case of absolute loss $\rho^{'} = 1$, $s_1 = S$ and $s_2 = 1$, whereas for hinge loss $s_1 = 1$ and $s_2 = \frac{1}{S}$.
+Furthermore, since $X$'s are Gaussian random variables, then so are $-X$'s thus we can further generalize that
 \begin{eqnarray*}
-\mathcal{L}_{\Lambda,H}({\bm w}) \!\!\!\!\!&=&\!\!\!\!\! \mathbb{E}_{M}[M(S + \hat{Y}_s)]\\
-&=& \!\!\!\!\!\rho^{'}S + \rho^{'}\hat{Y}_s\\
-&=& \!\!\!\!\!\rho^{'}S + q\sqrt{\!\!\frac{\Psi}{\Lambda^H}\!\!}\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!Z_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}
+\mathcal{L}_{\Lambda,H}({\bm w}) \!\!\!\!\!&=&\!\!\!\!\! \mathbb{E}_{M}[M(s_1 + s_2\hat{Y}_s)]\\
+&=& \!\!\!\!\!s_1\rho^{'} \!+\! s_2\rho^{'}\hat{Y}_s\\
+&=& \!\!\!\!\!s_1\rho^{'} \!+\! s_2q\sqrt{\!\!\frac{\Psi}{\Lambda^H}\!\!\!\!}\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!Z_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}.
 \end{eqnarray*}
@@
 \begin{equation}
-\mathcal{L}_{\Lambda,H}({\bm w}) = \rho^{'}S + q\sqrt{\!\!\frac{\Psi}{\Lambda^H}\!\!}\sum_{i_1,\dots,i_H=1}^{\Lambda}Z_{i_1,\dots,i_H}\prod_{k = 1}^{H}\tilde{w}_{i_k}.
+\mathcal{L}_{\Lambda,H}({\bm w}) = s_1\rho^{'} \!+\! s_2q\sqrt{\!\!\frac{\Psi}{\Lambda^H}\!\!\!\!}\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!Z_{i_1,\dots,i_H}\prod_{k = 1}^{H}\tilde{w}_{i_k}.
 \label{eq:befloss}
 \end{equation}
-Note that the spherical assumption in Equation~\ref{eq:spherical} directly implies that
+Note that the spherical assumption in Equation~\ref{eq:befspherical} directly implies that
 \begin{equation}
@@
 To simplify the notation in Equation~\ref{eq:befloss} we drop the letter accents and simply denote $\hat{w}$ as $w$.
-We skip constant $\rho^{'}S$ as it does not matter when minimizing the loss function.
+We skip constant $s_1\rho^{'}$ and $s_2$ (remaining constants are preserved for the purpose that will become evident shortly) as it does not matter when minimizing the loss function.
 \begin{equation}
@@
 
-\section{Proof of Theorem~\ref{thm:redun}}
+\section{Proof of Theorem~\ref{thm:unif}}
 \begin{proof}

### 2014-10-21 PAPER_AMMLY.tex
Theorem 3.2 fixed

@@
 where $r_{i_1,i_2,\dots,i_H}$ denotes whether the configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein2} or not thus $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$ and furthermore $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H} = \Psi$.
-In the notation $Y_{\Lambda}$, index $\Lambda$ refers to the size of set $\mathcal{A}$ (this notation will be helpful later in this section).
+In the notation $Y_{\Lambda}$, index $\Lambda$ refers to the number of unique weights of a network (this notation will be helpful later in this section).
 
-Consider a family of networks which have the same graph of connections as network $\mathcal{N}$ but different edge weighting such that they only have $s$ unique weights and $s \leq \Lambda$.
+Consider a family of networks which have the same graph of connections as network $\mathcal{N}$ but different edge weighting such that they only have $s$ unique weights and $s \leq \Lambda$ (through notation analogy expected output of this network will be called $Y_s$).
 It was recently shown~\cite{NIPS2013_5025,DBLP:journals/corr/DentonZBLF14} that for large-size networks large number of network parameters (according to~\cite{NIPS2013_5025} even up to $95\%$) are reduntant and can either be learned from a very small set of unique parameters or even not learned at all with almost no loss in prediction accuracy.
@@
 \begin{theorem}
-Let $\mathcal{N}$, whose output is $Y_{\Lambda}$, be the neural network predicting $1$ with probability $p$ (without loss of generality assume $p \leq 0.5$) and $-1$ otherwise.
-Let $\mathcal{M}$ be its $(s,\epsilon)$-reduction image for some $s \leq \Lambda$ and $\epsilon \in [0,p)$.
-Then
-\[corr(sign(Y_s),sign(Y_{\Lambda})) \geq \frac{2p(1 \!-\! p \!+\! \epsilon) \!-\! \epsilon}{2\sqrt{(p \!+\! \epsilon)(1 \!-\! p \!+\! \epsilon)p(1 \!-\! p)}},
+Let $\mathcal{N}$ be a neural network giving the output whose expectation $Y_{\Lambda}$ is given in Equation~\ref{eq:befapprox}.
+Let $\mathcal{M}$ be its $(s,\epsilon)$-reduction image for some $s \leq \Lambda$ and $\epsilon \in [0,p]$.
+Through analogy, let $Y_s$ be the expected output of network $\mathcal{M}$.
+Then the following holds
+\[corr(sign(Y_s),sign(Y_{\Lambda})) \geq \frac{1-2\epsilon}{1+2\epsilon},
 \]
@@
 \begin{proof}
-Consider two random variables $Z_s = sign(Y_s)$ and $Z_{\Lambda} = sign(Y_{\Lambda})$, where the first one considers the sign of prediction of network $\mathcal{N}$ and the latter considers the sign of prediction of network $\mathcal{M}$.
-Let $\mathcal{X}^{+}$ denote the set of data points for which $\mathcal{N}$ predicts $+1$ and let $\mathcal{X}^{-}$ denote the set of data points for which $\mathcal{N}$ predicts $-1$ ($\mathcal{X}^{+} \cup \mathcal{X}^{-} = \mathcal{X}$, where $\mathcal{X}$ is the entire dataset).
-Also let $p = \frac{|\mathcal{X}^{+}|}{|\mathcal{X}|}$ and without loss of generality assume $p \leq 0.5$.
-Furthermore, let $\mathcal{X}_{\epsilon}^{-}$ denote the dataset for which $Z_{\Lambda} = +1$ and $Z_s = -1$ and $\mathcal{X}_{\epsilon}^{+}$ denote the dataset for which $Z_{\Lambda} = -1$ and $Z_s = +1$, where $\frac{|\mathcal{X}_{\epsilon}^{+}| + |\mathcal{X}_{\epsilon}^{-}|}{\mathcal{X}} = \epsilon$.
+We will first proof the following more general lemma.
+\begin{lemma}
+Let $Y_1$ and $Y_2$ be the outputs of two arbitrary binary classifiers.
+Assume that the first classifiers predicts $1$ with probability $p$ where, without loss of generality, we assume $p \leq 0.5$ and $-1$ otherwise.
+Furthemore, let the prediction accuracy of the second classifier differ from the prediction accuracy of the first classifier by no more than $\epsilon \in [0,p]$.
+Then the following holds
+\[corr(sign(Y_1),sign(Y_2)) \geq \frac{2p(1 \!-\! p \!+\! \epsilon) \!-\! \epsilon}{2\sqrt{(p \!+\! \epsilon)(1 \!-\! p \!+\! \epsilon)p(1 \!-\! p)}}.
+\]
+\label{thm:redun}
+\end{lemma}
+\begin{proof}
+Consider two random variables $Z_1 = sign(Y_1)$ and $Z_2 = sign(Y_2)$.
+Let $\mathcal{X}^{+}$ denote the set of data points for which the first classifier predicts $+1$ and let $\mathcal{X}^{-}$ denote the set of data points for which the first classifier predicts $-1$ ($\mathcal{X}^{+} \cup \mathcal{X}^{-} = \mathcal{X}$, where $\mathcal{X}$ is the entire dataset).
+Also let $p = \frac{|\mathcal{X}^{+}|}{|\mathcal{X}|}$.
+Furthermore, let $\mathcal{X}_{\epsilon}^{-}$ denote the dataset for which $Z_1 = +1$ and $Z_2 = -1$ and $\mathcal{X}_{\epsilon}^{+}$ denote the dataset for which $Z_1 = -1$ and $Z_2 = +1$, where $\frac{|\mathcal{X}_{\epsilon}^{+}| + |\mathcal{X}_{\epsilon}^{-}|}{\mathcal{X}} = \epsilon$.
 Also let $\epsilon^{+} = \frac{|\mathcal{X}_{\epsilon}^{+}|}{\mathcal{X}}$ and $\epsilon^{-} = \frac{|\mathcal{X}_{\epsilon}^{-}|}{\mathcal{X}}$.
 Therefore
-\[Z_{\Lambda} \!=\! \left \{
+\[Z_1 \!=\! \left \{
   \begin{tabular}{c}
@@
 and
-\[Z_s \!=\! \left \{
+\[Z_2 \!=\! \left \{
   \begin{tabular}{c}
@@
 \]
-One can compute that $\mathbb{E}[Z_{\Lambda}] = 2p-1$, $\mathbb{E}[Z_s] = 2(p + \epsilon^{+} - \epsilon^{-}) - 1$, $\mathbb{E}[Z_sZ_{\Lambda}] = 1$, $std(Z_s) = 2\sqrt{p(p-1)}$, and finally $std(Z_\Lambda) = 2\sqrt{(p + \epsilon^{+} - \epsilon^{-})(p + \epsilon^{+} - \epsilon^{-} - 1)}$.
+One can compute that $\mathbb{E}[Z_1] = 2p-1$, $\mathbb{E}[Z_2] = 2(p + \epsilon^{+} - \epsilon^{-}) - 1$, $\mathbb{E}[Z_1Z_2] = 1 - 2\epsilon$, $std(Z_s) = 2\sqrt{p(1-p)}$, and finally $std(Z_\Lambda) = 2\sqrt{(p + \epsilon^{+} - \epsilon^{-})(1 - p - \epsilon^{+} + \epsilon^{-})}$.
 Thus we obtain
-\begin{eqnarray*}
-&&corr(sign(Y_s),sign(Y_{\Lambda})) = corr(Z_s,Z_{\Lambda})\\
-&=& \frac{\mathbb{E}[Z_sZ_{\Lambda}] - \mathbb{E}[Z_s]\mathbb{E}[Z_{\Lambda}]}{std(Z_s)std(Z_{\Lambda})}\\
-&=& \frac{1 - (2(p + \epsilon^{+} - \epsilon^{-}) - 1)(2p-1)}{4\sqrt{(p + \epsilon^{+} - \epsilon^{-})(p + \epsilon^{+} - \epsilon^{-} - 1)p(p-1)}}\\
-&=& \frac{2p + 2(1-2p)(p + \epsilon^{+} - \epsilon^{-})}{4\sqrt{(p + \epsilon^{+} - \epsilon^{-})(1 - p - \epsilon^{+} + \epsilon^{-})p(1 - p)}}\\
-&\geq& \frac{p + (1-2p)(p - \epsilon)}{2\sqrt{(p + \epsilon)(1 - p + \epsilon)p(1 - p)}}\\
-&=& \frac{2p(1 - p + \epsilon) - \epsilon}{2\sqrt{(p + \epsilon)(1 - p + \epsilon)p(1 - p)}}\\
-\end{eqnarray*}
+\begin{eqnarray}
+&&\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!corr(sign(Y_1),sign(Y_2)) = corr(Z_1,Z_2) \nonumber\\
+&\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!=& \!\!\!\!\!\!\!\!\!\!\frac{\mathbb{E}[Z_1Z_2] - \mathbb{E}[Z_1]\mathbb{E}[Z_2]}{std(Z_1)std(Z_2)} \nonumber\\
+&\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!=& \!\!\!\!\!\!\!\!\!\!\frac{1 - 2\epsilon - (1 - 2p)^2 + 2(1 - 2p)(\epsilon^{+} - \epsilon^{-})}{4\sqrt{p(1 - p)(p + \epsilon^{+} - \epsilon^{-})(1 - p - \epsilon^{+} + \epsilon^{-})}} \nonumber\\
+&\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\geq& \!\!\!\!\!\!\!\!\!\!\frac{1 - 2\epsilon - (1 - 2p)^2 - 2(1 - 2p)\epsilon}{4\sqrt{p(1 - p)(p + \epsilon)(1 - p + \epsilon)}}
+\label{eq:tmp}
+\end{eqnarray}
+\end{proof}
+Note that when the first classifier is network $\mathcal{N}$ considered in this paper and $\mathcal{M}$ is its $(s,\epsilon)$-reduction image $\mathbb{E}[Y_1] = 0$ and $\mathbb{E}[Y_2] = 0$ (that follows from the fact that $X$'s in Equation~\ref{eq:befapprox} have zero-mean).
+That implies $p=0.5$ which, when substituted to Equation~\ref{eq:tmp} gives the theorem statement.
 \end{proof}

### 2014-10-21 PAPER_AMMLY.tex
Last thereom fixes

@@
 Note that each path corresponds to a certain set of $H$ weights, which we refer to as a \textit{configuration of weights}, which are multiplied by each other.
-Random variable $A_{i,j}$ denotes whether path $(i,j)$ is active ($A_{i,j} = 1$) or not ($A_{i,j} = 0$).
-For our theoretical analysis we assume that $X$'s are identically distributed such that $X_{i_1,i_2,\dots,i_H}\sim\mathcal{N}(0,1)$.
+Finally, $A_{i,j}$ denotes whether a path $(i,j)$ is active ($A_{i,j} = 1$) or not ($A_{i,j} = 0$).
 
@@
 
-In this section we introduce certain assumptions regarding the neural network model.
+In this section we introduce randomness to the model and assume $X$s and $A$s are random.
+We make certain assumptions regarding the neural network model.
 These assumptions consider random variables $X$s and $A$s (their distributions and mutual dependencies) as well as they introduce spherical constraint on the model weights.
@@
 \end{equation}
+
+\paragraph{Input decomposability}
+We assume each input $X_i$ is a normal random variable such that $X_i\sim\mathcal{N}(0,1)$ and it can be decomposed as follows: 
+\[X_i = \frac{1}{\sqrt{v_i}}\sum_{j=1}^{v_i}Z_i^{(j)}
+\]
+for some positive $v_i$ and $Z$'s being independend identically distributed standard normal random variables.
+Furthermore we assume there exists more than one such decomposition.
+We will denote the set of all values of $v_i$, each taken from different decomposition, as a \textit{decomposition set of $X_i$}.
 
@@
 Consider $(s,\epsilon)$-reduction image of $\mathcal{N}$ for some $s \leq \Lambda$ and $\epsilon \in [0,1]$. The output $Y_s$ of the image network can in general be expressed as
-\[Y_s = q\!\!\!\sum_{i_1,\dots,i_H=1}^{s}\!\!\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}X_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}\!\!w_{i_k},
+\[Y_s = q\!\!\!\sum_{i_1,\dots,i_H=1}^{s}\!\!\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}X_{i_1,\dots,i_H}^{(j)}\rho\prod_{k = 1}^{H}\!\!w_{i_k},
 \]
@@
 We can further rewrite $Y_s$ as follows
-\[Y_s = q\!\!\!\sum_{i_1,\dots,i_H=1}^{s}\!\!\underbrace{\left(\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}\!\!\!X_{i_1,\dots,i_H} + 0 + \dots + 0\right)}_{r_{i_1,\dots,i_H}^{''} \text{summands}}\!\!\rho\prod_{k = 1}^{H}\!\!w_{i_k},
+\[Y_s = q\!\!\!\sum_{i_1,\dots,i_H=1}^{s}\!\!\underbrace{\left(\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}\!\!\!X_{i_1,\dots,i_H}^{(j)} + 0 + \dots + 0\right)}_{r_{i_1,\dots,i_H}^{''} \text{summands}}\!\!\rho\prod_{k = 1}^{H}\!\!w_{i_k},
 \]
@@
 We therefore require that $r_{i_1,\dots,i_H}^{''} \in \{\mathbb{Z}^{+}\cup{0}\}$, $r_{i_1,\dots,i_H}^{''} \geq r_{i_1,\dots,i_H}^{'}$ and $\sum_{i_1,\dots,i_H=1}^{s}r_{i_1,\dots,i_H}^{''} = \Lambda^H$.
-\textcolor{red}{We should provide the decoupling inequality as exact equality does not hold!} We furthermore define $Z$'s to be independend standard normal random variables satisfying the following equation (plethora of similar decoupling strategies are discussed in~\cite{opac-b1095246})
-\[\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}X_{i_1,\dots,i_H} = \sum_{j=1}^{r_{i_1,\dots,i_H}^{''}} \sqrt{\frac{r_{i_1,\dots,i_H}^{'}}{r_{i_1,\dots,i_H}^{''}}}Z_{i_1,\dots,i_H}^{(j)}. 
+Let $\hat{r}_{i_1,\dots,i_H} = \sqrt{\frac{r_{i_1,\dots,i_H}^{'}}{r_{i_1,\dots,i_H}^{''}}}$.
+We assume that $\frac{1}{\hat{r}_{i_1,\dots,i_H}^2}$ belongs to the decomposition set of $X_{i_1,\dots,i_H}^{(j)}$.
+This enables us to prove (proof is in the Supplementary material) the following result that we give as a lemma
+\begin{lemma}
+The decomposability of the input $X_{i_1,\dots,i_H}^{(j)}$ implies that
+\[Y_s = q\sum_{i_1,\dots,i_H=1}^{\Lambda}\hat{r}_{i_1,\dots,i_H}Z_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
 \]
-Let $\hat{r}_{i_1,\dots,i_H}^{(j)} = \sqrt{\frac{r_{i_1,\dots,i_H}^{'}}{r_{i_1,\dots,i_H}^{''}}}$. Therefore
-\begin{eqnarray*}
-Y_s &=& q\sum_{i_1,\dots,i_H=1}^{s}\sum_{j=1}^{r_{i_1,\dots,i_H}^{''}}\hat{r}_{i_1,\dots,i_H}^{(j)}Z_{i_1,\dots,i_H}^{(j)}\rho\prod_{k = 1}^{H}w_{i_k}\\
-&=& \sum_{i_1,\dots,i_H=1}^{\Lambda}\hat{r}_{i_1,\dots,i_H}Z_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
-\end{eqnarray*}
-where the last step comes from re-indexing terms.
+where $Z$'s are independend standard normal random variables.
+\label{lem:tmp2}
+\end{lemma}
 
@@
 \]
-\label{thm:redun}
 \end{lemma}
@@
 \end{proof}
+
+\section{Proof of Lemma~\ref{lem:tmp2}}
+
+The decomposability of $X_{i_1,\dots,i_H}^{(j)}$ implies that for independend standard normal random variables $Z$'s the following holds:
+\begin{eqnarray*}
+\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}X_{i_1,\dots,i_H}^{(j)} &\!\!\!\!\!=& \!\!\!\!\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}\hat{r}_{i_1,\dots,i_H}\sum_{k=1}^{\frac{1}{\hat{r}_{i_1,\dots,i_H}^2}}Z_{i_1,\dots,i_H}^{(k,j)}\\
+&\!\!\!\!\!=& \!\!\!\!\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{''}}\hat{r}_{i_1,\dots,i_H}Z_{i_1,\dots,i_H}^{(j)},
+\end{eqnarray*}
+where the last step comes from combining both summations and re-indexing the summands. Therefore
+\begin{eqnarray*}
+Y_s &=& q\sum_{i_1,\dots,i_H=1}^{s}\sum_{j=1}^{r_{i_1,\dots,i_H}^{''}}\hat{r}_{i_1,\dots,i_H}Z_{i_1,\dots,i_H}^{(j)}\rho\prod_{k = 1}^{H}w_{i_k}\\
+&=& \sum_{i_1,\dots,i_H=1}^{\Lambda}\hat{r}_{i_1,\dots,i_H}Z_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
+\end{eqnarray*}
+where the last step comes again from combining both summations and re-indexing the summands.
 

### 2014-10-21 PAPER_AMMLY.tex
theory simplification

@@
 We make certain assumptions regarding the neural network model.
-These assumptions consider random variables $X$s and $A$s (their distributions and mutual dependencies) as well as they introduce spherical constraint on the model weights.
+These assumptions consider random variables $X$s and $A$s (their distributions and mutual dependencies and we emphasize that all independence assumptions we make are standard in the literature~\cite{opac-b1095246}) as well as they introduce spherical constraint on the model weights.
 We also introduce two other assumptions regarding redundancy of network parameters and their uniformity (details in the text below), both of them are justified by empirical evidence in the literature.
@@
 Theorems~\ref{thm:redun} and~\ref{thm:unif} provide some guarantees regarding the quality of this approximation.
+
+\paragraph{Input}
+We assume each input $X_i$ is a normal random variable such that $X_i\sim N(0,1)$.
 
@@
 \end{equation}
-
-\paragraph{Input decomposability}
-We assume each input $X_i$ is a normal random variable such that $X_i\sim\mathcal{N}(0,1)$ and it can be decomposed as follows: 
-\[X_i = \frac{1}{\sqrt{v_i}}\sum_{j=1}^{v_i}Z_i^{(j)}
-\]
-for some positive $v_i$ and $Z$'s being independend identically distributed standard normal random variables.
-Furthermore we assume there exists more than one such decomposition.
-We will denote the set of all values of $v_i$, each taken from different decomposition, as a \textit{decomposition set of $X_i$}.
 
@@
 We therefore require that $r_{i_1,\dots,i_H}^{''} \in \{\mathbb{Z}^{+}\cup{0}\}$, $r_{i_1,\dots,i_H}^{''} \geq r_{i_1,\dots,i_H}^{'}$ and $\sum_{i_1,\dots,i_H=1}^{s}r_{i_1,\dots,i_H}^{''} = \Lambda^H$.
-Let $\hat{r}_{i_1,\dots,i_H} = \sqrt{\frac{r_{i_1,\dots,i_H}^{'}}{r_{i_1,\dots,i_H}^{''}}}$.
-We assume that $\frac{1}{\hat{r}_{i_1,\dots,i_H}^2}$ belongs to the decomposition set of $X_{i_1,\dots,i_H}^{(j)}$.
-This enables us to prove (proof is in the Supplementary material) the following result that we give as a lemma
+Let $\hat{r}_{i_1,\dots,i_H} = \sqrt{\frac{r_{i_1,\dots,i_H}^{'}}{r_{i_1,\dots,i_H}^{''}}}$ and for convinience assume that $\frac{1}{\hat{r}_{i_1,\dots,i_H}^2} \in \mathbb{Z}^{+}$.
+By the infinite divisibility property of normal distribution we can decompose each $X_{i_1,\dots,i_H}^{(j)}$ as the sum of $\frac{1}{\hat{r}_{i_1,\dots,i_H}^2}$ independent normal random variables (we call them $Z$'s).
+Thus
+\[X_{i_1,\dots,i_H}^{(j)} = \hat{r}_{i_1,\dots,i_H}\sum_{k=1}^{\frac{1}{\hat{r}_{i_1,\dots,i_H}^2}}Z_{i_1,\dots,i_H}^{(j,k)}.
+\]
+Furthemore, this decomposition is not unique. This enables us to prove (proof is in the Supplementary material) the following result that we give as a lemma.
 \begin{lemma}
@@
 \begin{eqnarray*}
-\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}X_{i_1,\dots,i_H}^{(j)} &\!\!\!\!\!=& \!\!\!\!\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}\hat{r}_{i_1,\dots,i_H}\sum_{k=1}^{\frac{1}{\hat{r}_{i_1,\dots,i_H}^2}}Z_{i_1,\dots,i_H}^{(k,j)}\\
+\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}X_{i_1,\dots,i_H}^{(j)} &\!\!\!\!\!=& \!\!\!\!\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}\hat{r}_{i_1,\dots,i_H}\sum_{k=1}^{\frac{1}{\hat{r}_{i_1,\dots,i_H}^2}}Z_{i_1,\dots,i_H}^{(j,k)}\\
 &\!\!\!\!\!=& \!\!\!\!\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{''}}\hat{r}_{i_1,\dots,i_H}Z_{i_1,\dots,i_H}^{(j)},

### 2014-10-22 PAPER_AMMLY.tex
Significant simplifications

--- 2014-10-21 PAPER_AMMLY.tex
@@
 Despite their modeling power, the interest in learning with early neural network significantly weakened when it was shown that they have several limitations including: i) learning limitations such as the inability of single-layer networks to solve the XOR problem~\cite{minsky69perceptrons}, ii) long training time of large networks and proness to overfitting~\cite{JMLR:v15:srivastava14a}, and iii) getting stuck in poor-quality local optima or saddle points while training~\cite{Larochelle:2009:EST:1577069.1577070}.
-Today many of these limitations can be solved with the development of new efficient training strategies (among them backpropagation algorithm~\cite{Werbos:74} which enables to solve the XOR problem), fast GPU-based implementations significantly reducing the training time, and techniques preventing the overfitting such as dropout (e.g.~\cite{JMLR:v15:srivastava14a}).
+Today many of these limitations can be solved with the development of new efficient training strategies (among them backpropagation algorithm~\cite{Werbos:74} which enables to solve the XOR problem), fast GPU-based implementations significantly reducing the training time, and techniques preventing the overfitting such as dropout (e.g.~\cite{journals/corr/abs-1207-0580,JMLR:v15:srivastava14a}).
 Therefore, after a long period of scepticism, the paradigm of learning with neural networks gained significant attention in recent years resulting in many new architectures, such as convolutional networks~\cite{lecun-gradientbased-learning-applied-1998}, recurrent neural networks~\cite{Graves:2009:NCS:1525650.1525782}, deep feedforward neural networks (e.g.~\cite{DBLP:journals/corr/Schmidhuber14} or wide networks~\cite{Huang14}, where the most fundamental difference between them and their early predecessors lies in a much larger parameter space (throughout the paper we refer to the number of network parameters as network size).
@@
 \]
-where $q = \sqrt{\frac{n_0n_1 + n_1n_2 + ... + n_{H-1}n_H}{n_0n_1...n_H}}$ is simply a normalization factor. The same expression for the output of the network can be re-expressed in the following way:
+where $q = \sqrt{(n_0n_1...n_H)^{(H-1)/2H}}$ is simply a normalization factor. The same expression for the output of the network can be re-expressed in the following way:
 \begin{equation}
@@
 Note that each path corresponds to a certain set of $H$ weights, which we refer to as a \textit{configuration of weights}, which are multiplied by each other.
-Random variable $A_{i,j}$ denotes whether path $(i,j)$ is active ($A_{i,j} = 1$) or not ($A_{i,j} = 0$).
-For our theoretical analysis we assume that $X$'s are identically distributed such that $X_{i_1,i_2,\dots,i_H}\sim\mathcal{N}(0,1)$.
+Finally, $A_{i,j}$ denotes whether a path $(i,j)$ is active ($A_{i,j} = 1$) or not ($A_{i,j} = 0$).
 
 \begin{definition}
-The mass of the network $\Psi$ is the total number of all paths between all network inputs and outputs: $\Psi = \prod_{i=0}^Hn_i$.
+The mass of the network $\Psi$ is the total number of all paths between all network inputs and outputs: $\Psi = \prod_{i=0}^Hn_i$. We will also denote $\Lambda$ to be $\Lambda = \sqrt[H]{\Psi}$.
 \end{definition}
@@
 \begin{definition}
-The size of the network $\Lambda$ is the total number of network parameters: $\Lambda = \sum_{i=0}^{H-1}n_in_{i+1}$.
+The size of the network $N$ is the total number of network parameters: $N = \sum_{i=0}^{H-1}n_in_{i+1}$.
 \end{definition}
@@
 Let $\Psi$ be the mass of the network, $d$ be the number of network inputs and $H$ be the depth of the network. The size of the network is bounded as
-\[\Psi^2\frac{1}{d} \geq \Lambda \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}} \geq \sqrt[H]{\Psi}.
+\[\Psi^2\frac{1}{d} \geq N \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}} \geq \sqrt[H]{\Psi} = \Lambda.
 \]
@@
 \end{theorem}
+\begin{corollary}
+For bounded network depth $H$, $\Lambda \rightarrow \infty$ iff $\Psi \rightarrow \infty$.
+For bounded network depth $H$, if the mass of the network $\Psi$ goes to $\infty$ ($\Psi \rightarrow \infty$) then the size of the network also goes to $\infty$ ($N \rightarrow \infty$) (equivalently $\Lambda \rightarrow \infty$ implies $N \rightarrow \infty$).
+\end{corollary}
 
@@
 
-\paragraph{Equally likely paths}
+\paragraph{Input}
+We assume each input $X_i$ is a normal random variable such that $X_i\sim N(0,1)$.
+
+\paragraph{Paths}
 We assume each path in Equation~\ref{eq:befrein} is equally likely to be active thus $A_{i,j}$'s will be modelled as Bernoulli random variables with the same probability of success $\rho$.
@@
 \end{equation}
-
-\paragraph{Spherical constraint}
-Let $\mathcal{W} = \{w_1,w_2,\dots,w_{\Lambda}\}$ be the set of all weights of the network. We make a benign assumption that the weights sattisfy the spherical condition 
-\begin{equation}
-\frac{1}{\Lambda}\sum_{i=1}^{\Lambda}w_i^2 = \mathcal{C},
-\label{eq:befspherical}
-\end{equation}
-where $\mathcal{C}$ is some positive constant.
+We furthermore decouple~\cite{opac-b1095246} the paths by assuming their mutual independence. \textcolor{red}{We might wanna write more.}
 
 \paragraph{Redundancy in network parametrization}
+Let $\mathcal{W} = \{w_1,w_2,\dots,w_{\Lambda}\}$ be the set of all weights of the network.
 Let $\mathcal{A}$ denote the set of all $H$-length configuration of weights chosen from $\mathcal{W}$ (order of weights in a configuration does matter).
-Note that the size of $\mathcal{A}$ is therefore $\Lambda^H$.
+Note that the size of $\mathcal{A}$ is therefore $N^H$.
 Also let $\mathcal{B}$ be a set such that each element correspond to the single configuration of weights from Equation~\ref{eq:befrein2}, thus $\mathcal{B} = \{(w_{1,1}^1,w_{1,1}^2,\dots,w_{1,1}^H),(w_{1,2}^1,w_{1,2}^2,\dots,w_{1,2}^H),\dots,\\(w_{n_0,\gamma}^1,w_{n_0,\gamma}^2,\dots,w_{n_0,\gamma}^H)\}$, where every single weight comes from set $\mathcal{W}$.
@@
 \begin{equation}
-Y_{\Lambda} \!:=\! \mathbb{E}_A[Y] \!=\! q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!\!\!\!\!r_{i_1\!,i_2,\dots,i_H}\!X_{i_1,i_2,\dots,i_H}\rho\!\prod_{k = 1}^{H}\!\!w_{i_k},
+Y_{\Lambda} \!:=\!
+\mathbb{E}_A[Y] \!=\!
+q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{N}\!\!\!\!\!\!\!\sum_{j = 1}^{r_{i_1\!,i_2,\dots,i_H}}\!\!\!\!\!X_{i_1,i_2,\dots,i_H}^{(j)}\rho\!\prod_{k = 1}^{H}\!\!w_{i_k}.
 \label{eq:befapprox}
 \end{equation}
-where $r_{i_1,i_2,\dots,i_H}$ denotes whether the configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein2} or not thus $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$ and furthermore $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H} = \Psi$.
-In the notation $Y_{\Lambda}$, index $\Lambda$ refers to the number of unique weights of a network (this notation will be helpful later in this section).
+We will now explain the notation.
+It is overcomplicated for purpose, as this notation will be useful later on.
+$r_{i_1,i_2,\dots,i_H}$ denotes whether the configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein2} or not, thus $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$, and $\{X_{i_1,i_2,\dots,i_H}^{(j)}\}_{j=1}^{r_{i_1,i_2,\dots,i_H}}$ denote a set of random variables corresponding to the same weight configuration (since $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$ this set has at most one element).
+Also $r_{i_1,i_2,\dots,i_H} = 0$ implies that summand $X_{i_1,i_2,\dots,i_H}^{(j)}\rho\prod_{k = 1}^{H}w_{i_k}$ is zeroed out).
+Note that $\sum_{j = 1}^{r_{i_1\!,i_2,\dots,i_H}}X_{i_1,i_2,\dots,i_H}^{(j)}$ could be replaced by $r_{i_1\!,i_2,\dots,i_H}X_{i_1,i_2,\dots,i_H}$ since $r_{i_1,i_2,\dots,i_H}$, but we choose this notation on purpose as it will be helpful later on.
+Furthermore, the following condition has to be satisfied: $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H} = \Psi$.
+In the notation $Y_{\Lambda}$, index $\Lambda$ refers to the number of unique weights of a network (this notation will also be helpful later).
 
@@
 \paragraph{Uniformity}
-Consider $(s,\epsilon)$-reduction image of $\mathcal{N}$ for some $s \leq \Lambda$ and $\epsilon \in [0,1]$. The output $Y_s$ of the image network can in general be expressed as
-\[Y_s = q\!\!\!\sum_{i_1,\dots,i_H=1}^{s}\!\!\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}X_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}\!\!w_{i_k},
+Consider network $\mathcal{M}$ to be a $(s,\epsilon)$-reduction image of $\mathcal{N}$ for some $s \leq \Lambda$ and $\epsilon \in [0,1]$.
+The output $Y_s$ of the image network can in general be expressed as
+\[Y_s = q\sum_{i_1,\dots,i_H=1}^{s}\sum_{j=1}^{t_{i_1,\dots,i_H}}X_{i_1,\dots,i_H}^{(j)}\rho\prod_{k = 1}^{H}w_{i_k},
 \]
-where $r_{i_1,\dots,i_H}^{'} \in \{\mathbb{Z}^{+}\cup{0}\}$ is the number of times each configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ repeats in Equation~\ref{eq:befapprox} and $\sum_{i_1,\dots,i_H=1}^{s}r_{i_1,\dots,i_H}^{'} = \Psi$.
-We can further rewrite $Y_s$ as follows
-\[Y_s = q\!\!\!\sum_{i_1,\dots,i_H=1}^{s}\!\!\underbrace{\left(\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}\!\!\!X_{i_1,\dots,i_H} + 0 + \dots + 0\right)}_{r_{i_1,\dots,i_H}^{''} \text{summands}}\!\!\rho\prod_{k = 1}^{H}\!\!w_{i_k},
-\]
-where $r_{i_1,\dots,i_H}^{''} \in \{\mathbb{Z}^{+}\cup{0}\}$ is the number of times each configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ would repeat in Equation~\ref{eq:befapprox} if all $r_{i_1,\dots,i_H}$ would be equal to $1$ and $\mathcal{W}$ would have $s$ unique weights and the remaining $(\Lambda - s)$ weights were repetitions\footnote{Note that each $r_{i_1,\dots,i_H}^{''}$ is not uniquely defined here as one could consider many different ways of constructing $\mathcal{W}$ by repeating the same weights different times.}.
-We therefore require that $r_{i_1,\dots,i_H}^{''} \in \{\mathbb{Z}^{+}\cup{0}\}$, $r_{i_1,\dots,i_H}^{''} \geq r_{i_1,\dots,i_H}^{'}$ and $\sum_{i_1,\dots,i_H=1}^{s}r_{i_1,\dots,i_H}^{''} = \Lambda^H$.
-\textcolor{red}{We should provide the decoupling inequality as exact equality does not hold!} We furthermore define $Z$'s to be independend standard normal random variables satisfying the following equation (plethora of similar decoupling strategies are discussed in~\cite{opac-b1095246})
-\[\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}X_{i_1,\dots,i_H} = \sum_{j=1}^{r_{i_1,\dots,i_H}^{''}} \sqrt{\frac{r_{i_1,\dots,i_H}^{'}}{r_{i_1,\dots,i_H}^{''}}}Z_{i_1,\dots,i_H}^{(j)}. 
-\]
-Let $\hat{r}_{i_1,\dots,i_H}^{(j)} = \sqrt{\frac{r_{i_1,\dots,i_H}^{'}}{r_{i_1,\dots,i_H}^{''}}}$. Therefore
-\begin{eqnarray*}
-Y_s &=& q\sum_{i_1,\dots,i_H=1}^{s}\sum_{j=1}^{r_{i_1,\dots,i_H}^{''}}\hat{r}_{i_1,\dots,i_H}^{(j)}Z_{i_1,\dots,i_H}^{(j)}\rho\prod_{k = 1}^{H}w_{i_k}\\
-&=& \sum_{i_1,\dots,i_H=1}^{\Lambda}\hat{r}_{i_1,\dots,i_H}Z_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
-\end{eqnarray*}
-where the last step comes from re-indexing terms.
-
-Finally we assume that unique weights are close to being evenly distributed on the graph of connections of network $\mathcal{M}$.
+where $t_{i_1,\dots,i_H} \in \{\mathbb{Z}^{+}\cup{0}\}$ is the number of times each configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ repeats in Equation~\ref{eq:befapprox} and $\sum_{i_1,\dots,i_H=1}^{s}t_{i_1,\dots,i_H} = \Psi$.
+We assume that unique weights are close to being evenly distributed on the graph of connections of network $\mathcal{M}$.
 We call this assumption a \textit{uniformity assumption} (note it is analogous to the maximum entropy assumption).
 This assumption is in general consistent with the approach in~\cite{NIPS2013_5025}.
-To be more specific, this assumption implies that for all $(i_1,i_2,\dots,i_H):i_1,i_2,\dots,i_H \in \{1,2,\dots,H\}$ there exists non-negative constant $c$ and $\delta \in [0,1]$ such that the following holds
+In particular, this assumption implies that for all $(i_1,i_2,\dots,i_H):i_1,i_2,\dots,i_H \in \{1,2,\dots,s\}$ there exists a positive constant $c \geq 1$ such that the following holds
 \begin{equation}
-c\delta\sqrt{\frac{\Psi}{\Lambda^H}} \leq \hat{r}_{i_1,i_2,\dots,i_H} \leq c\sqrt{\frac{\Psi}{\Lambda^H}},
+\frac{1}{c}\cdot\frac{\Psi}{s^H} \leq t_{i_1,i_2,\dots,i_H} \leq c\cdot\frac{\Psi}{s^H}.
 \label{eq:uniform}
 \end{equation}
-where the factor $\sqrt{\frac{\Psi}{\Lambda^H}}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus every node has equal probability of being adjacent to an edge with any of the unique weights) it holds that $\hat{r}_{i_1,i_2,\dots,i_H} = \sqrt{\frac{\Psi}{\Lambda^H}}$.
-Note that this condition can be sattified with large $\delta$ (close to $0$) if $s$ is sufficiently small.
+The factor $\sqrt{\frac{\Psi}{s^H}}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus with high probability every node is adjacent to an edge with any of the unique weights) it holds that $\hat{r}_{i_1,i_2,\dots,i_H} = \sqrt{\frac{\Psi}{s^H}}$.
+Note that this condition can be sattified with small $c$ (close to $1$) if $s$ is sufficiently small.
 
-Consider therefore an expression as follows
+For simplicity assume $\frac{\Psi}{s^H} \in \mathbb{Z}^{+}$ and $\sqrt[H]{\Psi} \in \mathbb{Z}^{+}$. Consider therefore an expression as follows
 \begin{equation}
-\hat{Y}_s = q\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}Z_{i_1,i_2,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
+\hat{Y}_s = q\sum_{i_1,\dots,i_H=1}^{s}\sum_{j=1}^{\frac{\Psi}{s^H}}X_{i_1,\dots,i_H}^{(j)}\rho\prod_{k = 1}^{H}w_{i_k},
 \label{eq:approx}
 \end{equation}
-which can be thought of as an output of some network $\mathcal{M}$ where the weights are still chosen from $\mathcal{A}$ but there are only $s$ unique weights in $\mathcal{A}$ among the total of $\Lambda$ weights, and furthermore every $H$ - length configuration of weights chosen from $\mathcal{A}$ is equally likely.
-Then the following theorem (Theorem~\ref{thm:unif}) captures the connection between $\hat{Y}_s$ and $Y_{\Lambda}$.
+which corresponds to a network for which the lower-bound and upper-bound in Equation~\ref{eq:uniform} match.
+Note that one can combine both summations in Equation~\ref{eq:approx} and re-index this equation to obtain
+\begin{equation}
+\hat{Y}_s = q\sum_{i_1,\dots,i_H=1}^{\Lambda}X_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k}.
+\label{eq:approxfinal}
+\end{equation}
+The following theorem (Theorem~\ref{thm:unif}) captures the connection between $\hat{Y}_s$ and $Y_{s}$.
 
 \begin{theorem}
-Under the uniformity assumption of Equation~\ref{eq:uniform}, random variable $\hat{Y}_s$ in Equation~\ref{eq:approx} and random variable $Y_{\Lambda}$ in Equation~\ref{eq:befapprox} sattisy the following
-\[corr(\hat{Y}_s,Y_{\Lambda}) \geq \delta
+Under the uniformity assumption of Equation~\ref{eq:uniform}, random variable $\hat{Y}_s$ in Equation~\ref{eq:approx} and random variable $Y_s$ in Equation~\ref{eq:befapprox} sattisy the following
+\[corr(\hat{Y}_s,Y_s) \geq \frac{1}{c^2}
 \]
@@
 \end{theorem}
+We will refer to $\hat{Y}_s$ as an $(s,\epsilon,\delta)$-\textit{approximator} of $Y_{\Lambda}$, where the quality of this approximation is captured in Theorems~\ref{thm:redun} and~\ref{thm:unif}.
+Intuitively, for large networks (our analysis in Section~\ref{sec:theory} considers $\Lambda \rightarrow \infty$) one would expect $s$ to be small enough to simultaneously guarantee sufficiently small (close to $1$) $c$ and preserve good accuracy (small $\epsilon$).
+\textcolor{red}{That is because large networks have significantly more modelling power thus small $s$ is a natural form of controlling the overfitting.
+Besides then the data is mapped to a higher dimensional space.}
 
-We will refer to $\hat{Y}_s$ as an $(s,\epsilon,\delta)$-\textit{approximator} of $Y_{\Lambda}$, where the quality of this approximation is captured in Theorems~\ref{thm:redun} and~\ref{thm:unif}.
-Intuitively, for large-size networks (our analysis in Section~\ref{sec:theory} considers $\Lambda \rightarrow \infty$) one would expect $s$ to be small enough to simultaneously guarantee sufficiently large (close to $1$) $\delta$ and preserve good accuracy (small $\epsilon$).
-\textcolor{red}{That is because large networks have significantly more modelling power thus small $s$ is a natural form of controlling the overfitting.
-Besides then the data is mapped to a higher dimensional space.} In the next we will consider two frequently used loss functions, absolute loss and hinge loss, where we approximate $Y_{\Lambda}$ with $\hat{Y}_s$.
+\paragraph{Spherical constraint}
+We finally make a benign assumption that the weights sattisfy the spherical condition 
+\begin{equation}
+\frac{1}{\Lambda}\sum_{i=1}^{\Lambda}w_i^2 = \mathcal{C},
+\label{eq:befspherical}
+\end{equation}
+where $\mathcal{C}$ is some positive constant.
+
+In the next we will consider two frequently used loss functions, absolute loss and hinge loss, where we approximate $Y_{\Lambda}$ with $\hat{Y}_s$.
 
@@
 \]
-where $Y_t$ is a random variable corresponding the true data labeling that takes values $-S$ or $S$ in case of the absolute loss and $-\frac{1}{S}$ or $\frac{1}{S}$ in case of the hinge loss, where $S = \sup_{\bf{w}}{\hat{Y}_s}$.
+where $Y_t$ is a random variable corresponding the true data labeling that takes values $-S$ or $S$ in case of the absolute loss and $-1$ or $1$ in case of the hinge loss, where $S = \sup_{\bf{w}}{\hat{Y}_s}$.
 Also note that in case of the hinge loss $\max$ operator can be modelled as Bernoulli random variable, that we will refer to as $M$, with success ($M = 1$) probability $\rho^{'} = \frac{1}{\rho\sqrt{\mathcal{C}^H}}$.
@@
   \begin{tabular}{c}
-  $\!\!\!\!\!\!\mathbb{E}_{M}[M(1 - \frac{1}{S}\hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = \frac{1}{S}$ \\
-  $\!\mathbb{E}_{M}[M(1 + \frac{1}{S}\hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -\frac{1}{S}$ \\
+  $\!\!\!\!\!\!\mathbb{E}_{M}[M(1 - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = 1$ \\
+  $\!\mathbb{E}_{M}[M(1 + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -1$ \\
   \end{tabular}
@@
   \begin{tabular}{c}
-  $\!\mathbb{E}_{M}[M(s_1 - s_2\hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t  > 0$ \\
-  $\!\mathbb{E}_{M}[M(s_1 + s_2\hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t < 0$ \\
+  $\!\mathbb{E}_{M}[M(S - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t  > 0$ \\
+  $\!\mathbb{E}_{M}[M(S + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t < 0$ \\
   \end{tabular}
@@
 \]
-where in case of absolute loss $\rho^{'} = 1$, $s_1 = S$ and $s_2 = 1$, whereas for hinge loss $s_1 = 1$ and $s_2 = \frac{1}{S}$.
-Furthermore, since $X$'s are Gaussian random variables, then so are $-X$'s thus we can further generalize that
+where in case of the absolute loss $\rho^{'} = 1$ and in case of the hinge loss $S = 1$. Furthermore, since $X$'s are Gaussian random variables, then so are $-X$'s thus we can further generalize that
 \begin{eqnarray*}
-\mathcal{L}_{\Lambda,H}({\bm w}) \!\!\!\!\!&=&\!\!\!\!\! \mathbb{E}_{M}[M(s_1 + s_2\hat{Y}_s)]\\
-&=& \!\!\!\!\!s_1\rho^{'} \!+\! s_2\rho^{'}\hat{Y}_s\\
-&=& \!\!\!\!\!s_1\rho^{'} \!+\! s_2q\sqrt{\!\!\frac{\Psi}{\Lambda^H}\!\!\!\!}\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!Z_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}.
+\mathcal{L}_{\Lambda,H}({\bm w}) \!\!\!\!\!&=&\!\!\!\!\! \mathbb{E}_{M}[M(S + \hat{Y}_s)]\\
+&=& \!\!\!\!\!S\rho^{'} \!+\! \rho^{'}\hat{Y}_s\\
+&=& \!\!\!\!\!S\rho^{'} \!+\! q\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!X_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}.
 \end{eqnarray*}
@@
 \begin{equation}
-\mathcal{L}_{\Lambda,H}({\bm w}) = s_1\rho^{'} \!+\! s_2q\sqrt{\!\!\frac{\Psi}{\Lambda^H}\!\!\!\!}\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!Z_{i_1,\dots,i_H}\prod_{k = 1}^{H}\tilde{w}_{i_k}.
+\mathcal{L}_{\Lambda,H}({\bm w}) = S\rho^{'} + q\sum_{i_1,\dots,i_H=1}^{\Lambda}X_{i_1,\dots,i_H}\prod_{k = 1}^{H}\tilde{w}_{i_k}.
 \label{eq:befloss}
@@
 To simplify the notation in Equation~\ref{eq:befloss} we drop the letter accents and simply denote $\hat{w}$ as $w$.
-We skip constant $s_1\rho^{'}$ and $s_2$ (remaining constants are preserved for the purpose that will become evident shortly) as it does not matter when minimizing the loss function.
+We skip constant $S\rho^{'}$ as it does not matter when minimizing the loss function.
+After substituting $q = \frac{1}{\Psi^{(H-1)/2H}}$ we obtain
 \begin{equation}
-\mathcal{L}_{\Lambda,H}({\bm w}) = \frac{1}{\Lambda^{(H-1)/2}}\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!Z_{i_1,i_2,\dots,i_H}w_{i_1}w_{i_2}\dots\!w_{i_H},
+\mathcal{L}_{\!\Lambda,H}({\bm w}) \!=\!
+\frac{1}{\Lambda^{\!(H\!-\!1)/2}}\!\!\!\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!\!\!\!\!Z_{i_1,i_2,\dots,i_H}\!w_{i_1}\!w_{i_2}\!\dots\!w_{i_H},
 \label{eq:spinglass}
 \end{equation}
-where the last inequality was obtained by substituting $q = \sqrt{\frac{\Lambda}{\Psi}}$.
 Equation~\ref{eq:spinglass} is the centered Gaussian process on the sphere $\mathcal{S} = S^{\Lambda-1}(\sqrt{\Lambda})$ and is equivalent to the Hamiltonian of the $H$-spin spherical spin-glass model.
@@
 Note that $\mathbb{E}[\hat{Y}_s] = 0$ and $\mathbb{E}[Y_{\Lambda}] = 0$. Furthermore
-\[\mathbb{E}[\hat{Y}_sY_{\Lambda}] = q^2\rho^2\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}\hat{r}_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2
+\[\mathbb{E}[\hat{Y}_sY_{\Lambda}] = q^2\rho^2\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\min\left(\frac{\Psi}{\Lambda^H},t_{i_1,i_2,\dots,i_H}\right)\prod_{k = 1}^{H}w_{i_k}^2
 \]
@@
 \]
-\[std(Y_{\Lambda}) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\hat{r}_{i_1,i_2,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2}.
+\[std(Y_{\Lambda}) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}t_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2}.
 \]
@@
 &\!\!\!\!\!\!\!\!\!=&\!\!\!\!\!\!\!
-\frac{\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}\hat{r}_{i_1,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2}{\sqrt{\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2\right)\!\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\hat{r}_{i_1,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2\right)}}\\
-&\!\!\!\!\!\!\!\!\geq& \delta, 
+\frac{\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\min\left(\frac{\Psi}{\Lambda^H},t_{i_1,\dots,i_H}\right)\prod_{k = 1}^{H}w_{i_k}^2}{\sqrt{\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2\right)\!\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!t_{i_1,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2\right)}}\\
+&\!\!\!\!\!\!\!\!\geq& \frac{1}{c^2}, 
 \end{eqnarray*}
@@
 \end{proof}
-
-\begin{comment}
-\section{Approximation of 2-spin Spin Glasses by 1-layer Neural Networks}
-
-The Hamiltonian of a H-spin glass is given by
-
-\begin{equation}
- S_H(w) = \sum_{i_1,...,i_H}^N x_{i_1,...,i_H} w_{i_1} \cdot ... \cdot w_{i_H}
-\end{equation}
-and the output of a deep linear network with $H$ layers by 
-\begin{equation}
- Y_H(w) = \sum_{p = (i_1,...,i_H) \in \mathcal{P}} x_{i_1,...,i_H} w_{i_1} \cdot ... \cdot w_{i_H}
-\end{equation}
-
-Here $\mathcal{P}$ denotes the set of all paths from inputs to outputs in the network. Let $\mathcal{U} = \{ w_{i_1} \cdot ... \cdot w_{i_H} : 1 \leq i_1,...,i_H \leq N \} $.
-Note that the number of terms in the sum $S_H(w)$ is equal to $|\mathcal{U}| = N^H$ and the number of terms in $Y_H(w)$ is equal to $|\mathcal{P}|$.
-
-\begin{definition}
- Let $P_1(w), P_2(w)$ be random polynomials in $w$, where $w \in \mathbb{R}^N$, and let $m_1,m_2$ be the number of nonzero terms in $P_1,P_2$.
-Assume that all nonzero terms which appear in $P_1$ also appear in $P_2$.
- We define a measure of similarity between the polynomials as $\Phi(P_1,P_2) = \frac{m_1}{m_2}$.
-\end{definition}
-
-\begin{lemma}
-Consider the following network $\mathcal{N}$ whose output is given by $Y(w) = \sum \sigma Wx$, where $\sigma$ is a rectified linear unit non-linearity.
-Furthermore assume that $rank(W) = k$.
-Then $\Phi(Y(w),S(w))  = \frac{1}{4k}$.
-\end{lemma}
-
-\begin{proof}
- Assume for simplicity that $W$ is $n \times n$. Since $W$ has rank $k$, it can be written as $W = UV^T$, where $U$ and $V$ have dimension $n \times k$.
- We can therefore reparameterize the system so that the free parameters consist of the entries of $U$ and $V$, which brings the number of parameters to $2kn$. 
- Assume these are reindexed of the form $\{w_1,w_2,...,w_{2kn} \}$.
- A spin glass model with this set of parameters and $H=2$ will have $(2kn)^2=4k^2n^2$ terms in its sum.
- Let us now count the number of unique terms in the polynomial $Y(w)$ which represents our network. 
- The matrix $W = UV^T$ has $n^2$ entries, each of which is of the form $u^Tv$ for some row $u$ of $U$ and $v$ of $V$. 
- Since $u,v \in \mathbb{R}^k$, each entry is the sum of $k$ terms of the form $w_i w_j$. 
- It follows that each entry in the column vector $Wx$ is the sum of $nk$ terms, and hence the output $y$ is the sum of $n^2k$ terms, all of the form $w_iw_jx_{ij}$.
- We thus have $\Phi(Y(w),S(w)) = \frac{n^2k}{4n^2k^2} = \frac{1}{4k}$.
-\end{proof}
-
-  In the above example, we can combine pairs of terms of the form $w_iw_jx_{ij} + w_jw_ix_{ji}$ into $w_iw_j(x_{ij}+x_{ji})$. 
-  The sum $(x_{ij}+x_{ji})$ has higher variance than the other input terms, but if this is a benign assumption for subsequent results then the ratio of terms becomes $\frac{1}{2k}$ rather than $\frac{1}{4k}$.
-
-\begin{lemma}
- The class of functions which can be learned by networks of the form $y = v^T \sigma Wx$ and $y = \sum \sigma Wx$ is equivalent. 
-\end{lemma}
-
-\begin{proof}
- We can show this by simple change of variables. 
- \begin{align*}
-  y &= v^T \sigma(Wx) \\
-  &= \sum_i v_i \sigma(\sum_j w_{ij} x_j) \\
-  &= \sum_i \sigma(\sum_j v_i w_{ij} x_j) \\
-  &= \sum_i \sigma(\sum_j w_{ij}' x_j) \\
-  &= \sum_i \sigma(W'x)
- \end{align*}
-
- where $w_{ij}' = v_i w_{ij}$.
-\end{proof}
-
-\begin{theorem}
- Let $Y(w)$ be the output of a one-layer linear network, $S(w)$ be the Hamiltonian of a 2-spin spin glass model, and assume that the weights of $Y$ have rank $k$. 
- Then $\Phi(Y(w),S(w)) = \frac{1}{4k}$.
-\end{theorem}
-
-\begin{proof}
- This follows directly from the two above lemmas.
-\end{proof}
-\end{comment}
 

### 2014-10-23 PAPER_AMMLY.tex
Final theory

@@
 \begin{abstract}
-We explore the approximate relation between the highly non-convex loss function of a simple model of the fully-connected feed-forward neural network and the Hamiltonian of the spherical spin-glass model under certain assumptions.
-Using the results from the random matrix theory, we study the complexity of neural networks and prove that for large-size networks the lowest critical values of the loss function are located in a well-defined narrow band lower-bounded by the global minimum and furthermore they form a layered structure.
+We study the connection between the highly non-convex loss function of a simple model of the fully-connected feed-forward neural network and the Hamiltonian of the spherical spin-glass model under the assumptions of: i) variable independence, ii) redundancy in network parametrization, and iii) uniformity.
+These assumptions enable us to explain the complexity of the fully decoupled neural network through the prism of the results from the random matrix theory.
+We prove that for large-size decoupled networks the lowest critical values of the loss function are located in a well-defined narrow band lower-bounded by the global minimum and furthermore they form a layered structure.
 Moreover, finding them outside the band diminishes exponentially with the size of the network.
-We empirically demonstrate that both simulated annealing and SGD converges to the band of the lowest critical values, and furthermore all critical points found there are local minima and correspond to the same high learning quality measured by the test error.
+We empirically demonstrate that both models exhibit strong similarities, despite the presence of high dependencies in real networks.
+We conjecture that both simulated annealing and SGD converges to the band of the lowest critical values, and furthermore all critical points found there are local minima and correspond to the same high learning quality measured by the test error.
 This emphasizes a major difference between large- and small-size networks where for the latter poor quality local minima have non-zero probability of being recovered.
@@
 Despite their modeling power, the interest in learning with early neural network significantly weakened when it was shown that they have several limitations including: i) learning limitations such as the inability of single-layer networks to solve the XOR problem~\cite{minsky69perceptrons}, ii) long training time of large networks and proness to overfitting~\cite{JMLR:v15:srivastava14a}, and iii) getting stuck in poor-quality local optima or saddle points while training~\cite{Larochelle:2009:EST:1577069.1577070}.
-Today many of these limitations can be solved with the development of new efficient training strategies (among them backpropagation algorithm~\cite{Werbos:74} which enables to solve the XOR problem), fast GPU-based implementations significantly reducing the training time, and techniques preventing the overfitting such as dropout (e.g.~\cite{journals/corr/abs-1207-0580,JMLR:v15:srivastava14a}).
+Today many of these limitations can be solved with the development of new efficient training strategies (among them backpropagation algorithm~\cite{Werbos:74}), fast GPU-based implementations significantly reducing the training time, and techniques preventing the overfitting such as dropout (e.g.~\cite{journals/corr/abs-1207-0580,JMLR:v15:srivastava14a}).
 Therefore, after a long period of scepticism, the paradigm of learning with neural networks gained significant attention in recent years resulting in many new architectures, such as convolutional networks~\cite{lecun-gradientbased-learning-applied-1998}, recurrent neural networks~\cite{Graves:2009:NCS:1525650.1525782}, deep feedforward neural networks (e.g.~\cite{DBLP:journals/corr/Schmidhuber14} or wide networks~\cite{Huang14}, where the most fundamental difference between them and their early predecessors lies in a much larger parameter space (throughout the paper we refer to the number of network parameters as network size).
@@
 The goal of this paper is to provide insights to the paradigm of large-size neural network optimization where the problem is highly non-convex.
-We establish the connection between the loss function (we focus on hinge loss and absolute loss) of the fully-connected one-output feed-forward neural network of depth $H$ with the Hamiltonian of the $H$-spin spherical spin-glass model.
-We show that the latter can be thought of us an approximator of the loss function of the network under certain assumptions which we also discuss, and furthermore we provide the theoretical guarantee of the quality of this approximation.
+We establish the connection between the loss function (we focus on hinge loss and absolute loss) of the fully-connected feed-forward neural network of depth $H$ with the Hamiltonian of the $H$-spin spherical spin-glass model under certain assumptions, in particular model decoupling, which are discussed in Section~\ref{sec:NNSG}.
 Through the prism of recent findings in random matrix theory~\cite{AAC2010}, in Section~\ref{sec:theory} we study the complexity, i.e.
-the exponential behavior of the mean number of critical points (in total and of given index), of neural networks.
+the exponential behavior of the mean number of critical points (in total and of given index), of neural networks under these assumptions.
 We prove that for large-size networks the local minima and low-index saddle points of the loss function lie within a narrow band lower-bounded by the global minimum and finding them outside the band diminishes exponentially with the size of the network.
@@
 To the best of our knowledge, this paper is the first work providing a theoretical description of the optimization paradigm with neural networks in the presence of large number of parameters.
+It has to be emphasized however that this connection relies on the assumptions made.
 It is also an attempt to make the modern neural network approach more a provable machine learning method and move it away from the 'black-box' shadow.
@@
 Nevertheless they provide no theortical justification for the existence of this connection which instead we provide in this paper.
-\textcolor{red}{We should comment why saddle-point problem in not a problem for us.}
 
@@
 Their results are not discussed in details here as it will be done in Section~\ref{sec:theory} in the context of neural networks.
-We build the bridge between their findings and neural networks and show that the objective function used by neural network is analogous to the Hamiltonian of the spin-glass model and thus their landscapes share the same properties.
+We build the bridge between their findings and neural networks and show that the objective function used by neural network is analogous to the Hamiltonian of the spin-glass model under the assumptions of: i) variable independence, ii) redundancy in network parametrization, and iii) uniformity, and thus their landscapes share the same properties.
 We emphasize that the connection between spin-glass models and neural networks was already explored back in the past (a summary can be found in~\cite{Dotsenko1995}).
@@
 \begin{equation}
-Y = q\sum_{i=1}^{n_0}\sum_{j = 1}^\gamma X_{i}A_{i,j}\prod_{k = 1}^{H}w_{i,j}^{(k)},
+Y = q\sum_{i=1}^{n_0}\sum_{j = 1}^\gamma X_{i,j}A_{i,j}\prod_{k = 1}^{H}w_{i,j}^{(k)},
 \label{eq:befrein}
@@
 where the first summation is over the network inputs and the second one is over all paths from a given network input to its output, where $\gamma$ is the total number of such paths (note that $\gamma = n_1n_2\dots n_H$).
+Also, for all $i = \{1,2,\dots,n_0\}$: $X_{i,1} = X_{i,2} = \dots = X_{i,\gamma}$.
 Furthermore, $w_{i,j}^{(k)}$ is the weight of the $k^{\text{th}}$ segment of path indexed with $(i,j)$ which connects layer $(k-1)^{st}$ with layer $k^{\text{th}}$ of the network.
@@
 \begin{definition}
-The mass of the network $\Psi$ is the total number of all paths between all network inputs and outputs: $\Psi = \prod_{i=0}^Hn_i$. We will also denote $\Lambda$ to be $\Lambda = \sqrt[H]{\Psi}$.
+The mass of the network $\Psi$ is the total number of all paths between all network inputs and outputs: $\Psi = \prod_{i=0}^Hn_i$. Also let $\Lambda$ as $\Lambda = \sqrt[H]{\Psi}$.
 \end{definition}
@@
 
-There mass and the size of the network depend on each other as captured in Theorem~\ref{thm:arge}.
+The mass and the size of the network depend on each other as captured in Theorem~\ref{thm:arge}.
 \begin{theorem}
 Let $\Psi$ be the mass of the network, $d$ be the number of network inputs and $H$ be the depth of the network. The size of the network is bounded as
-\[\Psi^2\frac{1}{d} \geq N \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}} \geq \sqrt[H]{\Psi} = \Lambda.
+\[\Psi^2H = \Lambda^{2H}H \geq N \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}} \geq \sqrt[H]{\Psi} = \Lambda.
 \]
@@
 \end{theorem}
-\begin{corollary}
-For bounded network depth $H$, $\Lambda \rightarrow \infty$ iff $\Psi \rightarrow \infty$.
-For bounded network depth $H$, if the mass of the network $\Psi$ goes to $\infty$ ($\Psi \rightarrow \infty$) then the size of the network also goes to $\infty$ ($N \rightarrow \infty$) (equivalently $\Lambda \rightarrow \infty$ implies $N \rightarrow \infty$).
-\end{corollary}
+In the rest of the paper we assume that the depth of the network $H$ is bounded.
+Therefore $N \rightarrow \infty$ iff $\Psi \rightarrow \infty$ and $N \rightarrow \infty$ iff $\Lambda \rightarrow \infty$.
 
 In the rest of this section we will be establishing a connection between the loss function of the neural network and the Hamiltonian of the spin-glass model.
-Under certain assumptions, that will be introduced and discussed, spin-glass model can be though of as an approximator of a network output.
-We will also provide the measure of quality of this approximation.
 All proofs are deferred to the Supplementary material.
@@
 
-In this section we introduce randomness to the model and assume $X$s and $A$s are random.
+In this section we introduce randomness to the model by assuming $X$s and $A$s are random.
 We make certain assumptions regarding the neural network model.
-These assumptions consider random variables $X$s and $A$s (their distributions and mutual dependencies) as well as they introduce spherical constraint on the model weights.
+They consider random variables $X$s and $A$s (their distributions and mutual dependencies) as well as they introduce spherical constraint on the model weights.
 We also introduce two other assumptions regarding redundancy of network parameters and their uniformity (details in the text below), both of them are justified by empirical evidence in the literature.
-The aim of this section is to obtain an approximator to the expectation $\mathbb{E}_A[Y]$ (note it is still a random variable) which, as will be seen in Section~\ref{subsec:LFSG}, is used in the definition of the loss function of neural network.
-Theorems~\ref{thm:redun} and~\ref{thm:unif} provide some guarantees regarding the quality of this approximation.
 
 \paragraph{Input}
-We assume each input $X_i$ is a normal random variable such that $X_i\sim N(0,1)$.
+We assume each input $X_{i,j}$ is a normal random variable such that $X_{i,j}\sim N(0,1)$.
+Clearly the model contains several dependencies as one input is associated with many paths in the network.
+That poses a major theoretical problem in analysing these models as in standard statistical learning theory the independence assumptions are heavily used~\cite{hastie01statisticallearning}.
+We therefore decouple the model by assyming the independence of $X_{i,j}$'s~\cite{opac-b1095246}.
+Under this assumption we will explore the similarity of this model to the spin-glass model, where the latter assumes heavy independence of random variables.
+We emphasize that despite the presence of high dependencies in real neural networks, both models exhibit high similarities as will be empirically demonstrated.
 
@@
 \begin{equation}
-\mathbb{E}_A[Y] = q\sum_{i=1}^{n_0}\sum_{j = 1}^\gamma X_{i}\rho\prod_{k = 1}^{H}w_{i,j}^{(k)}.
+\mathbb{E}_A[Y] = q\sum_{i=1}^{n_0}\sum_{j = 1}^\gamma X_{i,j}\rho\prod_{k = 1}^{H}w_{i,j}^{(k)}.
 \label{eq:befrein2}
 \end{equation}
-We furthermore decouple~\cite{opac-b1095246} the paths by assuming their mutual independence. \textcolor{red}{We might wanna write more.}
 
 \paragraph{Redundancy in network parametrization}
-Let $\mathcal{W} = \{w_1,w_2,\dots,w_{\Lambda}\}$ be the set of all weights of the network.
+Let $\mathcal{W} = \{w_1,w_2,\dots,w_N\}$ be the set of all weights of the network.
 Let $\mathcal{A}$ denote the set of all $H$-length configuration of weights chosen from $\mathcal{W}$ (order of weights in a configuration does matter).
@@
 \begin{equation}
-Y_{\Lambda} \!:=\!
-\mathbb{E}_A[Y] \!=\!
-q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{N}\!\!\!\!\!\!\!\sum_{j = 1}^{r_{i_1\!,i_2,\dots,i_H}}\!\!\!\!\!X_{i_1,i_2,\dots,i_H}^{(j)}\rho\!\prod_{k = 1}^{H}\!\!w_{i_k}.
+Y_N \!:=\! \mathbb{E}_A[Y] \!=\! q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{N}\!\!\!\!\!\!\!\sum_{j = 1}^{r_{i_1\!,i_2,\dots,i_H}}\!\!\!\!\!X_{i_1,i_2,\dots,i_H}^{(j)}\rho\!\prod_{k = 1}^{H}\!\!w_{i_k}.
 \label{eq:befapprox}
@@
 Also $r_{i_1,i_2,\dots,i_H} = 0$ implies that summand $X_{i_1,i_2,\dots,i_H}^{(j)}\rho\prod_{k = 1}^{H}w_{i_k}$ is zeroed out).
-Note that $\sum_{j = 1}^{r_{i_1\!,i_2,\dots,i_H}}X_{i_1,i_2,\dots,i_H}^{(j)}$ could be replaced by $r_{i_1\!,i_2,\dots,i_H}X_{i_1,i_2,\dots,i_H}$ since $r_{i_1,i_2,\dots,i_H}$, but we choose this notation on purpose as it will be helpful later on.
-Furthermore, the following condition has to be satisfied: $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H} = \Psi$.
-In the notation $Y_{\Lambda}$, index $\Lambda$ refers to the number of unique weights of a network (this notation will also be helpful later).
+Furthermore, the following condition has to be satisfied: $\sum_{i_1,i_2,\dots,i_H=1}^{N}r_{i_1,i_2,\dots,i_H} = \Psi$.
+In the notation $Y_N$, index $N$ refers to the number of unique weights of a network (this notation will also be helpful later).
 
-Consider a family of networks which have the same graph of connections as network $\mathcal{N}$ but different edge weighting such that they only have $s$ unique weights and $s \leq \Lambda$ (through notation analogy expected output of this network will be called $Y_s$).
+Consider a family of networks which have the same graph of connections as network $\mathcal{N}$ but different edge weighting such that they only have $s$ unique weights and $s \leq N$ (through notation analogy expected output of this network will be called $Y_s$).
 It was recently shown~\cite{NIPS2013_5025,DBLP:journals/corr/DentonZBLF14} that for large-size networks large number of network parameters (according to~\cite{NIPS2013_5025} even up to $95\%$) are reduntant and can either be learned from a very small set of unique parameters or even not learned at all with almost no loss in prediction accuracy.
@@
 \begin{definition}
-A network $\mathcal{M}$ which has the same graph of connections as $\mathcal{N}$ and the number of unique weights $s$ satisfying $s \leq \Lambda$ is called a $(s,\epsilon)$-\textit{reduction image} of $\mathcal{N}$ for some $\epsilon \in [0,1]$ if the prediction accuracy of $\mathcal{N}$ and $\mathcal{M}$ differ by no more than $\epsilon$ (thus they classify at most $\epsilon$ fraction of data points differently).
+A network $\mathcal{M}$ which has the same graph of connections as $\mathcal{N}$ and the number of unique weights $s$ satisfying $s \leq N$ is called a $(s,\epsilon)$-\textit{reduction image} of $\mathcal{N}$ for some $\epsilon \in [0,1]$ if the prediction accuracy of $\mathcal{N}$ and $\mathcal{M}$ differ by no more than $\epsilon$ (thus they classify at most $\epsilon$ fraction of data points differently).
 \end{definition}
@@
 \begin{theorem}
-Let $\mathcal{N}$ be a neural network giving the output whose expectation $Y_{\Lambda}$ is given in Equation~\ref{eq:befapprox}.
-Let $\mathcal{M}$ be its $(s,\epsilon)$-reduction image for some $s \leq \Lambda$ and $\epsilon \in [0,p]$.
+Let $\mathcal{N}$ be a neural network giving the output whose expectation $Y_N$ is given in Equation~\ref{eq:befapprox}.
+Let $\mathcal{M}$ be its $(s,\epsilon)$-reduction image for some $s \leq N$ and $\epsilon \in [0,0.5]$.
 Through analogy, let $Y_s$ be the expected output of network $\mathcal{M}$.
 Then the following holds
-\[corr(sign(Y_s),sign(Y_{\Lambda})) \geq \frac{1-2\epsilon}{1+2\epsilon},
+\[corr(sign(Y_s),sign(Y_N)) \geq \frac{1-2\epsilon}{1+2\epsilon},
 \]
-where $corr$ denotes the correlation defined as $corr(A,B) = \frac{\mathbb{E}[(A - \mathbb{E}[A]])(B - \mathbb{E}[B]])}{std(A)std(B)}$, $std$ is the standard deviation and $sign(\cdot)$ denotes the sign of prediction ($sign(Y_s)$ and $sign(Y_{\Lambda})$ are both random).
+where $corr$ denotes the correlation defined as $corr(A,B) = \frac{\mathbb{E}[(A - \mathbb{E}[A]])(B - \mathbb{E}[B]])}{std(A)std(B)}$, $std$ is the standard deviation and $sign(\cdot)$ denotes the sign of prediction ($sign(Y_s)$ and $sign(Y_N)$ are both random).
 \label{thm:redun}
@@
 
-The assumption of the redundancy of parameters implies that one can preserve $\epsilon$ to be close to $0$ even with $s << \Lambda$.
+The assumption of the redundancy of parameters implies that one can preserve $\epsilon$ to be close to $0$ even with $s << N$.
 
 \paragraph{Uniformity}
-Consider network $\mathcal{M}$ to be a $(s,\epsilon)$-reduction image of $\mathcal{N}$ for some $s \leq \Lambda$ and $\epsilon \in [0,1]$.
+Consider network $\mathcal{M}$ to be a $(s,\epsilon)$-reduction image of $\mathcal{N}$ for some $s \leq N$ and $\epsilon \in [0,1]$.
 The output $Y_s$ of the image network can in general be expressed as
@@
 \end{equation}
-The factor $\sqrt{\frac{\Psi}{s^H}}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus with high probability every node is adjacent to an edge with any of the unique weights) it holds that $\hat{r}_{i_1,i_2,\dots,i_H} = \sqrt{\frac{\Psi}{s^H}}$.
+The factor $\frac{\Psi}{s^H}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus with high probability every node is adjacent to an edge with any of the unique weights) it holds that $t_{i_1,i_2,\dots,i_H} = \frac{\Psi}{s^H}$.
 Note that this condition can be sattified with small $c$ (close to $1$) if $s$ is sufficiently small.
@@
 \end{theorem}
-We will refer to $\hat{Y}_s$ as an $(s,\epsilon,\delta)$-\textit{approximator} of $Y_{\Lambda}$, where the quality of this approximation is captured in Theorems~\ref{thm:redun} and~\ref{thm:unif}.
+We will refer to $\hat{Y}_s$ as an $(s,\epsilon,c)$-\textit{approximator} of $Y_N$, where the quality of this approximation is captured in Theorems~\ref{thm:redun} and~\ref{thm:unif}.
 Intuitively, for large networks (our analysis in Section~\ref{sec:theory} considers $\Lambda \rightarrow \infty$) one would expect $s$ to be small enough to simultaneously guarantee sufficiently small (close to $1$) $c$ and preserve good accuracy (small $\epsilon$).
@@
 
-In the next we will consider two frequently used loss functions, absolute loss and hinge loss, where we approximate $Y_{\Lambda}$ with $\hat{Y}_s$.
+Next we will consider two frequently used loss functions, absolute loss and hinge loss, where we approximate $Y_N$ with $\hat{Y}_s$.
 
@@
 \mathcal{L}_{\!\Lambda,H}({\bm w}) \!=\!
-\frac{1}{\Lambda^{\!(H\!-\!1)/2}}\!\!\!\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!\!\!\!\!Z_{i_1,i_2,\dots,i_H}\!w_{i_1}\!w_{i_2}\!\dots\!w_{i_H},
+\frac{1}{\Lambda^{\!(H\!-\!1)/2}}\!\!\!\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!\!\!\!\!X_{i_1,i_2,\dots,i_H}\!w_{i_1}\!w_{i_2}\!\!\dots\!w_{i_H}.
 \label{eq:spinglass}
@@
 \begin{proof}
-First we will prove the lower-bound. By the inequality between arithmetic and geometric mean the mass and the size of the network are connected as follows
-\[\Lambda \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{n_0n_H}} = \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}},
+First we will prove the lower-bound on $N$. By the inequality between arithmetic and geometric mean the mass and the size of the network are connected as follows
+\[N \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{n_0n_H}} = \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}},
 \]
 and since $\sqrt[H]{\Psi}\frac{H}{\sqrt[H]{d}} = \sqrt[H]{\prod_{i = 1}^{H}n_i}H \geq 1$ then 
-\[\Lambda \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}} \geq \sqrt[H]{\Psi}.
+\[N \geq \sqrt[H]{\Psi^2}\frac{H}{\sqrt[H]{d}} \geq \sqrt[H]{\Psi}.
 \]
-The upper-bound can be shown as follows
-\[\Lambda \leq \prod_{i=0}^{H-1}n_in_{i+1} = \frac{\Psi^2}{n_0n_H} = \Psi^2\frac{1}{d}.
+Next we show the upper-bound on $N$. Let $n_{max} = \max_{i \in \{1,2,\dots,H\}}n_i$. Then
+\[N \leq Hn_{max}^2 \leq H\Psi^2.
 \]
@@
 Then the following holds
-\[corr(sign(Y_1),sign(Y_2)) \geq \frac{2p(1 \!-\! p \!+\! \epsilon) \!-\! \epsilon}{2\sqrt{(p \!+\! \epsilon)(1 \!-\! p \!+\! \epsilon)p(1 \!-\! p)}}.
+\[corr(sign(Y_1),sign(Y_2))
+\]
+\[\geq \frac{1 - 2\epsilon - (1 - 2p)^2 - 2(1 - 2p)\epsilon}{4\sqrt{p(1 - p)(p + \epsilon)(1 - p + \epsilon)}}.
 \]
@@
 \begin{proof}
-Note that $\mathbb{E}[\hat{Y}_s] = 0$ and $\mathbb{E}[Y_{\Lambda}] = 0$. Furthermore
+Note that $\mathbb{E}[\hat{Y}_s] = 0$ and $\mathbb{E}[Y_s] = 0$. Furthermore
 \[\mathbb{E}[\hat{Y}_sY_{\Lambda}] = q^2\rho^2\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\min\left(\frac{\Psi}{\Lambda^H},t_{i_1,i_2,\dots,i_H}\right)\prod_{k = 1}^{H}w_{i_k}^2
@@
 \]
-\[std(Y_{\Lambda}) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}t_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2}.
+\[std(Y_s) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}t_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2}.
 \]
@@
 \begin{eqnarray*}
-&&\!\!\!\!\!\!\!\!\!corr(\hat{Y}_s,Y_{\Lambda})\\ 
+&&\!\!\!\!\!\!\!\!\!corr(\hat{Y}_s,Y_s)\\ 
 &\!\!\!\!\!\!\!\!\!=&\!\!\!\!\!\!\!

### 2014-10-23 PAPER_AMMLY.tex
shortening

@@
 In the rest of the paper we assume that the depth of the network $H$ is bounded.
-Therefore $N \rightarrow \infty$ iff $\Psi \rightarrow \infty$ and $N \rightarrow \infty$ iff $\Lambda \rightarrow \infty$.
+Therefore $N \rightarrow \infty$ iff $\Psi \rightarrow \infty$, and $N \rightarrow \infty$ iff $\Lambda \rightarrow \infty$.
 
@@
 \paragraph{Spherical constraint}
-We finally make a benign assumption that the weights sattisfy the spherical condition 
+We finally make a benign assumption that for some positive constant $\mathcal{C}$ weights sattisfy the spherical condition 
 \begin{equation}
-\frac{1}{\Lambda}\sum_{i=1}^{\Lambda}w_i^2 = \mathcal{C},
+\frac{1}{\Lambda}\sum_{i=1}^{\Lambda}w_i^2 = \mathcal{C}.
 \label{eq:befspherical}
 \end{equation}
-where $\mathcal{C}$ is some positive constant.
 
@@
 \end{eqnarray*}
-Note that both cases can be generalized to the following
+Note that both cases can be generalized as
 \[\mathcal{L}_{\Lambda,H}({\bm w}) = \left \{
@@
 \mathcal{L}_{\Lambda,H}({\bm w}) \!\!\!\!\!&=&\!\!\!\!\! \mathbb{E}_{M}[M(S + \hat{Y}_s)]\\
-&=& \!\!\!\!\!S\rho^{'} \!+\! \rho^{'}\hat{Y}_s\\
 &=& \!\!\!\!\!S\rho^{'} \!+\! q\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!X_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}.
 \end{eqnarray*}
-Let $\tilde{w}_i = \sqrt[H]{\rho\rho^{'}}w_i$ for all $i = \{1,2,\dots,k\}$. Note that $\tilde{w}_i = \frac{1}{\sqrt{C}}$. Thus
+Let $\tilde{w}_i = \sqrt[H]{\rho\rho^{'}}w_i$ for all $i = \{1,2,\dots,k\}$. Note that $\tilde{w}_i = \frac{1}{\sqrt{C}}w_i$. Thus
 \begin{equation}
@@
 Let $B \subset \mathbb{R}$ be any Borel set and $k$ be an integer such that $0 \leq k < \Lambda$.
-A random number of critical values of $\mathcal{L}_{\Lambda,H}({\bm w})$ in the set $\Lambda B = \{\Lambda X:x\in B\}$ with index equal to $k$ is
-\[\mathcal{C}_{\Lambda,k}(B) = \!\!\!\!\!\!\!\!\!\!\!\!\!\!\sum_{{\bm w}:\nabla \mathcal{L}_{\Lambda,H}({\bm w}) = 0}\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\mathbbm{1}\{\mathcal{L}_{\Lambda\!,H}({\bm w})\!\in\!
-\Lambda B\}\mathbbm{1}\{i(\nabla^2\mathcal{L}_{\Lambda\!,H}({\bm w})) \!=\!
-k\},
-\]
-and a random total number of critical values of $\mathcal{L}_{\Lambda,H}(w)$ in the set $\Lambda B = \{\Lambda X:x\in B\}$ is
-\[\mathcal{C}_{\Lambda}(B) = \sum_{{\bm w}:\nabla \mathcal{L}_{\Lambda,H}({\bm w}) = 0}\!\!\!\!\!\!\!\!\!\!\!\!\!\mathbbm{1}\{\mathcal{L}_{\Lambda,H}({\bm w})\!\in\! \Lambda B\},
-\]
-where $\nabla$ and $\nabla^2$ denote respectively gradient and Hessian restricted to $\mathcal{S}_{\Lambda}$ and $i(\nabla^2\mathcal{L}_{\Lambda,H}(w))$ is the number of negative eigenvalues of the Hessian $\nabla^2\mathcal{L}_{\Lambda,H}$ at ${\bm w}$ also called index of $\nabla^2\mathcal{L}_{\Lambda,H}$ at ${\bm w}$.
+We will denote as $\mathcal{C}_{\Lambda,k}(B)$ a random number of critical values of $\mathcal{L}_{\Lambda,H}({\bm w})$ in the set $\Lambda B = \{\Lambda X:x\in B\}$ with index\footnote{The number of negative eigenvalues of the Hessian $\nabla^2\mathcal{L}_{\Lambda,H}$ at ${\bm w}$ is also called index of $\nabla^2\mathcal{L}_{\Lambda,H}$ at ${\bm w}$.} equal to $k$.
+Similarily we will denote as $\mathcal{C}_{\Lambda}(B)$ a random total number of critical values of $\mathcal{L}_{\Lambda,H}(w)$ in the set $\Lambda B = \{\Lambda X:x\in B\}$.
 \end{definition}
@@
 
-Let us now introduce the number that we will refer to as $E_{\infty}$ and use later on.
-\begin{equation}
-E_{\infty} = E_{\infty}(H) = 2\sqrt{\frac{H-1}{H}}.
-\label{eq:E_inf}
-\end{equation}
-We will also define two non-decreasing, continuous functions on $\mathbb{R}$, $\Theta_H$ and $\Theta_{k,H}$ as follows
+\begin{definition}
+The ground state energy is the (normalized) minimum of the loss function $\mathcal{L}_{\Psi,c,H}$
+\[G^\Psi = \frac{1}{\Lambda}\inf_{{\bm w}\in \mathcal{S}}\mathcal{L}_{\Lambda,H}({\bm w}).
+\]
+\end{definition}
+
+Below we summarize the results of the theoretical analysis in~\cite{AAC2010} in the context of neural networks.
+\paragraph{The existence of the band of low-index critical points}
+One can directly use Theorem 2.12 in~\cite{AAC2010} to show that for large-size networks (more precisely when $\Lambda \rightarrow \infty$ but recall that $\Lambda \rightarrow \infty$ iff $N \rightarrow \infty$) and when $H \geq 4$ it is improbable to find a critical value below certain level $-\Lambda E_0(H)$, where $E_0(H)$ is some real number.
+
+Let us also  introduce the number that we will refer to as $E_{\infty}$. We will refer to this important threshold as an \textit{energy barrier} and define it as
+\[E_{\infty} = E_{\infty}(H) = 2\sqrt{\frac{H-1}{H}}.
+\]
+Theorem 2.14 in~\cite{AAC2010} implies that for large-size networks all critical values of the loss function that are of non-diverging index must lie below the threshold $-\Lambda E_{\infty}(H)$.
+Any critical point that lies above the energy barrier is a high-index saddle point with overwhelming probablity.
+Thus for large-size networks all critical values of the loss function that are of non-diverging index must lie in the band $\left(-\Lambda E_0(H),-\Lambda E_{\infty}(H)\right)$.
+
+\begin{figure*}[htp!]
+  \center
+\includegraphics[width = 1.65in]{Distr_cp.pdf}
+\includegraphics[width = 1.65in]{Distr_lm_sp_li.pdf} 
+\includegraphics[width = 1.65in]{Distr_lm_sp_li_zoomed_left.pdf} 
+\includegraphics[width = 1.65in]{Distr_lm_sp_li_zoomed_right.pdf} 
+\vspace{-0.3in}
+\caption{Distribution of the mean number of critical points, local minima and low-index saddle points (oryginal and zoomed).
+Parameters $H$ and $\Lambda$ were set to $H = 3$ and $\Lambda = 1000$.
+Black line: $u = -E_0(H)$, red line: $u = -E_{\infty}(H)$.
+Figure must be read in color.}
+\label{fig:Distr_cp_lm_sp}
+\vspace{-0.1in}
+\end{figure*}
+
+\paragraph{Layered structure of low-index critical points}
+From Theorem 2.15 in~\cite{AAC2010} it follows that for large-size networks finding a critical value with index larger or equal to $k$ (for any fixed integer $k$) below energy level $-\Lambda E_k(H)$ is improbable, where $-E_k(H) \in [-E_0(H),-E_{\infty}(H)]$.
+Furthermore, for any fixed $H \geq 3$, the sequence $\{E_k(H)\}_{k\in\mathbb{N}}$ is strictly decreasing and converges to $E_{\infty}$ as $k \rightarrow \infty$~\cite{AAC2010}.
+
+These results unravel a layered structure for the lowest critical values of the loss function of a large-size network, where with overwhelming probability the critical values above the global minimizer (ground state) of the loss function are local minima exclusively.
+Above the band ($\left(-\Lambda E_0(H),-\Lambda E_1(H)\right)$) containing only local minima (critical points of index $0$), there is another one, ($\left(-\Lambda E_1(H),-\Lambda E_2(H)\right)$), where one can only find local minima and saddle points of index $1$, and above this band there exists another one, ($\left(-\Lambda E_2(H),-\Lambda E_3(H)\right)$), where one can only find local minima and saddle points of index $1$ and $2$, etc.
+The above-described layered structure of the lowest critical values of the Hamiltonian of the spherical spin glass model was in-detail described in~\cite{AAC2010}, however with no connection to neural networks which is what we explore.
+
+Another important fact is that the band $(-E_0(H),-E_{\infty})$ is very narrow, i.e. it is order of magnitudes narrower than band $(-E_{\infty},0)$.
+
+\paragraph{Hardness of recovering the global minimum}
+Note that based on what was already shown recovering the global minimizer when starting from any (local) minima from one of the energy bands above, e.g.
+$\left(-\Lambda E_i(H),-\Lambda E_{i+1}(H)\right)$, diverges with $\Lambda$ since it is bounded below by $\Lambda (E_0(H) - E_i(H))$.
+\textcolor{red}{More should be written.}
+
+\paragraph{Logarithmic asymptotics of the mean number of critical points}
+We will now define two non-decreasing, continuous functions on $\mathbb{R}$, $\Theta_H$ and $\Theta_{k,H}$ as follows
 \[\Theta_H(u) = \left \{
@@
 Note that the maximal values of $\Theta_H(u)$ and $\Theta_{k,H}(u)$ are respectively $\frac{1}{2}\log(H-1)$ and $\frac{1}{2}\log(H-1) - \frac{H-2}{H}$.
-Figure~\ref{fig:Thetas} captures exemplary plots of the functions $\Theta_H(u)$ and $\Theta_{k,H}(u)$ for $k = 0$.
+Figure~\ref{fig:Thetas} captures exemplary plots of the functions $\Theta_H(u)$ and $\Theta_{k,H}(u)$.
 Also note that the following corollary holds.
@@
 \end{corollary}
-Finally, for any integer $k \geq 0$, let $E_k = E_k(H) > 0 $ be defined as the unique solution to 
-\[\Theta_{k,H}(-E_k) = 0.
-\]
-
-\begin{figure*}[htp!]
-  \center
-\includegraphics[width = 1.65in]{Distr_cp.pdf}
-\includegraphics[width = 1.65in]{Distr_lm_sp_li.pdf} 
-\includegraphics[width = 1.65in]{Distr_lm_sp_li_zoomed_left.pdf} 
-\includegraphics[width = 1.65in]{Distr_lm_sp_li_zoomed_right.pdf} 
-\vspace{-0.3in}
-\caption{Distribution of the mean number of critical points, local minima and low-index saddle points (oryginal and zoomed).
-Parameters $H$ and $\Lambda$ were set to $H = 3$ and $\Lambda = 1000$.
-Black line: $u = -E_0(H)$, red line: $u = -E_{\infty}(H)$.
-Figure must be read in color.}
-\label{fig:Distr_cp_lm_sp}
-\vspace{-0.1in}
-\end{figure*}
-
-For any fixed $H \geq 3$, the sequence $\{E_k(H)\}_{k\in\mathbb{\Lambda}}$ is strictly decreasing and converges to $E_{\infty}$ as $k \rightarrow \infty$~\cite{AAC2010}.
-Another important fact is that the band $(-E_0(H),-E_{\infty})$ is very narrow, i.e.
-it is order of magnitudes narrower than band $(-E_{\infty},0)$.
-We will now define the ground state energy.
-
-\begin{definition}
-The ground state energy is the (normalized) minimum of the loss function $\mathcal{L}_{\Psi,c,H}$
-\[G^\Psi = \frac{1}{\Lambda}\inf_{{\bm w}\in \mathcal{S}}\mathcal{L}_{\Lambda,H}({\bm w}).
-\]
-\end{definition}
-Next we provide theorems (resp.
-Theorem~\ref{thm:lb},~\ref{thm:ub},~\ref{thm:layer}, ~\ref{thm:lmsp} and~\ref{thm:cp}) which are direct consequences of the theoretical findings in~\cite{AAC2010} (resp.
-Theorem 2.12, 2.14, 2.15, 2.5 and 2.8).
-
-\begin{theorem}
-For every $H \geq 3$
-\[\liminf_{\Lambda \rightarrow \infty} G^\Psi \geq -E_0(H),
-\]
-and for $H \geq 4$
-\[\liminf_{\Lambda \rightarrow \infty} G^\Psi = -E_0(H) \:\:\:\text{in probability.}
-\]
-\label{thm:lb}
-\end{theorem}
-By Theorem~\ref{thm:lb}, for large-size networks it is improbable to find a critical value below level $-\Lambda E_0(H)$.
-\begin{theorem}
-For an integer $k \geq 0$ and $\epsilon > 0$,
-\[\limsup_{\Lambda \rightarrow \infty} \frac{1}{\Lambda^2}\log(\mathbb{P}(\mathcal{C}_{\Lambda,k}(-E_{\infty}(H) + \epsilon,\infty)>0)) < 0
-\]
-\label{thm:ub}
-\end{theorem}
-Theorem~\ref{thm:ub} implies that for large-size networks all critical values of the loss function that are of non-diverging index must lie below the threshold $-\Lambda E_{\infty}(H)$.
-We will refer to this important threshold as an \textit{energy barrier}.
-Any critical point that lies above the energy barrier is a high-index saddle point with overwhelming probablity.
-Theorem~\ref{thm:lb} and~\ref{thm:ub} both imply that for large-size networks all critical values of the loss function that are of non-diverging index must lie in the band $\left(-\Lambda E_0(H),-\Lambda E_{\infty}(H)\right)$.
-\begin{theorem}
-For $k \geq 0$ and $\epsilon > 0$,
-\[\limsup_{\Lambda \rightarrow \infty} \frac{1}{\Lambda^2}\log(\mathbb{P}(\sum_{i=k}^{\infty}\!\mathcal{C}_{\Lambda,i}(-E_k(H) - \epsilon,\infty) \!>\! 0)) \!<\! 0
-\]
-\label{thm:layer}
-\end{theorem}
-Theorem~\ref{thm:layer} implies that for large-size networks finding a critical value with index larger or equal to $k$ (for any fixed integer $k$) below energy level $-\Lambda E_k(H)$ is improbable.
-
-The statements of Theorems~\ref{thm:lb},~\ref{thm:ub} and~\ref{thm:layer} unravel a layered structure for the lowest critical values of the loss function of a large-size network, where with overwhelming probability the critical values above the global minimizer (ground state) of the loss function are local minima exclusively.
-Above the band ($\left(-\Lambda E_0(H),-\Lambda E_1(H)\right)$) containing only local minima (critical points of index $0$), there is another one, ($\left(-\Lambda E_1(H),-\Lambda E_2(H)\right)$), where one can only find local minima and saddle points of index $1$, and above this band there exists another one, ($\left(-\Lambda E_2(H),-\Lambda E_3(H)\right)$), where one can only find local minima and saddle points of index $1$ and $2$, etc.
-The above-described layered structure of the lowest critical values of the Hamiltonian of the spherical spin glass model was in-detail described in~\cite{AAC2010}, however with no connection to neural networks which is what we explore.
-
-An interesting implication of Theorems~\ref{thm:lb},~\ref{thm:ub} and~\ref{thm:layer} is that recovering the global minimizer when starting from any (local) minima from one of the energy bands above, e.g.
-$\left(-\Lambda E_i(H),-\Lambda E_{i+1}(H)\right)$, diverges with $\Lambda$ since it is bounded below by $\Lambda (E_0(H) - E_i(H))$.
 
 Next we will show the logarithmic asymptotics of the mean number of critical points (the asymptotics of the mean number of critical points can be found in the Supplementary material).
-\begin{theorem}
-For all $H \geq 2$ and $k \geq 0$ fixed
-\[\lim_{\Lambda \rightarrow \infty}\frac{1}{\Lambda}\log\mathbb{E}[\mathcal{C}_{\Lambda,k}(u)] = \Theta_{k,H}(u).
-\]
-\label{thm:lmsp}
-\end{theorem}
 \begin{theorem}
@@
 \]
-\label{thm:cp}
+and for all $H \geq 2$ and $k \geq 0$ fixed
+\[\lim_{\Lambda \rightarrow \infty}\frac{1}{\Lambda}\log\mathbb{E}[\mathcal{C}_{\Lambda,k}(u)] = \Theta_{k,H}(u).
+\]
+\label{thm:lmsp}
 \end{theorem}

### 2014-10-23 PAPER_AMMLY.tex
shortening_further

@@
 \begin{theorem}
-Under the uniformity assumption of Equation~\ref{eq:uniform}, random variable $\hat{Y}_s$ in Equation~\ref{eq:approx} and random variable $Y_s$ in Equation~\ref{eq:befapprox} sattisy the following
-\[corr(\hat{Y}_s,Y_s) \geq \frac{1}{c^2}
-\]
+Under the uniformity assumption of Equation~\ref{eq:uniform}, random variable $\hat{Y}_s$ in Equation~\ref{eq:approx} and random variable $Y_s$ in Equation~\ref{eq:befapprox} sattisfy the following: $corr(\hat{Y}_s,Y_s) \geq \frac{1}{c^2}$.
 \label{thm:unif}
@@
 \]
-where $Y_t$ is a random variable corresponding the true data labeling that takes values $-S$ or $S$ in case of the absolute loss and $-1$ or $1$ in case of the hinge loss, where $S = \sup_{\bf{w}}{\hat{Y}_s}$.
-Also note that in case of the hinge loss $\max$ operator can be modelled as Bernoulli random variable, that we will refer to as $M$, with success ($M = 1$) probability $\rho^{'} = \frac{1}{\rho\sqrt{\mathcal{C}^H}}$.
-We assume $M$ is independent of $\hat{Y}_s$.
-Therefore we obtain that
-\[\mathcal{L}^a_{\Lambda,H}({\bm w}) = \left \{
-  \begin{tabular}{c}
-  $\!\!\!\!\!\!S - \hat{Y}_s$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = S$ \\
-  $\!S + \hat{Y}_s$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -S$ \\
-  \end{tabular}
-\right.
+where $Y_t$ is a random variable corresponding to the true data labeling that takes values $-S$ or $S$ in case of the absolute loss and $-1$ or $1$ in case of the hinge loss, where $S = \sup_{\bf{w}}{\hat{Y}_s}$.
+Also note that in case of the hinge loss $\max$ operator can be modelled as Bernoulli random variable.
+It turns out that both losses can be generalized to the following expression
+\[\mathcal{L}_{\!\Lambda,H}({\bm w}) = \mathcal{C}_1 + \mathcal{C}_2q\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}X_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}\tilde{w}_{i_k},
 \]
-and
-\begin{eqnarray*}
-\mathcal{L}^h_{\Lambda,H}({\bm w}) &=& \mathbb{E}_{M,A}[M(
-1-Y_t\hat{Y}_s)]\\&=& \left \{
-  \begin{tabular}{c}
-  $\!\!\!\!\!\!\mathbb{E}_{M}[M(1 - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = 1$ \\
-  $\!\mathbb{E}_{M}[M(1 + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -1$ \\
-  \end{tabular}
-\right.
-\end{eqnarray*}
-Note that both cases can be generalized as
-\[\mathcal{L}_{\Lambda,H}({\bm w}) = \left \{
-  \begin{tabular}{c}
-  $\!\mathbb{E}_{M}[M(S - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t  > 0$ \\
-  $\!\mathbb{E}_{M}[M(S + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t < 0$ \\
-  \end{tabular}
-\right.,
-\]
-where in case of the absolute loss $\rho^{'} = 1$ and in case of the hinge loss $S = 1$. Furthermore, since $X$'s are Gaussian random variables, then so are $-X$'s thus we can further generalize that
-\begin{eqnarray*}
-\mathcal{L}_{\Lambda,H}({\bm w}) \!\!\!\!\!&=&\!\!\!\!\! \mathbb{E}_{M}[M(S + \hat{Y}_s)]\\
-&=& \!\!\!\!\!S\rho^{'} \!+\! q\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!X_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}.
-\end{eqnarray*}
-Let $\tilde{w}_i = \sqrt[H]{\rho\rho^{'}}w_i$ for all $i = \{1,2,\dots,k\}$. Note that $\tilde{w}_i = \frac{1}{\sqrt{C}}w_i$. Thus
+where
 \begin{equation}
-\mathcal{L}_{\Lambda,H}({\bm w}) = S\rho^{'} + q\sum_{i_1,\dots,i_H=1}^{\Lambda}X_{i_1,\dots,i_H}\prod_{k = 1}^{H}\tilde{w}_{i_k}.
-\label{eq:befloss}
-\end{equation}
-Note that the spherical assumption in Equation~\ref{eq:befspherical} directly implies that
-\begin{equation}
-\frac{1}{\Lambda}\sum_{i=1}^{\Lambda}\tilde{w}_i^2 = 1
+\frac{1}{\Lambda}\sum_{i=1}^{\Lambda}\tilde{w}_i^2 = 1,
 \label{eq:spherical}
 \end{equation}
+and $\mathcal{C}_1$, $\mathcal{C}_2$ are some constants and weights $\tilde{w}$ are simply scaled weights $w$.
+We skip the details showing this equivalence, and defer them to the Supplementary material, as they are strictly technical.
+
 To simplify the notation in Equation~\ref{eq:befloss} we drop the letter accents and simply denote $\hat{w}$ as $w$.
-We skip constant $S\rho^{'}$ as it does not matter when minimizing the loss function.
+We also skip constants $\mathcal{C}_1$ and $\mathcal{C}_2$ as they do not matter when minimizing the loss function.
 After substituting $q = \frac{1}{\Psi^{(H-1)/2H}}$ we obtain
@@
 Above the band ($\left(-\Lambda E_0(H),-\Lambda E_1(H)\right)$) containing only local minima (critical points of index $0$), there is another one, ($\left(-\Lambda E_1(H),-\Lambda E_2(H)\right)$), where one can only find local minima and saddle points of index $1$, and above this band there exists another one, ($\left(-\Lambda E_2(H),-\Lambda E_3(H)\right)$), where one can only find local minima and saddle points of index $1$ and $2$, etc.
-The above-described layered structure of the lowest critical values of the Hamiltonian of the spherical spin glass model was in-detail described in~\cite{AAC2010}, however with no connection to neural networks which is what we explore.
 
@@
 where 
-\[I(u) = -\frac{u}{E_{\infty}^2}\sqrt{u^2 - E_{\infty}^2} - \log(-u + \sqrt{u^2 - E_{\infty}^2}) + \log E_{\infty}.
+\[I(u) = -\frac{u}{E_{\infty}^2}\sqrt{u^2 \!-\! E_{\infty}^2} - \log(-u + \sqrt{u^2 \!-\! E_{\infty}^2}) + \log E_{\infty}.
 \]
@@
 
+\section{Loss function as a $H$ - spin spherical spin-glass model}
+
+We consider two loss functions, (random) absolute loss $\mathcal{L}^a_{\Lambda,H}(w)$ and (random) hinge loss $\mathcal{L}^h_{\Lambda,H}(w)$ defined as
+\[\mathcal{L}^a_{\Lambda,H}({\bm w}) = |Y_t - \hat{Y}_s|
+\]
+and
+\[\mathcal{L}^h_{\Lambda,H}({\bm w}) = \max(0,1-Y_t\hat{Y}_s).
+\]
+where $Y_t$ is a random variable corresponding to the true data labeling that takes values $-S$ or $S$ in case of the absolute loss and $-1$ or $1$ in case of the hinge loss, where $S = \sup_{\bf{w}}{\hat{Y}_s}$.
+Note that in case of the hinge loss $\max$ operator can be modelled as Bernoulli random variable, that we will refer to as $M$, with success ($M = 1$) probability $\rho^{'} = \frac{\mathcal{C}^{'}}{\rho\sqrt{\mathcal{C}^H}}$ for some non-negative constant $\mathcal{C}^{'}$.
+We assume $M$ is independent of $\hat{Y}_s$.
+Therefore we obtain that
+\[\mathcal{L}^a_{\Lambda,H}({\bm w}) = \left \{
+  \begin{tabular}{c}
+  $\!\!\!\!\!\!S - \hat{Y}_s$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = S$ \\
+  $\!S + \hat{Y}_s$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -S$ \\
+  \end{tabular}
+\right.
+\]
+and
+\begin{eqnarray*}
+\mathcal{L}^h_{\Lambda,H}({\bm w}) &=& \mathbb{E}_{M,A}[M(
+1-Y_t\hat{Y}_s)]\\&=& \left \{
+  \begin{tabular}{c}
+  $\!\!\!\!\!\!\mathbb{E}_{M}[M(1 - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = 1$ \\
+  $\!\mathbb{E}_{M}[M(1 + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -1$ \\
+  \end{tabular}
+\right.
+\end{eqnarray*}
+Note that both cases can be generalized as
+\[\mathcal{L}_{\Lambda,H}({\bm w}) = \left \{
+  \begin{tabular}{c}
+  $\!\mathbb{E}_{M}[M(S - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t  > 0$ \\
+  $\!\mathbb{E}_{M}[M(S + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t < 0$ \\
+  \end{tabular}
+\right.,
+\]
+where in case of the absolute loss $\rho^{'} = 1$ and in case of the hinge loss $S = 1$.
+Furthermore, using the fact that $X$'s are Gaussian random variables one we can further generalize both cases as
+\[\mathcal{L}_{\Lambda,H}({\bm w}) = S\rho^{'} \!+\! q\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!X_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}.
+\]
+Let $\tilde{w}_i = \sqrt[H]{\frac{\rho\rho^{'}}{\mathcal{C}^{'}}}w_i$ for all $i = \{1,2,\dots,k\}$. Note that $\tilde{w}_i = \frac{1}{\sqrt{C}}w_i$. Thus
+\begin{equation}
+\mathcal{L}_{\Lambda,H}({\bm w}) = S\rho^{'} + q\mathcal{C}^{'}\sum_{i_1,\dots,i_H=1}^{\Lambda}X_{i_1,\dots,i_H}\prod_{k = 1}^{H}\tilde{w}_{i_k}.
+\label{eq:befloss}
+\end{equation}
+Note that the spherical assumption in Equation~\ref{eq:befspherical} directly implies that
+\begin{equation*}
+\frac{1}{\Lambda}\sum_{i=1}^{\Lambda}\tilde{w}_i^2 = 1
+\end{equation*}
+To simplify the notation in Equation~\ref{eq:befloss} we drop the letter accents and simply denote $\hat{w}$ as $w$.
+We skip constant $S\rho^{'}$ and $\mathcal{C}^{'}$ as it does not matter when minimizing the loss function.
+After substituting $q = \frac{1}{\Psi^{(H-1)/2H}}$ we obtain
+\begin{equation*}
+\mathcal{L}_{\!\Lambda,H}({\bm w}) \!=\!
+\frac{1}{\Lambda^{\!(H\!-\!1)/2}}\!\!\!\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!\!\!\!\!X_{i_1,i_2,\dots,i_H}\!w_{i_1}\!w_{i_2}\!\!\dots\!w_{i_H}.
+\end{equation*}
+
 \section{Asymptotics of the mean number of critical points and local minima}

### 2014-10-23 PAPER_AMMLY.tex
shortening_further

@@
 
-The assumption of the redundancy of parameters implies that one can preserve $\epsilon$ to be close to $0$ even with $s << N$.
+The redundancy assumption implies that one can preserve $\epsilon$ to be close to $0$ even with $s << N$.
 
@@
 We assume that unique weights are close to being evenly distributed on the graph of connections of network $\mathcal{M}$.
-We call this assumption a \textit{uniformity assumption} (note it is analogous to the maximum entropy assumption).
-This assumption is in general consistent with the approach in~\cite{NIPS2013_5025}.
-In particular, this assumption implies that for all $(i_1,i_2,\dots,i_H):i_1,i_2,\dots,i_H \in \{1,2,\dots,s\}$ there exists a positive constant $c \geq 1$ such that the following holds
+We call this assumption a \textit{uniformity assumption}.
+Thus this assumption implies that for all $(i_1,i_2,\dots,i_H):i_1,i_2,\dots,i_H \in \{1,2,\dots,s\}$ there exists a positive constant $c \geq 1$ such that the following holds
 \begin{equation}
@@
 which corresponds to a network for which the lower-bound and upper-bound in Equation~\ref{eq:uniform} match.
-Note that one can combine both summations in Equation~\ref{eq:approx} and re-index this equation to obtain
+Note that one can combine both summations in Equation~\ref{eq:approx} and re-index its terms to obtain
 \begin{equation}
@@
 We also skip constants $\mathcal{C}_1$ and $\mathcal{C}_2$ as they do not matter when minimizing the loss function.
-After substituting $q = \frac{1}{\Psi^{(H-1)/2H}}$ we obtain
+After substituting $q = \frac{1}{\Psi^{(H-1)/2H}} = \frac{1}{\Lambda^{(H-1)/2}}$ we obtain
 \begin{equation}
@@
 An asymptotic evaluation of the comlexity of spherical $H$-spin spherical spin-glass models via random matrix theory was studied in the literature~\cite{AAC2010} where a precise description of the energy landscape for the Hamiltonians of these models is provided.
-In this paper we explore a strong connection of the Hamiltonian of these models, originated from physics, and the strongly non-convex loss functions used in deep learning.
-We use the results of the theoretical analysis of the complexity of spin-glass models~\cite{AAC2010} to gain an understading of the optimization in deep learning.
+In this paper we use the results of the theoretical analysis of the complexity of spin-glass models~\cite{AAC2010} to gain an understading of the optimization of strongly non-convex loss functions of neural networks.
 
@@
 
-Another important fact is that the band $(-E_0(H),-E_{\infty})$ is very narrow, i.e. it is order of magnitudes narrower than band $(-E_{\infty},0)$.
+The band $(-E_0(H),-E_{\infty})$ is in practice very narrow, i.e.
+it is order of magnitudes narrower than band $(-E_{\infty},0)$ (an example is shown in Figure~\ref{fig:Distr_cp_lm_sp} and~\ref{fig:Thetas}).
 
@@
 Next we will show the logarithmic asymptotics of the mean number of critical points (the asymptotics of the mean number of critical points can be found in the Supplementary material). 
-\begin{theorem}
+\begin{theorem}[\cite{AAC2010}, Theorem 2.5 and 2.8]
 For all $H \geq 2$
@@
 
-Below, we provide the asymptotics of the mean number of critical points (Theorem~\ref{thm:cpprecise}) and the mean number of local minima (Theorem~\ref{thm:lmspprecise}), which extend Theorem~\ref{thm:lmsp} and Theorem~\ref{thm:cp}.
+Below, we provide the asymptotics of the mean number of critical points (Theorem~\ref{thm:cpprecise}) and the mean number of local minima (Theorem~\ref{thm:lmspprecise}), which extend Theorem~\ref{thm:lmsp}.
 Those results are the consequences of Theorem 2.17.

### 2014-10-23 PAPER_AMMLY.tex
shortening_further

@@
 \vspace{-0.05in}
-\item Probability of finding a poor quality local minima is non-zero for small-size networks and it exponentially diminishes with the network size.
+\item Probability of finding a poor quality local minima is non-zero for small-size networks and it diminishes with the network size.
 \vspace{-0.05in}
 \item Finding the global minimum on the training set is not useful in practice as it often leads to overfitting.
-\vspace{-0.05in}
-\item The local minima are mostly flat and are characterised by Hessian with mostly zero eigenvalues. This is an indication that large-size networks can be simplified.
-\vspace{-0.05in}
-\item The number of positive eigenvalues of the Hessian at local minima is invariant to network size.
 \end{itemize}
@@
 Therefore $N \rightarrow \infty$ iff $\Psi \rightarrow \infty$, and $N \rightarrow \infty$ iff $\Lambda \rightarrow \infty$.
+Assuming boundedness of $H$ implies our results are primarily concerning wide, rather than deep, neural network learning.
 
@@
 Intuitively, for large networks (our analysis in Section~\ref{sec:theory} considers $\Lambda \rightarrow \infty$) one would expect $s$ to be small enough to simultaneously guarantee sufficiently small (close to $1$) $c$ and preserve good accuracy (small $\epsilon$).
-\textcolor{red}{That is because large networks have significantly more modelling power thus small $s$ is a natural form of controlling the overfitting.
-Besides then the data is mapped to a higher dimensional space.}
 

### 2014-10-23 PAPER_AMMLY.tex
shortening_further

@@
 These assumptions enable us to explain the complexity of the fully decoupled neural network through the prism of the results from the random matrix theory.
-We prove that for large-size decoupled networks the lowest critical values of the loss function are located in a well-defined narrow band lower-bounded by the global minimum and furthermore they form a layered structure.
+We prove that for large-size decoupled networks the lowest critical values of the random loss function are located in a well-defined narrow band lower-bounded by the global minimum and furthermore they form a layered structure.
 Moreover, finding them outside the band diminishes exponentially with the size of the network.
@@
 This emphasizes a major difference between large- and small-size networks where for the latter poor quality local minima have non-zero probability of being recovered.
-Simultaneously we prove that recovering the global minimum diminishes with the network size and that it is in practice irrelevant as global minimum often leads to data overfitting.
+Simultaneously we prove that recovering the global minimum becomes harder as the network size increases and that it is in practice irrelevant as global minimum often leads to overfitting.
 \end{abstract}
@@
 \label{fig:Distr_cp_lm_sp}
-\vspace{-0.1in}
+\vspace{-0.05in}
 \end{figure*}
@@
 
-\textcolor{red}{We need to prove that we get ot local minima not flat saddle points from Bengio paper.}
+\section{Conclusion}
+\label{sec:ConandFutWork}
 
-\section{Conclusion and Future Work}
-\label{sec:ConandFutWork}
+This paper establishes a connection between the neural network model and the spin-glass model.
+We show that under certain assumptions, the loss function of the fully decoupled large-size neural network of depth $H$ has similar landscape to the Hamiltonian of the $H$-spin spherical spin-glass model.
+In particular we show that the low-index critical points of the random loss function lie in the narrow band 'close' to the global minimum and form a layered structure.
+We empirically demonstrate that both models studied here are highly similar also in real settings, despite the presence of variable dependencies in real networks.
+We conjecture that common learning algorithms converge to the band of low-index critical points and recover local minima which are equivalent in terms of the test error.
+Moreover, the local minima recovered for large-size networks are of significantly higher quality than in case of the small-size networks, where for the latter the theoretical results of this paper do not hold.
+We finally demonstrate that recovering global minimum is irrelevant for large-size networks as it often leads to data overfitting.
 
